### 2024-08-14 manuscript_and_modelling_plots_takeovers.Rmd
Data and initial analysis script

---
title: "manuscript_modelling_and_plots_takeovers"
author: "Courtney Goodridge"
date: "14/02/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The code in this script produces the plots and model for the following manuscript:

## Packages

Here we load the packages that will be used for this analysis

```{r}
if(!require(here)) install.packages("here")
library(here)

if(!require(ggplot2)) install.packages("ggplot2")
library(ggplot2)

if(!require(dplyr)) install.packages("dplyr")
library(dplyr)

if(!require(tidyr)) install.packages("tidyr")
library(tidyr)

if(!require(viridis)) install.packages("viridis")
library(viridis)

if(!require(gridExtra)) install.packages("gridExtra")
library(gridExtra)

if(!require(readr)) install.packages("readr")
library(readr)

if(!require(plyr)) install.packages("plyr")
library(plyr)

if(!require(stringr)) install.packages("stringr")
library(stringr)

if(!require(readxl)) install.packages("readxl")
library(readxl)

if(!require(data.table)) install.packages("data.table")
library(data.table)

if(!require(xfun)) install.packages("xfun")
library(xfun)

if(!require(cowplot)) install.packages("cowplot")
library(cowplot)

if(!require(gganimate)) install.packages("gganimate")
library(gganimate)

if(!require(ggExtra)) install.packages("ggExtra")
library(ggExtra)

if(!require(plotly)) install.packages("plotly")
library(plotly)

if(!require(brms)) install.packages("brms")
library(brms)

if(!require(bayestestR)) install.packages("bayestestR")
library(bayestestR)

if(!require(emmeans)) install.packages("emmeans")
library(emmeans)

if(!require(ROSE)) install.packages("ROSE")
library(ROSE)

if(!require(Rmisc)) install.packages("Rmisc")
library(Rmisc)

if(!require(metafolio)) install.packages("metafolio")
library(metafolio)

if(!require(tibble)) install.packages("tibble")
library(tibble)

if(!require(modelr)) install.packages("modelr")
library(modelr)

if(!require(tidybayes)) install.packages("tidybayes")
library(tidybayes)

if(!require(mgcv)) install.packages("mgcv")
library(mgcv)

if(!require(ciTools)) install.packages("ciTools")
library(ciTools)

if(!require(gratia)) install.packages("gratia")
library(gratia)

if(!require(scales)) install.packages("scales")
library(scales)

if(!require(patchwork)) install.packages("patchwork")
library(patchwork)

if(!require(ggforce)) install.packages("ggforce")
library(ggforce)
```

## Load vehicle data

This provides timing responses to takeovers and collision data. We also remove participants that were removed in the gaze entropy analysis.

```{r}
# response data frame for vehicle and eye data per trial
response.vehicle.eye <- fread(file = here::here("takeover_performance_cogload_time_budget/Data/takeover.responses.critical.lat.long.csv"))

# removing participants from vehicle and gaze data
response.vehicle.eye <- response.vehicle.eye %>%
  dplyr::filter(ppid != 34, ppid != 39, ppid != 47) %>%
  tidyr::drop_na()

# make collision data 1s and 0s
response.vehicle.eye <- response.vehicle.eye %>%
  dplyr::mutate(collision = case_when(collision == TRUE ~ 1,
                                      collision == FALSE ~ 0))
```

## Loading participant information

```{r}
# select demographic data such as age, annual miles driven, years with license
participant.info <- read.csv(here::here("gaze_entropy_heterogenous/data/participant_info.csv")) %>%
  dplyr::select(1:5) %>%
  dplyr::rename("age" = "ï..Age", "ppid" = "Participant.ID")

# combine entropy dataframe with the participant information dataframe
response.vehicle.eye <- merge(response.vehicle.eye, participant.info, by = c("ppid"))

# some of these variables are added into the models later. To maintain numerical stability, they are centre so that the mean is 0 
response.vehicle.eye$age.c <- scale(response.vehicle.eye$age, center = T, scale = F)

response.vehicle.eye$Approximate.Annual.Mileage..Miles.c <- scale(response.vehicle.eye$Approximate.Annual.Mileage..Miles., center = T, scale = F)

response.vehicle.eye$No..of.years.holding.a.full.UK.driving.license.c <- scale(response.vehicle.eye$No..of.years.holding.a.full.UK.driving.license, center = T, scale = F)
```

# Removing outliers

Thre removal of outliers should only be done if the data do not represent actual behaviour for completing the task. In this sense, tag any RTs that are more than 4 SDs away from the mean of that condition as an outlier. This rules out responses where a driver took exceptionally long to place their hands on the steering wheel following a critical event.

```{r}
# computing outliers for braking reaction time
response.vehicle.eye <-  response.vehicle.eye %>%
  #dplyr::filter(collision == 0) %>%
  tidyr::drop_na() %>%
  dplyr::group_by(n_back, ttc_criticality.x) %>%
  dplyr::mutate(mean.rt = mean(rt), sd.rt = sd(rt)) %>%
  dplyr::mutate(sd.rt.4 =  sd.rt * 4) %>%
  dplyr::mutate(mean_4_sd = mean.rt + sd.rt.4) %>%
  dplyr::mutate(rt.outlier = rt > mean_4_sd)

# calculating outliers for hands on reaction time
response.vehicle.eye <-  response.vehicle.eye %>%
  #dplyr::filter(collision == 0) %>%
  tidyr::drop_na() %>%
  dplyr::group_by(n_back, ttc_criticality.x) %>%
  dplyr::mutate(mean.ho = mean(ho.rt), sd.ho = sd(ho.rt)) %>%
  dplyr::mutate(sd.ho.4 =  sd.ho * 4) %>%
  dplyr::mutate(mean_4_sd = mean.ho + sd.ho.4) %>%
  dplyr::mutate(ho.outlier = ho.rt > mean_4_sd)
```

# Number of participants

```{r}
response.vehicle.eye %>%
  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
  dplyr::group_by(ppid) %>%
  dplyr::slice(1) %>%
  dplyr::ungroup() %>%
  dplyr::summarise(avg = mean(age), min_age = min(age), max_age = max(age), mean_milage = mean(Approximate.Annual.Mileage..Miles.), min_mileage = min(Approximate.Annual.Mileage..Miles.), max_mileage = max(Approximate.Annual.Mileage..Miles.), mean_license = mean(No..of.years.holding.a.full.UK.driving.license), min_license = min(No..of.years.holding.a.full.UK.driving.license), max_license = max(No..of.years.holding.a.full.UK.driving.license), N = n()) %>%
  View()
```

# Modelling: Braking RT - model fitting

A paper by Ruscio et al (2015) proposed that braking reaction time is a multi-component cognitive skill:

1) Perception of the stimuli i.e, the looming signal towards the driver. This could realistically be detected via a change in pupil dilation as the looming lead vehicle comes to towards them
2) Time for mental processing of the situation
3) Moving foot from the accelerator pedal
4) time need to muscle to move foot toward the brake
5) Beginning of pressure on brake pedal.

In that study, they focus on braking in manual driving and thus lifting the foot from the accelerator and onto the brake is consider a component. However in the current study, driver's feet were off the pedal. Hence future work might want to begin modelling potential changes in "non-decision time" associated with event criticality and n-back. In this sense, ndt refers to steps 1 and 2.

```{r}
# load model
mod_braking_rt_bayesian_shifted_lognormal_ttc_slope <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/braking_rt_shifted_log_ttc_slope_priors.rds"))

# adding a random slope for the criticality of the effect
mod_braking_rt_bayesian_shifted_lognormal_ttc_slope <- brm(data = response.vehicle.eye %>% 
                                                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>% 
                                                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>% 
                                                             dplyr::mutate(ppid = as.factor(ppid)), 
                                                           family = shifted_lognormal(),
                                                           rt ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor| ppid),
                                                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                                                     prior(student_t(3, 0, 2.5), class = "b"),
                                                                     prior(lkj(2), class = cor)),
                                                                     iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
                                                                     file = "braking_rt_shifted_log_ttc_slope_priors")

# posterior predictive checks
pp_check(mod_braking_rt_bayesian_shifted_lognormal_ttc_slope, type = "dens_overlay_grouped", group = "n_back", ndraws = 100) +
  ggtitle("shifted_lognormal")

print(summary(mod_braking_rt_bayesian_shifted_lognormal_ttc_slope), digits = 5)
describe_posterior(mod_braking_rt_bayesian_shifted_lognormal_ttc_slope, centrality = "mean")
```

# Modelling: Braking RT - Visualising posterior draws and means

In the chunk below, I plot the posterior expected values alongside the distributions, over the raw data. The function *data_grid()* produces an empty dataframe from which to generate predictions from bthe model (https://mjskay.github.io/tidybayes/articles/tidy-brms.html)

```{r}
# Creates long format data frame of each participant within each condition. This is new data from which we can make some predictions regarding the effects of n-back and and ttc
empty_grid = response.vehicle.eye %>%
  dplyr::ungroup() %>%
  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0) %>%
  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
  data_grid(n_back, ttc_criticality_factor, ppid)

# we use a new dataset to plug into the model and a generate posterior predictive distribution. For this, we take into account the uncertainty of the fixed coefficients, the uncertainty of the variance parameters (random effects), and the uncertainty of individual observations (residual variance). With the model that contains this information and the new data, we can generate predictions regarding the uncertainty of new, unobserved data points.
predicted_draws = empty_grid %>%
  add_predicted_draws(mod_braking_rt_bayesian_shifted_lognormal_ttc_slope)

# When focusing on the marginal effects, we want to focus on the uncertainty of the parameter values, rather than individual residuals. So we can use the epred_draws() function to generate expected values. These include uncertainty of just two elements: uncertainty of the fixed effects, and uncertainty of the variance parameter (random effects). The argument re_formula = NULL is the default and thus the random effects are incorporated by default. Setting re_formula = NA removes the influences of the random effects.

# It should be noted that for the shifted log normal distribution, E(y) = exp(mu + sigma^2 / 2 + ndt) (https://github.com/paul-buerkner/brms/blob/28f778d7933f95422dda8f9a9f4333b975261120/R/posterior_epred.R#L341)
expected_values = empty_grid %>%
  add_epred_draws(mod_braking_rt_bayesian_shifted_lognormal_ttc_slope)

# labels
ttc_labs <- c("TTC = 3 s", "TTC = 5 s")
names(ttc_labs) <- c(as.factor(3), as.factor(5))

# expected values and model predicted means

posterior_braking_rt <- response.vehicle.eye %>%
  dplyr::ungroup() %>%
  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0) %>%
  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
  ggplot(aes(x = rt, y = n_back)) +
  stat_pointinterval(aes(x = .epred), data = expected_values, .width = c(.50, .95), position = position_nudge(y = -0.35)) +
  stat_interval(aes(x = .prediction), data = predicted_draws, .width = c(.50, .80, .95, .99)) +
  geom_jitter(data = response.vehicle.eye %>%
  dplyr::ungroup() %>%
  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0) %>%
  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)), size = 2, height = .08, alpha = .3) +
  #geom_point(conditional_df_fitted[[3]], mapping = aes(x = estimate__, y = n_back), col = "white") +
  scale_y_discrete(labels = c('No N-B','N-B'), guide = guide_axis(angle = 90)) +
  scale_color_brewer("Posterior predictive interval") +
  ggtitle("A") +
  #xlim(.5, 3.5) +
  xlab(expression(RT[B]~ "(s)")) +
  ylab(" ") +
  scale_x_continuous(breaks = seq(1, 3, .5), labels = label_number(accuracy = .5)) +
  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
  theme_bw() +
  theme(legend.position = "bottom", legend.direction = "horizontal", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 8, face = "bold"), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

# predicted gloabl mean RTs implied by the model

# setting re_formula = NA tells the function to not use any random effects - here we plot the n-back specific distributions 
grand_mean_n_back_dist <- mod_braking_rt_bayesian_shifted_lognormal_ttc_slope %>% 
  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
                                    n_back = FALSE),
              re_formula = NA)

grand_mean_n_back_dist %>% mean_hdi()

global_mean_ttc_braking_rt <- ggplot(grand_mean_n_back_dist ,aes(x = .epred, y = " ", fill = ttc_criticality_factor)) +
  stat_halfeye(alpha = .5) +
  ylab(NULL) +
  xlab(expression("Predicted mean"~ RT[B]~ "(s)")) +
  ggtitle("B") +
  scale_fill_discrete(name = "TTC", labels = c("3 s", "5 s")) +
  xlim(1, 1.6) +
  theme_bw() +
  theme(legend.position = c(.87, .60), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

# and now we plot the distribution of the difference between n_back and no n-back 
grand_mean_n_back_mer <- mod_braking_rt_bayesian_shifted_lognormal_ttc_slope %>% 
  emmeans(~ ttc_criticality_factor,
          at = list(n_back = FALSE),
          epred = TRUE, re_formula = NA) %>% 
  contrast(method = "revpairwise") %>% 
  gather_emmeans_draws()

grand_mean_n_back_mer  %>% mean_hdi()

# Marginal Effects at Representative values (MER) of TTC on braking RT
MER_ttc_braking_rt <- ggplot(grand_mean_n_back_mer, aes(x = .value, y = " ")) +
  stat_halfeye() +
  ylab(NULL) +
  xlab(expression(MER[RT[B]]~ "(s) for TTC")) +
  ggtitle("C") +
  scale_fill_discrete(name = "TTC", labels = c("3 s", "5 s")) +
  theme_bw() +
  theme(legend.position = c(.9, .7), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

fig1 <- posterior_braking_rt / (global_mean_ttc_braking_rt | MER_ttc_braking_rt)

# plot saving
ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript_plots/fig1.tiff"), plot = fig1, width = 16, height = 11, units = 'cm', dpi = 300, type = 'cairo')
```

# Modelling: hands-on time

Seemingly no effect of cognitive load on hands on time. Small effect on criticality

```{r}
# hands on time - distributions
ggplot(response.vehicle.eye %>%
                dplyr::filter(rt.outlier == FALSE, ho.rt != 0, collision == 0), mapping = aes(x = ho.rt)) +
  geom_histogram(aes(fill = as.factor(n_back)), alpha = 0.5, bins = 50, col = "black") + 
  xlab("Hands on RT (s)") +
  facet_wrap(~ ttc_criticality.x) +
  xlim(0, 3.5)

# load model
mod_ho_rt_bayesian_shifted_lognormal_ttc_slope <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/ho_rt_shifted_log_ttc_slope_priors.rds"))

# adding a random slope for the criticality of the effect
mod_ho_rt_bayesian_shifted_lognormal_ttc_slope <- brm(data = response.vehicle.eye %>%
                                                   dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>% 
                                                     dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>% 
                                                     dplyr::mutate(ppid = as.factor(ppid)),
                                                   family = shifted_lognormal(), 
                                                   ho.rt ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor| ppid),
                                                   prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                                             prior(student_t(3, 0, 2.5), class = "b"),
                                                             prior(lkj(2), class = cor)),
                                                   iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13, 
                                                   file = "ho_rt_shifted_log_ttc_slope_priors")

print(summary(mod_ho_rt_bayesian_shifted_lognormal_ttc_slope), digits = 5)
describe_posterior(mod_ho_rt_bayesian_shifted_lognormal_ttc_slope)

#### predicted posterior means and distribution ####
predicted_draws = empty_grid %>%
  add_predicted_draws(mod_ho_rt_bayesian_shifted_lognormal_ttc_slope)

expected_values = empty_grid %>%
  add_epred_draws(mod_ho_rt_bayesian_shifted_lognormal_ttc_slope)

# labels
ttc_labs <- c("TTC = 3 s", "TTC = 5 s")
names(ttc_labs) <- c(as.factor(3), as.factor(5))

posterior_ho_rt <- response.vehicle.eye %>%
  dplyr::ungroup() %>%
  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
  ggplot(aes(x = ho.rt, y = n_back)) +
  stat_pointinterval(aes(x = .epred), data = expected_values, .width = c(.50, .95), position = position_nudge(y = -0.35)) +
  stat_interval(aes(x = .prediction), data = predicted_draws, .width = c(.50, .80, .95, .99)) +
  geom_jitter(data = response.vehicle.eye %>%
  dplyr::ungroup() %>%
  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)), size = 2, height = .05, alpha = .3) +
  #geom_point(conditional_df_fitted[[3]], mapping = aes(x = estimate__, y = n_back), col = "white") +
  scale_y_discrete(labels = c('No N-B','N-B'), guide = guide_axis(angle = 90)) +
  scale_color_brewer("Posterior predictive interval") +
  ggtitle("A") +
  #xlim(.5, 3.5) +
  xlab(expression(RT[HO]~ "(s)")) +
  ylab(" ") +
  scale_x_continuous(limits = c(0, 3.5), breaks = seq(0, 3, .5), labels = label_number(accuracy = .5)) +
  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
  theme_bw() +
  theme(legend.position = "bottom", legend.direction = "horizontal", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 8, face = "bold"), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

#### Global mean effect of TTC ####

# setting re_formula = NA tells the function to not use any random effects - here we plot the n-back specific distributions 
grand_mean_n_back_dist_hort <- mod_ho_rt_bayesian_shifted_lognormal_ttc_slope %>% 
  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
                                    n_back = FALSE),
              re_formula = NA)

grand_mean_n_back_dist_hort %>% mean_hdi()

global_mean_ttc_ho_rt <- ggplot(grand_mean_n_back_dist_hort, aes(x = .epred, y = " ", fill = ttc_criticality_factor)) +
  stat_halfeye(alpha = .5) +
  ylab(NULL) +
  xlab(expression("Predicted mean"~ RT[HO]~ "(s)")) +
  ggtitle("B") +
  scale_fill_discrete(name = "TTC", labels = c("3 s", "5 s")) +
  theme_bw() +
  theme(legend.position = c(.88, .60), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

# and now we plot the distribution of the difference between n_back and no n-back 
grand_mean_n_back_mer_hort <- mod_ho_rt_bayesian_shifted_lognormal_ttc_slope %>% 
  emmeans(~ ttc_criticality_factor,
          at = list(n_back = FALSE),
          epred = TRUE, re_formula = NA) %>% 
  contrast(method = "revpairwise") %>% 
  gather_emmeans_draws()

grand_mean_n_back_mer_hort %>% mean_hdi()

# MER of TTC on hands on RT
MER_ttc_ho_rt <- ggplot(grand_mean_n_back_mer_hort, aes(x = .value, y = " ")) +
  stat_halfeye() +
  ylab(NULL) +
  xlab(expression(MER[RT[HO]]~ "(s) of TTC")) +
  ggtitle("C") +
  scale_fill_discrete(name = "TTC", labels = c("3 s", "5 s")) +
  theme_bw() +
  theme(legend.position = c(.93, .62), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

fig2 <- posterior_ho_rt / (global_mean_ttc_ho_rt | MER_ttc_ho_rt)

# plot saving
ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript_plots/fig2.tiff"), plot = fig2, width = 16, height = 11, units = 'cm', dpi = 300, type = 'cairo')
```

# Difference between hands on time and braking reaction time

```{r}
response.vehicle.eye.removed <- response.vehicle.eye %>%
  dplyr::ungroup() %>%
  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0) %>%
  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x), ppid = as.factor(ppid))

effects_existing_groups_braking_rt <- mod_braking_rt_bayesian_shifted_lognormal_ttc_slope %>%
  emmeans(~ ttc_criticality_factor + ppid,
          at = list(n_back = FALSE,
                    ppid = levels(as.factor(response.vehicle.eye.removed$ppid))),
          epred = TRUE, re_formula = NULL) %>% 
  contrast(method = "revpairwise", by = "ppid") %>% 
  gather_emmeans_draws() %>%
  mean_hdi()

braking_rt_mer_drivers <- effects_existing_groups_braking_rt %>%
  ggplot() +
  geom_point(mapping = aes(x = .value, y = ppid)) +
  geom_errorbarh(mapping = aes(x = .value, y = ppid, xmin = .lower, xmax = .upper), height = .5) +
  geom_vline(mapping = aes(xintercept = 0), linetype = "dashed", col = "red") + 
  xlim(-1, 3) +
  ggtitle("A") +
  ylab("Drivers") +
  xlab(expression(italic(BRT[MER])~ "of TTC (s) for each driver")) +
  theme_bw() +
  theme(legend.position = c(.9, .7), axis.title.x = element_text(size = 12), axis.text.x = element_text(size = 12), axis.title.y = element_text(size = 12), axis.text.y = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10)) +
  expand_limits(y = c(-5, 20))

effects_existing_groups_ho_rt <- mod_ho_rt_bayesian_shifted_lognormal_ttc_slope %>%
  emmeans(~ ttc_criticality_factor + ppid,
          at = list(n_back = FALSE,
                    ppid = levels(as.factor(response.vehicle.eye.removed$ppid))),
          epred = TRUE, re_formula = NULL) %>% 
  contrast(method = "revpairwise", by = "ppid") %>% 
  gather_emmeans_draws() %>%
  mean_hdi()

ho_rt_mer_drivers <- effects_existing_groups_ho_rt %>%
  ggplot() +
  geom_point(mapping = aes(x = .value, y = ppid)) +
  geom_errorbarh(mapping = aes(x = .value, y = ppid, xmin = .lower, xmax = .upper), height = .5) +
  geom_vline(mapping = aes(xintercept = 0), linetype = "dashed", col = "red") +
  xlim(-1, 3) +
  ggtitle("B") +
  xlab(expression(italic(HORT[MER])~ "of TTC (s) for each driver")) +
  ylab("Drivers") +
  theme_bw() +
  theme(legend.position = c(.9, .7), axis.title.x = element_text(size = 12), axis.text.x = element_text(size = 12), axis.title.y = element_text(size = 12), axis.text.y = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10)) +
  expand_limits(y = c(-5, 20))

fig3 <- braking_rt_mer_drivers / ho_rt_mer_drivers

# plot saving
ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript_plots/fig3.tiff"), plot = fig3, width = 17, height = 15, units = 'cm', dpi = 300, type = 'cairo')
```

## Modelling - SD of SWA

```{r}

# load model
mod_sd_steer_bayesian_lognormal_priors <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/sd_steer_lognormal_priors.rds"))

# sd of steering variance with regularising priors
mod_sd_steer_bayesian_lognormal_priors <- brm(data = response.vehicle.eye %>%
                                         dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>% 
                                         dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>% 
                                         dplyr::mutate(ppid = as.factor(ppid)),
                                       family = lognormal(),
                                       sd_steer ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor| ppid),
                                       prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                                 prior(student_t(3, 0, 2.5), class = "b")),
                                       iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
                                       file = "sd_steer_lognormal_priors")

print(summary(mod_sd_steer_bayesian_lognormal_priors), digits = 5)
describe_posterior(mod_sd_steer_bayesian_lognormal_priors, centrality = "mean")

# posterior predictive checks
pp_check(mod_sd_steer_bayesian_lognormal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)

# sd of steering variance with flat priors?
mod_sd_steer_bayesian_lognormal_flat_priors <- brm(data = response.vehicle.eye %>%
                                                     dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>% 
                                                     dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                                                     dplyr::mutate(ppid = as.factor(ppid)),
                                                   family = lognormal(), 
                                                   sd_steer ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor| ppid),
                                                   iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
                                                   file = "sd_steer_lognormal")

# logit model with weakly informative priors
prior(student_t(3, 0, 2.5)) %>% 
  parse_dist() %>% 
  ggplot(aes(xdist = .dist_obj, y = prior)) + 
  stat_halfeye(.width = c(.5, .99)) +
  scale_y_discrete(NULL, breaks = NULL, expand = expansion(add = 0.1)) +
  scale_x_continuous(expression(italic(p)(beta[1]))) +
  theme_bw() +xlim(-20, 20)

prior(cauchy(0, 2.5)) %>% 
  parse_dist() %>% 
  ggplot(aes(xdist = .dist_obj, y = prior)) + 
  stat_halfeye(.width = c(.5, .99)) +
  scale_y_discrete(NULL, breaks = NULL, expand = expansion(add = 0.1)) +
  scale_x_continuous(expression(italic(p)(beta[1]))) +
  theme_bw() +
  xlim(-20, 20)

print(summary(mod_sd_steer_bayesian_lognormal_flat_priors), digits = 5)
describe_posterior(mod_sd_steer_bayesian_lognormal_flat_priors)

### effect of TTC s###
grand_mean_ttc_sd_steer <- mod_sd_steer_bayesian_lognormal_priors %>% 
  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
                                    n_back = FALSE),
              re_formula = NA)

grand_mean_ttc_sd_steer %>% mean_hdi()

# and now we plot the distribution of the difference between n_back and no n-back 
grand_mean_ttc_ame_sd_steer <- mod_sd_steer_bayesian_lognormal_priors %>% 
  emmeans(~ ttc_criticality_factor,
          at = list(n_back = FALSE),
          epred = TRUE, re_formula = NA) %>% 
  contrast(method = "revpairwise") %>% 
  gather_emmeans_draws()

grand_mean_ttc_ame_sd_steer %>% mean_hdi()

#### effect of n-back ###
grand_mean_n_back_sd_steer <- mod_sd_steer_bayesian_lognormal_priors %>% 
  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3)),
                                    n_back = c(FALSE, TRUE)),
              re_formula = NA)

grand_mean_n_back_sd_steer %>% mean_hdi()

grand_mean_n_back_ame_sd_steer <- mod_sd_steer_bayesian_lognormal_priors %>% 
  emmeans(~ n_back,
          at = list(ttc_criticality_factor = as.factor(3)),
          epred = TRUE, re_formula = NA) %>% 
  contrast(method = "revpairwise") %>% 
  gather_emmeans_draws()

grand_mean_n_back_ame_sd_steer %>% mean_hdi()

```

## Modelling - longituindal accelerations

- TO DO

Tidy up longitudinal jerk modelling

Model lateral jerk to see if model fit and inferences are still good (with maximal random effects)

Add random interactions to all the other models

Adjust the plots and tables

Send to co-authors and start on supplemental material.

```{r}
# distribution of negative longitudinal jerk
ggplot(response.vehicle.eye %>%
         dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
         dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
         dplyr::mutate(ppid = as.factor(ppid)), mapping = aes(max_long_jerk)) +
  geom_histogram() +
  facet_grid(n_back ~ ttc_criticality_factor)

max_long_skewnormal_hella_weak_priors <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/max_long_skewnormal_hella_weak.rds"))

# model of maximum longitudinal acceleration with hella weak priors. To check if the model is blowing up cause if lack of priors constraining parameter values
max_long_skewnormal_hella_weak_priors <- brm(data = response.vehicle.eye %>%
                                               dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
                                               dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                                               dplyr::mutate(ppid = as.factor(ppid)),
                                      family = skew_normal(),
                                      prior = c(prior(normal(0, 100), class = "Intercept"),
                                                prior(normal(0, 100), class = "b")),
                                      max_long ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor | ppid),
                                      control = list(adapt_delta = 0.99999999999),
                                      iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
                                      file = "max_long_skewnormal_hella_weak")

grand_mean_n_back_dist <- max_long_skewnormal_hella_weak_priors %>% 
  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
                                    n_back = c(TRUE, FALSE)),
              re_formula = NA)

grand_mean_n_back_dist %>% mean_hdi()

print(summary(max_long_skewnormal_hella_weak_priors), digits = 5)
describe_posterior(max_long_skewnormal_hella_weak_priors, centrality = "mean")

pp_check(max_long_skewnormal_hella_weak_priors, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)

pp_check(max_long_skewnormal_hella_weak_priors, type = "stat_grouped", stat = "mean", group = "n_back")
pp_check(max_long_skewnormal_hella_weak_priors, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")

pp_check(max_long_skewnormal_hella_weak_priors, type = "stat_2d", stat = c("max", "min"))

max_long_skewnormal_kinda_weak_priors <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/max_long_skewnormal_kinda_weak.rds"))

# model of maximum longitudinal acceleration with kinda weak priors. Do parameter values still make sense ruling out really extreme values. 
max_long_skewnormal_kinda_weak_priors <- brm(data = response.vehicle.eye %>%
                                               dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
                                               dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                                               dplyr::mutate(ppid = as.factor(ppid)),
                                      family = skew_normal(),
                                      prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                                prior(student_t(3, 0, 2.5), class = "b")),
                                      max_long ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor | ppid),
                                      control = list(adapt_delta = 0.99999999999),
                                      iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
                                      file = "max_long_skewnormal_kinda_weak")

print(summary(max_long_skewnormal_kinda_weak_priors), digits = 5)
describe_posterior(max_long_skewnormal_kinda_weak_priors, centrality = "mean")

pp_check(max_long_skewnormal_kinda_weak_priors, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
pp_check(max_long_skewnormal_kinda_weak_priors, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)

pp_check(max_long_skewnormal_kinda_weak_priors, type = "stat_grouped", stat = "mean", group = "n_back")
pp_check(max_long_skewnormal_kinda_weak_priors, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")

pp_check(max_long_skewnormal_specific_priors, type = "stat_2d", stat = c("max", "min"))

grand_mean_n_back_dist <- max_long_skewnormal_kinda_weak_priors %>% 
  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
                                    n_back = c(TRUE, FALSE)),
              re_formula = NA)

grand_mean_n_back_dist %>% mean_hdi()

# model of maximum longitudinal acceleration with kinda weak priors. Including an interaction in the random effects
max_long_skewnormal_kinda_weak_priors_maximal <- brm(data = response.vehicle.eye %>%
                                               dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
                                               dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                                               dplyr::mutate(ppid = as.factor(ppid)),
                                      family = skew_normal(),
                                      prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                                prior(student_t(3, 0, 2.5), class = "b")),
                                      max_long ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor | ppid),
                                      control = list(adapt_delta = 0.99999999999),
                                      iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
                                      file = "max_long_skewnormal_kinda_weak_maximal")

print(summary(max_long_skewnormal_kinda_weak_priors_maximal), digits = 5)
describe_posterior(max_long_skewnormal_kinda_weak_priors_maximal, centrality = "mean")

pp_check(max_long_skewnormal_kinda_weak_priors_maximal, type = "stat_grouped", stat = "mean", group = "n_back")

ggplot() +
  geom_vline(response.vehicle.eye %>%
               dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
               dplyr::group_by(n_back) %>%
               dplyr::summarise(m = mean(max_long)), mapping = aes(xintercept = m)) +
  geom_histogram(pp_n_back_data$data %>%
                   dplyr::mutate(n_back = group), mapping = aes(x = value)) +
  facet_wrap(~ n_back)

pp_check(max_long_skewnormal_kinda_weak_priors_maximal, type = "stat_grouped", stat = "median", group = "ttc_criticality_factor")

pp_check(max_long_skewnormal_kinda_weak_priors_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
pp_check(max_long_skewnormal_kinda_weak_priors_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)

grand_mean_n_back_dist <- max_long_skewnormal_kinda_weak_priors_maximal %>% 
  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
                                    n_back = c(TRUE, FALSE)),
              re_formula = NA)

grand_mean_n_back_dist %>% mean_hdi()

max_long_laplace_kinda_weak_priors_maximal <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/max_long_asym_laplace_kinda_weak_maximal.rds"))

# model of maximum longitudinal acceleration with kinda weak priors. Including an interaction in the random effects
max_long_laplace_kinda_weak_priors_maximal <- brm(data = response.vehicle.eye %>%
                                               dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
                                               dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                                               dplyr::mutate(ppid = as.factor(ppid)),
                                      family = asym_laplace(),
                                      prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                                prior(student_t(3, 0, 2.5), class = "b")),
                                      max_long ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor | ppid),
                                      control = list(adapt_delta = 0.99999999999),
                                      iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
                                      file = "max_long_asym_laplace_kinda_weak_maximal")

print(summary(max_long_laplace_kinda_weak_priors_maximal), digits = 5)
describe_posterior(max_long_laplace_kinda_weak_priors_maximal, centrality = "mean")

grand_mean_n_back_dist <- max_long_laplace_kinda_weak_priors_maximal %>% 
  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
                                    n_back = c(TRUE, FALSE)),
              re_formula = NA)

grand_mean_n_back_dist %>% mean_hdi()

pp_check(max_long_laplace_kinda_weak_priors_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
pp_check(max_long_laplace_kinda_weak_priors_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)

pp_check(max_long_laplace_kinda_weak_priors_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
pp_check(max_long_laplace_kinda_weak_priors_maximal, type = "stat_grouped", stat = "mean", group = "n_back")

# model of maximum longitudinal acceleration with kinda weak priors. Including an interaction in the random effects - seems like a more specific prior helps the model fit. Work out what the parameters are for laplace and work out if we can get more specific? Also toy around with removing interaction random effect? 
max_long_laplace_specific_priors <- brm(data = response.vehicle.eye %>%
                                               dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
                                               dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                                               dplyr::mutate(ppid = as.factor(ppid)),
                                      family = asym_laplace(),
                                      prior = c(prior(normal(9, .5), class = "Intercept"),
                                                prior(normal(.5, .1), class = "b", coef = "ttc_criticality_factor5"),
                                                prior(student_t(3, 0, 2.5), class = "b", coef = "n_backTRUE"),
                                                prior(student_t(3, 0, 2.5), class = "b", coef = "n_backTRUE:ttc_criticality_factor5")),
                                      max_long ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor | ppid),
                                      control = list(adapt_delta = 0.99999999999),
                                      iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
                                      file = "max_long_laplace_specific_priors")

grand_mean_n_back_dist <- max_long_laplace_specific_priors %>% 
  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
                                    n_back = c(TRUE, FALSE)),
              re_formula = NA)

grand_mean_n_back_dist %>% mean_hdi()

print(summary(max_long_laplace_specific_priors), digits = 5)
describe_posterior(max_long_laplace_specific_priors, centrality = "mean")

pp_check(max_long_laplace_specific_priors, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
pp_check(max_long_laplace_specific_priors, type = "stat_grouped", stat = "mean", group = "n_back")

pp_check(max_long_laplace_specific_priors, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
pp_check(max_long_laplace_specific_priors, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)

# model of maximum longitudinal acceleration with kinda weak priors. Including an interaction in the random effects
max_long_laplace_kinda_weak_priors <- brm(data = response.vehicle.eye %>%
                                               dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
                                               dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                                               dplyr::mutate(ppid = as.factor(ppid)),
                                      family = asym_laplace(),
                                      prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                                prior(student_t(3, 0, 2.5), class = "b")),
                                      max_long ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor | ppid),
                                      control = list(adapt_delta = 0.99999999999),
                                      iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
                                      file = "max_long_asym_laplace_kinda_weak")

print(summary(max_long_laplace_specific_priors), digits = 5)
describe_posterior(max_long_laplace_specific_priors, centrality = "mean")

pp_check(max_long_laplace_kinda_weak_priors, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
pp_check(max_long_laplace_kinda_weak_priors, type = "stat_grouped", stat = "mean", group = "n_back")

pp_check(max_long_laplace_kinda_weak_priors, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
pp_check(max_long_laplace_kinda_weak_priors, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)

# prior for beta_0 i.e., when ttc = 3, and N-back = FALSE. max decelerations typically do not exceed 11 m/s^2 so the prior distribution for TTC = 3 should reflect this. 
prior(normal(9, .5)) %>% 
  parse_dist() %>% 
  ggplot(aes(xdist = .dist_obj, y = prior)) + 
  stat_halfeye(.width = c(.5, .99)) +
  scale_y_discrete(NULL, breaks = NULL, expand = expansion(add = 0.1)) +
  scale_x_continuous(expression(italic(p)(beta[1]))) +
  theme_bw()

# model of maximum longitudinal acceleration with kinda weak priors. Including an interaction in the random effects
max_long_laplace_specific_priors <- brm(data = response.vehicle.eye %>%
                                               dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
                                               dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                                               dplyr::mutate(ppid = as.factor(ppid)),
                                      family = asym_laplace(),
                                      prior = c(prior(normal(0, 50), class = "Intercept"),
                                                prior(normal(0, 50), class = "b")),
                                      max_long ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor | ppid),
                                      control = list(adapt_delta = 0.99999999999),
                                      iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
                                      file = "max_long_laplace_hella_weak_normal_0_50")

print(summary(max_long_laplace_specific_priors), digits = 5)
describe_posterior(max_long_laplace_normal_0_5, centrality = "mean")

pp_check(max_long_laplace_hella_weak_normal_0_50, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
pp_check(max_long_laplace_hella_weak_normal_0_50, type = "stat_grouped", stat = "mean", group = "n_back")

pp_check(max_long_laplace_hella_weak_normal_0_50, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
pp_check(max_long_laplace_hella_weak_normal_0_50, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)

grand_mean_n_back_dist <- max_long_laplace_hella_weak %>% 
  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
                                    n_back = c(TRUE, FALSE)),
              re_formula = NA)

grand_mean_n_back_dist %>% mean_hdi()

max_long_laplace_hella_weak <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/max_long_laplace_hella_weak.rds"))

max_long_laplace_normal_0_5 <- brm(data = response.vehicle.eye %>%
                                               dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
                                               dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                                               dplyr::mutate(ppid = as.factor(ppid)),
                                      family = asym_laplace(),
                                      prior = c(prior(normal(0, 5), class = "Intercept"),
                                                prior(normal(0, 5), class = "b")),
                                      max_long ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor | ppid),
                                      control = list(adapt_delta = 0.99999999999),
                                      iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
                                      file = "max_long_laplace_normal_0_5")

print(summary(max_long_laplace_normal_0_5), digits = 5)
describe_posterior(max_long_laplace_normal_0_5, centrality = "mean")

pp_check(max_long_laplace_hella_weak, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
pp_check(max_long_laplace_hella_weak, type = "stat_grouped", stat = "mean", group = "n_back")

pp_check(max_long_laplace_hella_weak, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
pp_check(max_long_laplace_hella_weak, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)

grand_mean_n_back_dist <- max_long_laplace_hella_weak %>% 
  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
                                    n_back = c(TRUE, FALSE)),
              re_formula = NA)

grand_mean_n_back_dist %>% mean_hdi()

# model of maximum longitudinal acceleration with kinda weak priors. Including an interaction in the random effects

max_long_mixture_weak_priors  <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/max_long_mixture_weak_prior.rds"))

skew_skew_mix = mixture(family = skew_normal(), family = skew_normal(), order = 'mu')

max_long_mixture_6 <- brm(data = response.vehicle.eye %>%
                                dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
                                dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                                dplyr::mutate(ppid = as.factor(ppid)),
                              family = skew_skew_mix,
                                      prior = c(prior(student_t(3, 0, 2.5), class = "Intercept", dpar = "mu1"),
                                                prior(student_t(3, 0, 2.5), class = "Intercept", dpar = "mu2"),
                                                prior(student_t(3, 0, 2.5), class = "b", dpar = "mu1"),
                                                prior(student_t(3, 0, 2.5), class = "b", dpar = "mu2")),
                                      bf(max_long ~ n_back * ttc_criticality_factor + (1 | ppid),
                                         theta1 ~ ttc_criticality_factor),
                                      control = list(adapt_delta = 0.99999999999),
                                      iter = 6000, warmup = 3000, chains = 4, cores = 4, seed = 13,
                                      file = "max_long_mixture_6")

print(summary(max_long_mixture_6), digits = 5)
describe_posterior(max_long_mixture_6, centrality = "mean")

pp_check(max_long_mixture_6, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
pp_check(max_long_mixture_6, type = "stat_grouped", stat = "mean", group = "n_back")

pp_check(max_long_mixture_6, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
pp_check(max_long_mixture_6, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)

grand_mean_n_back_dist <- max_long_mixture_2_ttc %>% 
  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5))),
              re_formula = NA)

grand_mean_n_back_dist %>% mean_hdi()

# model of maximum longitudinal acceleration with hella weak priors. To check if the model is blowing up cause if lack of priors constraining parameter values
max_long_jerk_skewnormal_reg_priors_maximal <- brm(data = response.vehicle.eye %>%
                                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
                                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                                             dplyr::mutate(ppid = as.factor(ppid)),
                                           family = skew_normal(),
                                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                                     prior(student_t(3, 0, 2.5), class = "b")),
                                           max_long_jerk ~ n_back.x * ttc_criticality_factor + (n_back.x * ttc_criticality_factor | ppid),
                                           control = list(adapt_delta = 0.99999999999),
                                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
                                           file = "max_long_jerk_skewnormal_reg_priors_maximal")

print(summary(max_long_jerk_skewnormal_reg_priors_maximal), digits = 5)
describe_posterior(max_long_jerk_skewnormal_reg_priors_maximal, centrality = "mean")

pp_check(max_long_jerk_skewnormal_reg_priors_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
pp_check(max_long_jerk_skewnormal_reg_priors_maximal, type = "stat_grouped", stat = "mean", group = "n_back.x")

pp_check(max_long_jerk_skewnormal_reg_priors_maximal, type = "hist", stat = "mean", group = "n_back.x")

pp_check(max_long_jerk_skewnormal_reg_priors_maximal, type = "dens_overlay_grouped", group = "n_back.x", ndraws = 100)
pp_check(max_long_jerk_skewnormal_reg_priors_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)

# model of maximum longitudinal acceleration with hella weak priors. To check if the model is blowing up cause if lack of priors constraining parameter values
max_long_jerk_laplace_reg_priors_maximal <- brm(data = response.vehicle.eye %>%
                                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
                                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                                             dplyr::mutate(ppid = as.factor(ppid)),
                                           family = asym_laplace(),
                                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                                     prior(student_t(3, 0, 2.5), class = "b")),
                                           max_long_jerk ~ n_back.x * ttc_criticality_factor + (n_back.x * ttc_criticality_factor | ppid),
                                           control = list(adapt_delta = 0.99999999999),
                                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
                                           file = "max_long_jerk_laplace_reg_priors_maximal")

print(summary(max_long_jerk_laplace_reg_priors_maximal), digits = 5)
describe_posterior(max_long_jerk_laplace_reg_priors_maximal, centrality = "mean")

pp_check(max_long_jerk_laplace_reg_priors_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
pp_check(max_long_jerk_laplace_reg_priors_maximal, type = "stat_grouped", stat = "mean", group = "n_back.x")

pp_check(max_long_jerk_laplace_reg_priors_maximal, type = "dens_overlay_grouped", group = "n_back.x", ndraws = 100)
pp_check(max_long_jerk_laplace_reg_priors_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)

# setting re_formula = NA tells the function to not use any random effects - here we plot the n-back specific distributions 
grand_mean_n_back_dist <- max_long_jerk_skewnormal_reg_priors %>% 
  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
                                    n_back.x = FALSE),
              re_formula = NA)

grand_mean_n_back_dist %>% mean_hdi()

# prior for beta_C i.e., the change in max long when TTC = 5 s
prior(uniform(10, 11)) %>% 
  parse_dist() %>% 
  ggplot(aes(xdist = .dist_obj, y = prior)) + 
  stat_halfeye(.width = c(.5, .99)) +
  scale_y_discrete(NULL, breaks = NULL, expand = expansion(add = 0.1)) +
  scale_x_continuous(expression(italic(p)(beta[1]))) +
  theme_bw()

# regularising priors for the rest of the parameters
prior(normal(9, 1)) %>% 
  parse_dist() %>% 
  ggplot(aes(xdist = .dist_obj, y = prior)) + 
  stat_halfeye(.width = c(.5, .99)) +
  scale_y_discrete(NULL, breaks = NULL, expand = expansion(add = 0.1)) +
  scale_x_continuous(expression(italic(p)(beta[1]))) +
  theme_bw()

prior(student_t(30, 9, 2.5)) %>% 
  parse_dist() %>% 
  ggplot(aes(xdist = .dist_obj, y = prior)) + 
  stat_halfeye(.width = c(.5, .99)) +
  scale_y_discrete(NULL, breaks = NULL, expand = expansion(add = 0.1)) +
  scale_x_continuous(expression(italic(p)(beta[1]))) +
  theme_bw()

```

## Modelling - lateral accelerations

```{r}
ggplot(response.vehicle.eye %>%
         dplyr::filter(rt.outlier == FALSE, ho.rt != 0, collision == 0), mapping = aes(x = max_lat)) +
  geom_histogram(aes(fill = as.factor(n_back)), alpha = 0.5, bins = 50, col = "black") +
  facet_wrap(~ttc_criticality.x)

# load model
mod_max_lat_bayesian_lognormal <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/max_lat_lognormal_priors.rds"))

# model of maximum longitudinal acceleration with priors
mod_max_lat_bayesian_lognormal <- brm(data = response.vehicle.eye %>%
                                        dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
                                        dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                                        dplyr::mutate(ppid = as.factor(ppid)),
                                      family = lognormal(),
                                      prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                                prior(student_t(3, 0, 2.5), class = "b")),
                                       max_lat ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor | ppid),
                                      control = list(adapt_delta = 0.99999999999),
                                      iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
                                      file = "max_lat_lognormal_priors")

print(summary(mod_max_lat_bayesian_lognormal), digits = 5)
describe_posterior(mod_max_lat_bayesian_lognormal, centrality = "mean")

# effect of event critcality
grand_mean_ttc_ame_max_la <- mod_max_lat_bayesian_lognormal %>% 
  emmeans(~ ttc_criticality_factor,
          at = list(n_back = FALSE),
          epred = TRUE, re_formula = NA) %>% 
  contrast(method = "revpairwise") %>% 
  gather_emmeans_draws()

grand_mean_ttc_ame_max_la %>% mean_hdi()

# effect of n-back
grand_mean_ttc_ame_max_la <- mod_max_lat_bayesian_lognormal %>% 
  emmeans(~ n_back,
          at = list(ttc_criticality_factor = as.factor(5)),
          epred = TRUE, re_formula = NA) %>% 
  contrast(method = "revpairwise") %>% 
  gather_emmeans_draws()

grand_mean_ttc_ame_max_la %>% mean_hdi()

#### predicted posterior means and distribution ####
predicted_draws = empty_grid %>%
  add_predicted_draws(mod_max_lat_bayesian_lognormal)

expected_values = empty_grid %>%
  add_epred_draws(mod_max_lat_bayesian_lognormal)

posterior_max_lat <- response.vehicle.eye %>%
  dplyr::ungroup() %>%
  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0) %>%
  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
  ggplot(aes(x = max_lat, y = n_back)) +
  stat_pointinterval(aes(x = .epred), data = expected_values, .width = c(.50, .95), position = position_nudge(y = -0.35)) +
  stat_interval(aes(x = .prediction), data = predicted_draws, .width = c(.50, .80, .95, .99)) +
  geom_jitter(data = response.vehicle.eye %>%
  dplyr::ungroup() %>%
  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0) %>%
  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)), height = .03, alpha = .2) +
  #geom_point(conditional_df_fitted[[3]], mapping = aes(x = estimate__, y = n_back), col = "white") +
  scale_y_discrete(labels = c('No N-B','N-B'), guide = guide_axis(angle = 90)) +
  ggtitle("A") +
  scale_color_brewer("Posterior predictive interval") +
  xlim(0, 10) +
  xlab(expression(MAX[LA] ~"("~m/s^2~")")) +
  ylab(" ") +
  #scale_x_continuous(breaks = seq(0, .8, .2), labels = label_number(accuracy = 0.01)) +
  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
  theme_bw() +
  theme(legend.position = "bottom", legend.direction = "horizontal", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 8, face = "bold"), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

avg_lat_acc <- ggplot(critical.manual %>%
         dplyr::arrange(trialid, timestamp_common_manual) %>%
         dplyr::group_by(n_back, ttc_criticality, timestamp_common_manual) %>%
         dplyr::summarise(lat_acc = mean(latacc)) %>%
         dplyr::ungroup(), mapping = aes(x = timestamp_common_manual, y = lat_acc, col = as.factor(ttc_criticality))) +
  geom_path() +
  ggtitle("B") +
  ylab(expression("LA ("~m/s^2~")")) +
  xlab("Time (s)") +
  scale_color_discrete(name = "TTC", labels = c("3 s", "5 s")) +
  facet_wrap(~ n_back, labeller = labeller(n_back = l.labs)) +
  theme_bw() +
  theme(legend.position = c(.35, .21), legend.direction = "horizontal", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

fig6 <- posterior_max_lat / avg_lat_acc

# plot saving
ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript_plots/fig6.tiff"), plot = fig6, width = 16, height = 11, units = 'cm', dpi = 300, type = 'cairo')

# predicted means for max lat
grand_mean_n_back_dist <- mod_max_lat_bayesian_lognormal %>% 
  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
                                    n_back = FALSE),
              re_formula = NA)

grand_mean_n_back_dist %>% mean_hdi()
```

## SDLP

```{r}
# SDLP - distributions
ggplot(response.vehicle.eye %>%
                dplyr::filter(rt.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15), mapping = aes(x = sdlp)) +
  geom_histogram(aes(fill = as.factor(n_back)), alpha = 0.5, bins = 50, col = "black") + 
  xlab("SDLP") +
  facet_wrap(~ ttc_criticality.x)

# load model
mod_sdlp_bayesian_lognormal_priors <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/sdlp_lognormal_priors.rds"))

# initial model of SDLP
mod_sdlp_bayesian_lognormal_priors <- brm(data = response.vehicle.eye %>%
                                     dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
                                     dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                                     dplyr::mutate(ppid = as.factor(ppid)),
                                   family = lognormal(),
                                   prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                                prior(student_t(3, 0, 2.5), class = "b")),
                                   sdlp ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor| ppid),
                                   control = list(adapt_delta = 0.95),
                                   iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13, 
                                   file = "sdlp_lognormal_priors")

print(summary(mod_sdlp_bayesian_lognormal_priors), digits = 5)
describe_posterior(mod_sdlp_bayesian_lognormal_priors, centrality = "mean")

pp_check(mod_sdlp_bayesian_lognormal_priors, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100) 
pp_check(mod_sdlp_bayesian_lognormal_priors, type = "stat_grouped", stat = "mean", group = c("ttc_criticality_factor"))

#### predicted posterior means and distribution ####
predicted_draws = empty_grid %>%
  add_predicted_draws(mod_sdlp_bayesian_lognormal_priors)

expected_values = empty_grid %>%
  add_epred_draws(mod_sdlp_bayesian_lognormal_priors)

# labels
ttc_labs <- c("TTC = 3 s", "TTC = 5 s")
names(ttc_labs) <- c(as.factor(3), as.factor(5))

posterior_sdlp <- response.vehicle.eye %>%
  dplyr::ungroup() %>%
  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
  ggplot(aes(x = sdlp, y = n_back)) +
  stat_pointinterval(aes(x = .epred), data = expected_values, .width = c(.50, .95), position = position_nudge(y = -0.35)) +
  stat_interval(aes(x = .prediction), data = predicted_draws, .width = c(.50, .80, .95, .99)) +
  geom_jitter(data = response.vehicle.eye %>%
  dplyr::ungroup() %>%
  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)), size = 2, height = .05, alpha = .3) +
  #geom_point(conditional_df_fitted[[3]], mapping = aes(x = estimate__, y = n_back), col = "white") +
  scale_y_discrete(labels = c('No N-B','N-B'), guide = guide_axis(angle = 90)) +
  scale_color_brewer("Posterior predictive interval") +
  ggtitle("A") +
  #xlim(.5, 3.5) +
  xlab(expression(SD[LP]~ "(m)")) +
  ylab(" ") +
  xlim(0, 2) +
  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
  theme_bw() +
  theme(legend.position = "bottom", legend.direction = "horizontal", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 8, face = "bold"), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

# predicted global mean RTs implied by the model

# setting re_formula = NA tells the function to not use any random effects - here we plot the n-back specific distributions 
grand_mean_n_back_dist <- mod_sdlp_bayesian_lognormal_priors %>% 
  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
                                    n_back = FALSE),
              re_formula = NA)

grand_mean_n_back_dist %>% mean_hdi()

global_mean_ttc_SDLP <- ggplot(grand_mean_n_back_dist ,aes(x = .epred, y = " ", fill = ttc_criticality_factor)) +
  stat_halfeye(alpha = .5) +
  ylab(NULL) +
  xlab(expression("Predicted mean"~ SD[LP]~ "(m)")) +
  ggtitle("B") +
  scale_fill_discrete(name = "TTC", labels = c("3 s", "5 s")) +
  theme_bw() +
  theme(legend.position = c(.88, .6), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

# and now we plot the distribution of the difference between n_back and no n-back 
grand_mean_n_back_mer <- mod_sdlp_bayesian_lognormal_priors %>% 
  emmeans(~ ttc_criticality_factor,
          at = list(n_back = FALSE),
          epred = TRUE, re_formula = NA) %>% 
  contrast(method = "revpairwise") %>% 
  gather_emmeans_draws()

grand_mean_n_back_mer %>% mean_hdi()

grand_mean_n_back_mer <- mod_sdlp_bayesian_lognormal_priors %>% 
  emmeans(~ n_back,
          at = list(ttc_criticality_factor = as.factor(5)),
          epred = TRUE, re_formula = NA) %>% 
  contrast(method = "revpairwise") %>% 
  gather_emmeans_draws()

grand_mean_n_back_mer %>% mean_hdi()

# Average marginal effect (AME) of TTC on braking RT
MER_ttc_SDLP <- ggplot(grand_mean_n_back_mer, aes(x = .value, y = " ")) +
  stat_halfeye() +
  ylab(NULL) +
  xlab(expression(MER[SD[LP]]~ "(m) of TTC")) +
  ggtitle("C") +
  scale_fill_discrete(name = "TTC", labels = c("3 s", "5 s")) +
  theme_bw() +
  theme(legend.position = c(.9, .7), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

fig7 <- posterior_sdlp / (global_mean_ttc_SDLP | MER_ttc_SDLP)

# plot saving
ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript_plots/fig7.tiff"), plot = fig7, width = 16, height = 11, units = 'cm', dpi = 300, type = 'cairo')
```

## Loading model for SD of horizontal gaze during manual driving

```{r}
# load model
mod_sd_yaw_gaussian <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/sd_yaw_gaussian_priors.rds"))

# initial model of sd_yaw
mod_sd_yaw_gaussian <- brm(data = response.vehicle.eye %>%
                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                             dplyr::mutate(ppid = as.factor(ppid)),
                           family = gaussian(),
                           sd_yaw ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor| ppid),
                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                     prior(student_t(3, 0, 2.5), class = "b")),
                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13, 
                                                   file = "sd_yaw_gaussian_priors")
# posterior predictive checks
pp_check(mod_sd_yaw_gaussian, type = "dens_overlay_grouped", group = "n_back", ndraws = 100) +
  ggtitle("gaussian")

print(summary(mod_sd_yaw_gaussian), digits = 5)
describe_posterior(mod_sd_yaw_gaussian)
```

## Modelling SD yaw during automation

```{r}
# load model
mod_sd_yaw_automation_gaussian <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/sd_yaw_automation_gaussian_priors.rds"))

# initial model of sd_yaw
mod_sd_yaw_automation_gaussian <- brm(data = response.vehicle.eye %>%
                             dplyr::filter(rt.outlier == FALSE, 
                                           ho.outlier == FALSE, 
                                           ho.rt != 0, collision == 0, 
                                           ho.rt > .15) %>%
                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                             dplyr::mutate(ppid = as.factor(ppid)),
                           family = gaussian(),
                           sd_yaw_automation ~ n_back + (n_back | ppid),
                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                     prior(student_t(3, 0, 2.5), class = "b")),
                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13, 
                                                   file = "sd_yaw_automation_gaussian_priors")
# model summmary
print(summary(mod_sd_yaw_automation_gaussian), digits = 5)
describe_posterior(mod_sd_yaw_automation_gaussian)

# posterior predictive checks
pp_check(mod_sd_yaw_automation_gaussian, type = "dens_overlay_grouped", group = "n_back", ndraws = 100) 
pp_check(mod_sd_yaw_automation_gaussian, type = "stat_grouped", stat = "mean", group = c("n_back"))

# average predicted SD of yaw during automation with and without n-back
sd_yaw_automation_n_back_dist <- mod_sd_yaw_automation_gaussian %>% 
  epred_draws(newdata = expand_grid(n_back = c(TRUE, FALSE)),
              re_formula = NA)

sd_yaw_automation_n_back_dist %>% mean_hdi()

# average effect
sd_yaw_automation_n_back_mer <- mod_sd_yaw_automation_gaussian %>% 
  emmeans(~ n_back,
          epred = TRUE, re_formula = NA) %>% 
  contrast(method = "revpairwise") %>% 
  gather_emmeans_draws()

sd_yaw_automation_n_back_mer %>% mean_hdi()

# 
prior(student_t(3, -2, 2.5)) %>% 
  parse_dist() %>% 
  ggplot(aes(xdist = .dist_obj, y = prior)) + 
  stat_halfeye(.width = c(.5, .99)) +
  scale_y_discrete(NULL, breaks = NULL, expand = expansion(add = 0.1)) +
  scale_x_continuous(expression(italic(p)(beta[1]))) +
  theme_bw()

```

## Plotting SD of horizontal/vertical gaze data

```{r}
# labels - n-back
l.labs <- c("No N-back", "N-back")
names(l.labs) <- c("FALSE", "TRUE")

# labels - ttc
ttc_labs <- c("TTC = 3 s", "TTC = 5 s")
names(ttc_labs) <- c(as.factor(3), as.factor(5))

n_back_TRUE_automation <- ggplot(dat.eye.automation %>%
         dplyr::filter(n_back == TRUE), mapping = aes(x = yaw, y = pitch)) +
  geom_density_2d(aes(col = ..level..), alpha = .5, binwidth = .00003) +
  facet_wrap(~ n_back, labeller = labeller(n_back = l.labs)) +
  ggtitle("B") +
  scale_colour_viridis_c(option = "C") +
  annotate(
    'text',
    x = 0,
    y = -30,
    label = 'Reduced horizontal dispersion',
    fontface = 'bold', 
    size = 2.5
  ) +
  annotate(
    'text',
    x = 25,
    y = 18,
    label = 'Increased gaze concentration',
    fontface = 'bold',
    size = 2.5
  ) +
  annotate(
    'curve',
    x = 27, # Play around with the coordinates until you're satisfied
    y = 16,
    yend = 5,
    xend = 10,
    linewidth = .7,
    curvature = 0,
    arrow = arrow(length = unit(0.2, 'cm'))
  ) +
  annotate(
    'text',
    x = -25,
    y = 14,
    label = 'Rear-view mirror',
    fontface = 'bold', 
    size = 2.5
  ) +
  annotate(
    'text',
    x = 40,
    y = -20,
    label = 'Wing mirror',
    fontface = 'bold', 
    size = 2.5
  ) +
  annotate( # visual tunneling
    'rect',
    xmin = -3,
    xmax = 10,
    ymin = -10,
    ymax = 4,
    alpha = 0, # This was put back to 0.5
    size = .5,
    col = viridis(2)[2]
  ) +
   annotate( # rear-view mirror
    'rect',
    xmin = -35,
    xmax = -15,
    ymin = -3,
    ymax = 12,
    alpha = 0, 
    size = .5,
    col = viridis(2)[2]
  ) +
     annotate( # wing mirror
    'rect',
    xmin = 32,
    xmax = 48,
    ymin = -18,
    ymax = -1,
    alpha = 0, 
    size = .5,
    col = viridis(2)[2]
  ) +
    annotate(
    'curve',
    x = -10, # Play around with the coordinates until you're satisfied
    y = -27,
    yend = -12,
    xend = -7,
    linewidth = .7,
    curvature = -0.3,
    arrow = arrow(length = unit(0.2, 'cm'))
  ) +
  annotate(
    'curve',
    x = 20, # Play around with the coordinates until you're satisfied
    y = -27,
    yend = -10,
    xend = 18,
    linewidth = .7,
    curvature = 0.3,
    arrow = arrow(length = unit(0.2, 'cm'))
  ) +
  xlab("Yaw (°)") +
  ylab("Pitch (°)") +
  xlim(-50, 50) +
  scale_y_continuous(limits = c(-32, 20), breaks = seq(-30, 20, 15)) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 11), 
        axis.text.x = element_text(size = 11), 
        axis.title.y = element_text(size = 11), 
        axis.text.y = element_text(size = 11), 
        title = element_text(size = 18),
        plot.title = element_text(size = 15, face = "bold"), 
        strip.text = element_text(face = "bold", size = 10))

n_back_FALSE_automation <- ggplot(dat.eye.automation %>%
         dplyr::filter(n_back == FALSE), mapping = aes(x = yaw, y = pitch)) +
  geom_density_2d(aes(col = ..level..), alpha = .5, binwidth = .00003) +
  facet_wrap(~ n_back, labeller = labeller(n_back = l.labs)) +
  ggtitle("A") +
  scale_colour_viridis_c(option = "C") +
  annotate( # visual tunneling
    'rect',
    xmin = -3,
    xmax = 10,
    ymin = -10,
    ymax = 4,
    alpha = 0, # This was put back to 0.5
    size = .5,
    col = viridis(2)[2]
  ) +
   annotate( # rear-view mirror
    'rect',
    xmin = -35,
    xmax = -15,
    ymin = -3,
    ymax = 12,
    alpha = 0, 
    size = .5,
    col = viridis(2)[2]
  ) +
     annotate( # wing mirror
    'rect',
    xmin = 32,
    xmax = 48,
    ymin = -18,
    ymax = -1,
    alpha = 0, 
    size = .5,
    col = viridis(2)[2]
  ) +
  annotate(
    'text',
    x = -25,
    y = 14,
    label = 'Rear-view mirror',
    fontface = 'bold', 
    size = 2.5
  ) +
  annotate(
    'text',
    x = 40,
    y = -20,
    label = 'Wing mirror',
    fontface = 'bold', 
    size = 2.5
  ) +
  xlab("Yaw (°)") +
  ylab("Pitch (°)") +
  xlim(-50, 50) +
  scale_y_continuous(limits = c(-32, 20), breaks = seq(-30, 20, 15)) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 11), 
        axis.text.x = element_text(size = 11), 
        axis.title.y = element_text(size = 11), 
        axis.text.y = element_text(size = 11), 
        title = element_text(size = 18),
        plot.title = element_text(size = 15, face = "bold"), 
        strip.text = element_text(face = "bold", size = 10))

n_back_automation_disp <- n_back_FALSE_automation + n_back_TRUE_automation + plot_layout(axes = "collect")

# plot saving
ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript_plots/n_back_automation_disp.tiff"), plot = n_back_automation_disp, width = 16, height = 8, units = 'cm', dpi = 300, type = 'cairo')

# gaze concentration during manual driving

n_back_ttc_manual_disp_ttc5 <- ggplot(dat.eye.manual %>%
                                   dplyr::filter(ttc_criticality == 5), mapping = aes(x = yaw, y = pitch)) +
  geom_density_2d(aes(col = ..level..), alpha = .5, binwidth = .00003) +
  facet_grid(ttc_criticality ~ n_back, labeller = labeller(n_back = l.labs, ttc_criticality = ttc_labs)) +
  ggtitle("B") +
  scale_colour_viridis_c(option = "C") +
  annotate( # dashboard area
    'rect',
    xmin = -10,
    xmax = 25,
    ymin = -30,
    ymax = -15,
    alpha = 0, 
    size = .5,
    col = viridis(2)[2]
  ) +
  annotate( # visual tunneling
    'rect',
    xmin = -3,
    xmax = 10,
    ymin = -10,
    ymax = 4,
    alpha = 0, # This was put back to 0.5
    size = .5,
    col = viridis(2)[2]
  ) +
    annotate(
    'text',
    x = 25,
    y = 18,
    label = 'Increased gaze concentration',
    fontface = 'bold',
    size = 2.5
  ) +
  annotate(
    'curve',
    x = 27, # Play around with the coordinates until you're satisfied
    y = 16,
    yend = 5,
    xend = 10,
    linewidth = .7,
    curvature = 0,
    arrow = arrow(length = unit(0.2, 'cm'))
  ) +
  annotate(
    'text',
    x = 10,
    y = -32,
    label = 'Dashboard area',
    fontface = 'bold', 
    size = 2.5
  ) +
  xlab("Yaw (°)") +
  ylab("Pitch (°)") +
  xlim(-50, 50) +
  scale_y_continuous(limits = c(-32, 20), breaks = seq(-30, 20, 15)) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 11), 
        axis.text.x = element_text(size = 11), 
        axis.title.y = element_text(size = 11), 
        axis.text.y = element_text(size = 11), 
        title = element_text(size = 18),
        plot.title = element_text(size = 15, face = "bold"), 
        strip.text = element_text(face = "bold", size = 10))

n_back_ttc_manual_disp_ttc3 <- ggplot(dat.eye.manual %>%
                                   dplyr::filter(ttc_criticality == 3), mapping = aes(x = yaw, y = pitch)) +
  geom_density_2d(aes(col = ..level..), alpha = .5, binwidth = .00003) +
  facet_grid(ttc_criticality ~ n_back, labeller = labeller(n_back = l.labs, ttc_criticality = ttc_labs)) +
  ggtitle("A") +
  scale_colour_viridis_c(option = "C") +
  annotate( # dashboard area
    'rect',
    xmin = -10,
    xmax = 25,
    ymin = -30,
    ymax = -15,
    alpha = 0, 
    size = .5,
    col = viridis(2)[2]
  ) +
  annotate( # visual tunneling
    'rect',
    xmin = -3,
    xmax = 10,
    ymin = -10,
    ymax = 4,
    alpha = 0, # This was put back to 0.5
    size = .5,
    col = viridis(2)[2]
  ) +
  annotate(
    'text',
    x = 10,
    y = -32,
    label = 'Dashboard area',
    fontface = 'bold', 
    size = 2.5
  ) +
  xlab("Yaw (°)") +
  ylab("Pitch (°)") +
  xlim(-50, 50) +
  scale_y_continuous(limits = c(-32, 20), breaks = seq(-30, 20, 15)) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 11), 
        axis.text.x = element_text(size = 11), 
        axis.title.y = element_text(size = 11), 
        axis.text.y = element_text(size = 11), 
        title = element_text(size = 18),
        plot.title = element_text(size = 15, face = "bold"), 
        strip.text = element_text(face = "bold", size = 10))

n_back_ttc_manual_disp <- n_back_ttc_manual_disp_ttc3 / n_back_ttc_manual_disp_ttc5 + plot_layout(axes = "collect")

# plot saving
ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript_plots/n_back_ttc_manual_disp.tiff"), plot = n_back_ttc_manual_disp, width = 16, height = 16, units = 'cm', dpi = 300, type = 'cairo')

#### predicted posterior means and distribution ####
predicted_draws = empty_grid %>%
  add_predicted_draws(mod_sd_yaw_gaussian)

expected_values = empty_grid %>%
  add_epred_draws(mod_sd_yaw_gaussian)

posterior_sdyaw <- response.vehicle.eye %>%
  dplyr::ungroup() %>%
  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
  ggplot(aes(x = sd_yaw, y = n_back)) +
  stat_pointinterval(aes(x = .epred), data = expected_values, .width = c(.50, .95), position = position_nudge(y = -0.35)) +
  stat_interval(aes(x = .prediction), data = predicted_draws, .width = c(.50, .80, .95, .99)) +
  geom_jitter(data = response.vehicle.eye %>%
  dplyr::ungroup() %>%
  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)), size = 2, height = .05, alpha = .3) +
  #geom_point(conditional_df_fitted[[3]], mapping = aes(x = estimate__, y = n_back), col = "white") +
  scale_y_discrete(labels = c('No N-B','N-B'), guide = guide_axis(angle = 90)) +
  scale_color_brewer("Posterior predictive interval") +
  ggtitle("A") +
  #xlim(.5, 3.5) +
  xlab(expression(SD[YAW]~ "(°)")) +
  ylab(" ") +
  #xlim(0, 2) +
  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
  theme_bw() +
  theme(legend.position = "bottom", legend.direction = "horizontal", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 8, face = "bold"), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

# predicted global mean RTs implied by the model

# setting re_formula = NA tells the function to not use any random effects - here we plot the n-back specific distributions 
grand_mean_ttc_dist <- mod_sd_yaw_gaussian %>% 
  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
                                    n_back = FALSE),
              re_formula = NA)

grand_mean_ttc_dist %>% mean_hdi()

global_mean_ttc_sdyaw <- ggplot(grand_mean_ttc_dist ,aes(x = .epred, y = " ", fill = ttc_criticality_factor)) +
  stat_halfeye(alpha = .5) +
  ylab(NULL) +
  xlab(expression("Predicted mean"~ SD[YAW]~ "(°)")) +
  ggtitle("B") +
  scale_fill_discrete(name = "TTC", labels = c("3 s", "5 s")) +
  xlim(8, 14) +
  theme_bw() +
  theme(legend.position = c(.88, .6), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

# and now we plot the distribution of the difference between n_back and no n-back 
grand_mean_ttc_mer <- mod_sd_yaw_gaussian %>% 
  emmeans(~ ttc_criticality_factor,
          at = list(n_back = FALSE),
          epred = TRUE, re_formula = NA) %>% 
  contrast(method = "revpairwise") %>% 
  gather_emmeans_draws()

grand_mean_ttc_mer %>% mean_hdi()

# Average marginal effect (AME) of TTC on braking RT
MER_ttc_sdyaw <- ggplot(grand_mean_ttc_mer, aes(x = .value, y = " ")) +
  stat_halfeye() +
  ylab(NULL) +
  xlab(expression(MER[SD[YAW]]~ "(°)")) +
  ggtitle("C") +
  scale_fill_discrete(name = "TTC", labels = c("3 s", "5 s")) +
  theme_bw() +
  theme(legend.position = c(.9, .7), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

fig8 <- posterior_sdyaw / (global_mean_ttc_sdyaw  | MER_ttc_sdyaw)

# plot saving
ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript_plots/fig8.tiff"), plot = fig8, width = 16, height = 11, units = 'cm', dpi = 300, type = 'cairo')

## effect of n-back on SD yaw
grand_mean_n_back_dist <- mod_sd_yaw_gaussian %>% 
  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3)),
                                    n_back = c(FALSE, TRUE)),
              re_formula = NA)

grand_mean_n_back_dist %>% mean_hdi()

grand_mean_n_back_mer <- mod_sd_yaw_gaussian %>% 
  emmeans(~ n_back,
          at = list(ttc_criticality_factor = as.factor(3)),
          epred = TRUE, re_formula = NA) %>% 
  contrast(method = "revpairwise") %>% 
  gather_emmeans_draws()

grand_mean_n_back_mer  %>% mean_hdi()
```

## Individual variation of SD of yaw

## TO DO

- MAKE TITLES ON GZE SUBPLOTS A NORMAL SIZE
- PUT ARROWS ON STRIP PLOT
- CLEAN UP CODE SCRIPT FOR PUBLICATION

```{r}
# relative size of  heterogenity effect for 2-back on mu
summary(mod_sd_yaw_gaussian)[["random"]][["ppid"]][2,1] / summary(mod_sd_yaw_gaussian)[["fixed"]][2,1]

# removing outliers and collisions from a specific dataframe
response.vehicle.eye.removed <- response.vehicle.eye %>%
  dplyr::ungroup() %>%
  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt >.15) %>%
  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x), ppid = as.factor(ppid))

# individual effects for SD of yaw during manual driving
ppid.effects <- as.data.frame(ranef(mod_sd_yaw_gaussian)) %>%
  dplyr::select(ppid.Estimate.n_backTRUE) %>%
  dplyr::mutate(ranef = ppid.Estimate.n_backTRUE + summary(mod_sd_yaw_gaussian)[["fixed"]][2,1]) %>%
  tibble::rownames_to_column("ppid")

ppid.effects$x <- 0

# CI interval for average effect
bayes.credible.intervals <- as.data.frame(summary(mod_sd_yaw_gaussian)[["fixed"]][3:4])

# select random effects parameter 
ran.effects <- summary(mod_sd_yaw_gaussian)[["random"]][["ppid"]][2,1]

# strip plot of individual effects
strip_plot <- ggplot() +
  geom_jitter(ppid.effects, mapping = aes(x = x, y = ranef), width = .05, height = 0, size = 4,
              shape = 21, colour = "black", fill = viridis(5)[3], alpha = .95, stroke = 1) +
  scale_y_continuous(limits = c(-4.5, 3), breaks = seq(-4.5, 3, 1.5), labels = label_number(accuracy = 0.1)) +
  ylab(expression("N-back effect on" ~ mu ~ "of" ~ SD[YAW] ~ "during manual driving (°)")) +
  xlab("") + 
  ggtitle("A") +
  xlim(-1, 1) +
  geom_hline(aes(yintercept = bayes.credible.intervals$`l-95% CI`[2], linetype ="95% CI"), size = 1.5,  color = viridis(5)[3]) +
  geom_hline(aes(yintercept = bayes.credible.intervals$`u-95% CI`[2], linetype="95% CI"), size = 1.5,  color = viridis(5)[3]) +
  geom_hline(aes(yintercept = summary(mod_sd_yaw_gaussian)[["fixed"]][2,1], linetype = "beta_1"), size = 1.5, color = "black") +
  geom_hline(aes(yintercept = summary(mod_sd_yaw_gaussian)[["fixed"]][2,1] + 1.96 * ran.effects, linetype = "95% HI"), size = 1.5, color = viridis(5)[2]) +
  geom_hline(aes(yintercept = summary(mod_sd_yaw_gaussian)[["fixed"]][2,1] - 1.96 * ran.effects, linetype = "95% HI"), size = 1.5, color = viridis(5)[2]) +
  scale_linetype_manual(name = " ", values = c(2, 1, 1), labels = c(expression(CI[95]), expression(HI[95]), expression(beta[N])), guide = guide_legend(override.aes = list(color = c(viridis(5)[3], viridis(5)[2], "black")))) +
  scale_fill_manual(name = "Parameter", values = c(viridis(5)[2])) +
   annotate( # increased gaze concentration
    'rect',
    xmin = -.25,
    xmax = .25,
    ymin = -2.49,
    ymax = -2.24,
    alpha = 0.5, # This was put back to 0.5
    fill = turbo(5)[5],
    col = 'black'
  ) +
  annotate( # no difference in gaze concentration
    'rect',
    xmin = -.25,
    xmax = .25,
    ymin = -.1,
    ymax = .15,
    alpha = 0.5, # This was put back to 0.5
    fill = viridis(5)[4],
    col = 'black'
  ) +
  theme_bw() +
  coord_flip() + 
  theme(legend.position = c(.181, .60), panel.grid.major.y = element_blank(), panel.grid.minor.y = element_blank(),legend.key = element_blank(), legend.key.width = unit(0.2, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(), legend.key.size = unit(.05, 'cm'), plot.title = element_text(size = 15, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 7))

# heterogenity intervals for the effect of N-back on SD of yaw during manual driving
summary(mod_sd_yaw_gaussian)[["fixed"]][2,1] + 1.96 * ran.effects
summary(mod_sd_yaw_gaussian)[["fixed"]][2,1] - 1.96 * ran.effects

# participant 3, beta_n = -0.065
p_3 <- ggplot(dat.eye.manual %>%
         dplyr::filter(ppid == 3), mapping = aes(x = yaw, y = pitch)) +
  geom_density_2d(aes(col = ..level..), alpha = .5, binwidth = .00003) +
  facet_wrap(~ n_back, labeller = labeller(n_back = l.labs)) +
  scale_colour_viridis_c(option = "C") +
  ggtitle(label = "B",
          subtitle = "Participant 3," ~ beta[N[14]] ~ "= -.065") +
  xlab("Yaw (°)") +
  ylab("Pitch (°)") +
  xlim(-50, 50) +
  scale_y_continuous(limits = c(-32, 20), breaks = seq(-30, 20, 15)) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 11), 
        axis.text.x = element_text(size = 11), 
        axis.title.y = element_text(size = 11), 
        axis.text.y = element_text(size = 11), 
        title = element_text(size = 18),
        strip.text = element_text(face = "bold", size = 10),
        plot.subtitle = element_text(size = 12, colour = viridis(5)[4]),
        plot.title = element_text(size = 15, face = "bold"))

# participant 14, beta_n = .036
p_14 <- ggplot(dat.eye.manual %>%
         dplyr::filter(ppid == 14), mapping = aes(x = yaw, y = pitch)) +
  geom_density_2d(aes(col = ..level..), alpha = .5, binwidth = .00003) +
  facet_wrap(~ n_back, labeller = labeller(n_back = l.labs)) +
  scale_colour_viridis_c(option = "C") +
  ggtitle(label = " ",
          subtitle = "Participant 14," ~ beta[N[14]] ~ "= .036") +
  xlab("Yaw (°)") +
  ylab("Pitch (°)") +
  xlim(-50, 50) +
  scale_y_continuous(limits = c(-32, 20), breaks = seq(-30, 20, 15)) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 11), 
        axis.text.x = element_text(size = 11), 
        axis.title.y = element_text(size = 11), 
        axis.text.y = element_text(size = 11), 
        title = element_text(size = 18),
        strip.text = element_text(face = "bold", size = 10),
        plot.subtitle = element_text(size = 12, colour = viridis(5)[4]),
        plot.title = element_text(size = 15, face = "bold"))

# participant 7, beta_n = -2.128
p_7 <- ggplot(dat.eye.manual %>%
         dplyr::filter(ppid == 7), mapping = aes(x = yaw, y = pitch)) +
  geom_density_2d(aes(col = ..level..), alpha = .5, binwidth = .00003) +
  facet_wrap(~ n_back, labeller = labeller(n_back = l.labs)) +
  scale_colour_viridis_c(option = "C") +
  ggtitle(label = "C",
          subtitle = "Participant 7," ~ beta[N[7]] ~ "= -2.128") +
  xlab("Yaw (°)") +
  ylab("Pitch (°)") +
  xlim(-50, 50) +
  scale_y_continuous(limits = c(-32, 20), breaks = seq(-30, 20, 15)) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 11), 
        axis.text.x = element_text(size = 11), 
        axis.title.y = element_text(size = 11), 
        axis.text.y = element_text(size = 11), 
        title = element_text(size = 18),
        strip.text = element_text(face = "bold", size = 10),
        plot.subtitle = element_text(size = 12, colour = turbo(5)[5]),
        plot.title = element_text(size = 15, face = "bold"))

# participant 13, beta_n = -2.391
p_13 <- ggplot(dat.eye.manual %>%
         dplyr::filter(ppid == 13), mapping = aes(x = yaw, y = pitch)) +
  geom_density_2d(aes(col = ..level..), alpha = .5, binwidth = .00003) +
  facet_wrap(~ n_back, labeller = labeller(n_back = l.labs)) +
  scale_colour_viridis_c(option = "C") +
  ggtitle(label = " ",
          subtitle = "Participant 13," ~ beta[N[13]] ~ "= -2.391") +
  xlab("Yaw (°)") +
  ylab("Pitch (°)") +
  xlim(-50, 50) +
  scale_y_continuous(limits = c(-32, 20), breaks = seq(-30, 20, 15)) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 11), 
        axis.text.x = element_text(size = 11), 
        axis.title.y = element_text(size = 11), 
        axis.text.y = element_text(size = 11), 
        title = element_text(size = 18),
        strip.text = element_text(face = "bold", size = 10),
        plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 12, colour = turbo(5)[5]))

fig99 <- strip_plot / (p_3 | p_14) / (p_7 | p_13)

ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript_plots/fig99.tiff"), plot = fig99, width = 16, height = 18, units = 'cm', dpi = 300, type = 'cairo')
```

### 2024-08-15 manuscript_and_modelling_plots_takeovers.Rmd
initialing analysis script and data for the analysis

@@
 
-Tidy up longitudinal jerk modelling
-
-Model lateral jerk to see if model fit and inferences are still good (with maximal random effects)
-
-Add random interactions to all the other models
-
-Adjust the plots and tables
-
-Send to co-authors and start on supplemental material.
+Calculate the average absolute lateral accelerations were and see if it correlates with maximum lateral accelerations
+
+Find studies that talk about max decelerations being around 12 m/s^2 and how this makes modelling the response difficult by just taking the max value, but averaging over the all the decleration produces some nice fits - I think it's Gold et al or maybe Radlymayr et al who mentions the max longitudinal metric
+
+Further investigate variance in the effect of N-back on mean deceleration.
+
+Check if a Gaussian produces a better fit than the skew gaussian.
 
 ```{r}
-# distribution of negative longitudinal jerk
 ggplot(response.vehicle.eye %>%
@@
          dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
-         dplyr::mutate(ppid = as.factor(ppid)), mapping = aes(max_long_jerk)) +
+         dplyr::mutate(ppid = as.factor(ppid)), mapping = aes(mean_decel)) +
   geom_histogram() +
   facet_grid(n_back ~ ttc_criticality_factor)
+
+# regularising priors for parameter values
+prior(student_t(5, 9, 2.5)) %>% 
+  parse_dist() %>% 
+  ggplot(aes(xdist = .dist_obj, y = prior)) + 
+  stat_halfeye(.width = c(.5, .99)) +
+  scale_y_discrete(NULL, breaks = NULL, expand = expansion(add = 0.1)) +
+  scale_x_continuous(expression(italic(p)(beta[1]))) +
+  theme_bw()
+
+prior(normal(9, 2)) %>% 
+  parse_dist() %>% 
+  ggplot(aes(xdist = .dist_obj, y = prior)) + 
+  stat_halfeye(.width = c(.5, .99)) +
+  scale_y_discrete(NULL, breaks = NULL, expand = expansion(add = 0.1)) +
+  scale_x_continuous(expression(italic(p)(beta[1]))) +
+  theme_bw()
+
+mean_decel_skewnormal_reg_priors_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/mean_decel_skewnormal_reg_priors_maximal.rds"))
+
+# model of maximum longitudinal jerk with regularising priors. Random effects structure is maximal
+mean_decel_skewnormal_reg_priors_maximal <- brm(data = response.vehicle.eye %>%
+                                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
+                                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
+                                             dplyr::mutate(ppid = as.factor(ppid)),
+                                           family = skew_normal(),
+                                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
+                                                     prior(student_t(3, 0, 2.5), class = "b")),
+                                           bf(mean_decel ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor | ppid)),
+                                           control = list(adapt_delta = 0.99999999999),
+                                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
+                                           file = here::here("takeover_performance_cogload_time_budget/Models/mean_decel_skewnormal_reg_priors_maximal"))
+# summarising model parameters 
+print(summary(mean_decel_skewnormal_reg_priors_maximal), digits = 5)
+describe_posterior(mean_decel_skewnormal_reg_priors_maximal , centrality = "mean")
+
+pp_check(mean_decel_skewnormal_reg_priors_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
+pp_check(mean_decel_skewnormal_reg_priors_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
+
+pp_check(mean_decel_skewnormal_reg_priors_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
+pp_check(mean_decel_skewnormal_reg_priors_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
+
+pp_check(mean_decel_skewnormal_reg_priors_maximal, type = "hist", group = "ttc_criticality_factor")
+
+# model of maximum longitudinal jerk with regularising priors. Random effects structure is maximal
+skew_skew_mix = mixture(family = skew_normal(), family = skew_normal(), order = 'mu')
+
+max_long_jerk_skewnormal_mix_reg_priors_maximal <- brm(data = response.vehicle.eye %>%
+                                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
+                                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
+                                             dplyr::mutate(ppid = as.factor(ppid)),
+                                           family = skew_skew_mix,
+                                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept", dpar = "mu1"),
+                                                prior(student_t(3, 0, 2.5), class = "Intercept", dpar = "mu2"),
+                                                prior(student_t(3, 0, 2.5), class = "b", dpar = "mu1"),
+                                                prior(student_t(3, 0, 2.5), class = "b", dpar = "mu2")),
+                                           max_long_jerk ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor | ppid),
+                                           control = list(adapt_delta = 0.99999999999),
+                                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
+                                           file = here::here("takeover_performance_cogload_time_budget/Models/max_long_jerk_skewnormal_mix_reg_priors_maximal"))
+# summarising model parameters 
+print(summary(max_long_jerk_skewnormal_mix_reg_priors_maximal), digits = 5)
+describe_posterior(max_long_jerk_skewnormal_reg_priors_maximal, centrality = "mean")
+
+pp_check(max_long_jerk_skewnormal_reg_priors_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
+pp_check(max_long_jerk_skewnormal_reg_priors_maximal, type = "stat_grouped", stat = "mean", group = "n_back.x")
+
+pp_check(max_long_jerk_skewnormal_reg_priors_maximal, type = "hist", stat = "mean", group = "n_back.x")
+
+pp_check(max_long_jerk_skewnormal_mix_reg_priors_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
+pp_check(max_long_jerk_skewnormal_mix_reg_priors_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
+
+grand_mean_n_back_dist <- max_long_jerk_skewnormal_reg_priors_maximal %>% 
+  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
+                                    n_back = c(TRUE, FALSE)),
+              re_formula = NA)
+
+grand_mean_n_back_dist %>% mean_hdi()
 
@@
 
-max_long_mixture_weak_priors  <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/max_long_mixture_weak_prior.rds"))
+max_long_mixture_6  <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/max_long_jerk_skewnormal_reg_priors_maximal.rds"))
 
@@
 pp_check(max_long_mixture_6, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-pp_check(max_long_mixture_6, type = "stat_grouped", stat = "mean", group = "n_back")
-
-pp_check(max_long_mixture_6, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
+pp_check(max_long_mixture_6, type = "stat_grouped", stat = "mean", group = "n_back.x")
+
+pp_check(max_long_mixture_6, type = "dens_overlay_grouped", group = "n_back.x", ndraws = 100)
 pp_check(max_long_mixture_6, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
 
-grand_mean_n_back_dist <- max_long_mixture_2_ttc %>% 
-  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5))),
+grand_mean_n_back_dist <- max_long_mixture_6 %>% 
+  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
+                                    n_back.x = c(TRUE, FALSE)),
               re_formula = NA)
@@
 grand_mean_n_back_dist %>% mean_hdi()
-
-# model of maximum longitudinal acceleration with hella weak priors. To check if the model is blowing up cause if lack of priors constraining parameter values
-max_long_jerk_skewnormal_reg_priors_maximal <- brm(data = response.vehicle.eye %>%
-                                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
-                                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
-                                             dplyr::mutate(ppid = as.factor(ppid)),
-                                           family = skew_normal(),
-                                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
-                                                     prior(student_t(3, 0, 2.5), class = "b")),
-                                           max_long_jerk ~ n_back.x * ttc_criticality_factor + (n_back.x * ttc_criticality_factor | ppid),
-                                           control = list(adapt_delta = 0.99999999999),
-                                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
-                                           file = "max_long_jerk_skewnormal_reg_priors_maximal")
-
-print(summary(max_long_jerk_skewnormal_reg_priors_maximal), digits = 5)
-describe_posterior(max_long_jerk_skewnormal_reg_priors_maximal, centrality = "mean")
-
-pp_check(max_long_jerk_skewnormal_reg_priors_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-pp_check(max_long_jerk_skewnormal_reg_priors_maximal, type = "stat_grouped", stat = "mean", group = "n_back.x")
-
-pp_check(max_long_jerk_skewnormal_reg_priors_maximal, type = "hist", stat = "mean", group = "n_back.x")
-
-pp_check(max_long_jerk_skewnormal_reg_priors_maximal, type = "dens_overlay_grouped", group = "n_back.x", ndraws = 100)
-pp_check(max_long_jerk_skewnormal_reg_priors_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
 
@@
 
-# prior for beta_C i.e., the change in max long when TTC = 5 s
-prior(uniform(10, 11)) %>% 
-  parse_dist() %>% 
-  ggplot(aes(xdist = .dist_obj, y = prior)) + 
-  stat_halfeye(.width = c(.5, .99)) +
-  scale_y_discrete(NULL, breaks = NULL, expand = expansion(add = 0.1)) +
-  scale_x_continuous(expression(italic(p)(beta[1]))) +
-  theme_bw()
-
-# regularising priors for the rest of the parameters
-prior(normal(9, 1)) %>% 
-  parse_dist() %>% 
-  ggplot(aes(xdist = .dist_obj, y = prior)) + 
-  stat_halfeye(.width = c(.5, .99)) +
-  scale_y_discrete(NULL, breaks = NULL, expand = expansion(add = 0.1)) +
-  scale_x_continuous(expression(italic(p)(beta[1]))) +
-  theme_bw()
-
-prior(student_t(30, 9, 2.5)) %>% 
-  parse_dist() %>% 
-  ggplot(aes(xdist = .dist_obj, y = prior)) + 
-  stat_halfeye(.width = c(.5, .99)) +
-  scale_y_discrete(NULL, breaks = NULL, expand = expansion(add = 0.1)) +
-  scale_x_continuous(expression(italic(p)(beta[1]))) +
-  theme_bw()
-
+d <- max_long_mixture_6$data
+
+ggplot(d, mapping = aes(max_long_jerk)) +
+  geom_histogram() +
+  facet_grid(n_back.x ~ ttc_criticality_factor)
 ```
@@
   geom_histogram(aes(fill = as.factor(n_back)), alpha = 0.5, bins = 50, col = "black") +
-  facet_wrap(~ttc_criticality.x)
+  facet_grid(n_back ~ttc_criticality.x)
+
+ggplot(response.vehicle.eye %>%
+         dplyr::filter(rt.outlier == FALSE, ho.rt != 0, collision == 0), mapping = aes(x = mean_lat_acc)) +
+  geom_histogram(aes(fill = as.factor(n_back)), alpha = 0.5, bins = 50, col = "black") +
+  facet_grid(n_back ~ttc_criticality.x)
 

### 2024-08-15 manuscript_and_modelling_plots_takeovers.Rmd
model plots and code for response time metrics

@@
 
-# Modelling: Braking RT - model fitting
+# Braking RT - model fitting
 
@@
 ```{r}
-# load model
-mod_braking_rt_bayesian_shifted_lognormal_ttc_slope <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/braking_rt_shifted_log_ttc_slope_priors.rds"))
+# loading model
+braking_rt_shifted_lognormal_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/braking_rt_shifted_lognormal_maximal.rds"))
 
 # adding a random slope for the criticality of the effect
-mod_braking_rt_bayesian_shifted_lognormal_ttc_slope <- brm(data = response.vehicle.eye %>% 
+braking_rt_shifted_lognormal_maximal <- brm(data = response.vehicle.eye %>%
                                               dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
@@
                                             family = shifted_lognormal(),
-                                                           rt ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor| ppid),
+                                            bf(rt ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor| ppid)),
                                             prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
@@
                                             iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
-                                                                     file = "braking_rt_shifted_log_ttc_slope_priors")
+                                            file = here::here("takeover_performance_cogload_time_budget/Models/braking_rt_shifted_lognormal_maximal.rds"))
+
+print(summary(braking_rt_shifted_lognormal_maximal), digits = 5)
+describe_posterior(braking_rt_shifted_lognormal_maximal, centrality = "mean")
 
 # posterior predictive checks
-pp_check(mod_braking_rt_bayesian_shifted_lognormal_ttc_slope, type = "dens_overlay_grouped", group = "n_back", ndraws = 100) +
-  ggtitle("shifted_lognormal")
-
-print(summary(mod_braking_rt_bayesian_shifted_lognormal_ttc_slope), digits = 5)
-describe_posterior(mod_braking_rt_bayesian_shifted_lognormal_ttc_slope, centrality = "mean")
-```
-
-# Modelling: Braking RT - Visualising posterior draws and means
+pp_check(braking_rt_shifted_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
+pp_check(braking_rt_shifted_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
+
+# posterior predictive checks
+pp_check(braking_rt_shifted_lognormal_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100) 
+pp_check(braking_rt_shifted_lognormal_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100) 
+```
+
+# Braking RT - model predictions
+
+Calculating predicted braking RT implied by the model parameters, and the average effect of time budget on braking RT
+
+```{r}
+# average effect of TTC on braking RT 
+braking_rt_MER_TTC <- braking_rt_shifted_lognormal_maximal %>% 
+  emmeans(~ ttc_criticality_factor,
+          at = list(n_back = FALSE),
+          epred = TRUE, re_formula = NA) %>% 
+  contrast(method = "revpairwise") %>% 
+  gather_emmeans_draws()
+
+braking_rt_MER_TTC  %>% mean_hdi()
+
+# predicted global mean RTs implied by the model # setting re_formula = NA tells the function to not use any random effects - here we plot the TTC specific distributions 
+predicted_braking_rt_ttc <- braking_rt_shifted_lognormal_maximal %>% 
+  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
+                                    n_back = FALSE),
+              re_formula = NA)
+
+predicted_braking_rt_ttc %>% mean_hdi()
+```
+
+# Braking RT - visualising posterior draws and means
 
@@
 predicted_draws = empty_grid %>%
-  add_predicted_draws(mod_braking_rt_bayesian_shifted_lognormal_ttc_slope)
+  add_predicted_draws(braking_rt_shifted_lognormal_maximal)
 
@@
 expected_values = empty_grid %>%
-  add_epred_draws(mod_braking_rt_bayesian_shifted_lognormal_ttc_slope)
+  add_epred_draws(braking_rt_shifted_lognormal_maximal)
 
@@
   ggtitle("A") +
-  #xlim(.5, 3.5) +
+  xlim(.5, 3.5) +
   xlab(expression(RT[B]~ "(s)")) +
   ylab(" ") +
-  scale_x_continuous(breaks = seq(1, 3, .5), labels = label_number(accuracy = .5)) +
+  #scale_x_continuous(breaks = seq(.5, 3, .5), labels = label_number(accuracy = .5)) +
   facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
@@
 
-# predicted gloabl mean RTs implied by the model
-
-# setting re_formula = NA tells the function to not use any random effects - here we plot the n-back specific distributions 
-grand_mean_n_back_dist <- mod_braking_rt_bayesian_shifted_lognormal_ttc_slope %>% 
-  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
-                                    n_back = FALSE),
-              re_formula = NA)
-
-grand_mean_n_back_dist %>% mean_hdi()
-
-global_mean_ttc_braking_rt <- ggplot(grand_mean_n_back_dist ,aes(x = .epred, y = " ", fill = ttc_criticality_factor)) +
+predicted_braking_rt_ttc_plot <- ggplot(predicted_braking_rt_ttc, aes(x = .epred, y = " ", fill = ttc_criticality_factor)) +
   stat_halfeye(alpha = .5) +
   ylab(NULL) +
-  xlab(expression("Predicted mean"~ RT[B]~ "(s)")) +
+  xlab(expression("Predicted" ~ mu ~ "of" ~ RT[B]~ "(s)")) +
   ggtitle("B") +
@@
 
-# and now we plot the distribution of the difference between n_back and no n-back 
-grand_mean_n_back_mer <- mod_braking_rt_bayesian_shifted_lognormal_ttc_slope %>% 
-  emmeans(~ ttc_criticality_factor,
-          at = list(n_back = FALSE),
-          epred = TRUE, re_formula = NA) %>% 
-  contrast(method = "revpairwise") %>% 
-  gather_emmeans_draws()
-
-grand_mean_n_back_mer  %>% mean_hdi()
-
 # Marginal Effects at Representative values (MER) of TTC on braking RT
-MER_ttc_braking_rt <- ggplot(grand_mean_n_back_mer, aes(x = .value, y = " ")) +
+braking_rt_MER_TTC_plot <- ggplot(braking_rt_MER_TTC, aes(x = .value, y = " ")) +
   stat_halfeye() +
@@
 
-fig1 <- posterior_braking_rt / (global_mean_ttc_braking_rt | MER_ttc_braking_rt)
+fig4 <- posterior_braking_rt / (predicted_braking_rt_ttc_plot | braking_rt_MER_TTC_plot)
 
 # plot saving
-ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript_plots/fig1.tiff"), plot = fig1, width = 16, height = 11, units = 'cm', dpi = 300, type = 'cairo')
-```
-
-# Modelling: hands-on time
+ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig4.tiff"), plot = fig4, width = 16, height = 11, units = 'cm', dpi = 300, type = 'cairo')
+```
+
+# Hands-on time: model fitting
 
@@
 
-# load model
-mod_ho_rt_bayesian_shifted_lognormal_ttc_slope <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/ho_rt_shifted_log_ttc_slope_priors.rds"))
+# loading model
+handson_rt_shifted_lognormal_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/handson_rt_shifted_lognormal_maximal.rds"))
 
 # adding a random slope for the criticality of the effect
-mod_ho_rt_bayesian_shifted_lognormal_ttc_slope <- brm(data = response.vehicle.eye %>%
+handson_rt_shifted_lognormal_maximal <- brm(data = response.vehicle.eye %>%
                                                    dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>% 
@@
                                                    family = shifted_lognormal(), 
-                                                   ho.rt ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor| ppid),
+                                                   bf(ho.rt ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor| ppid)),
                                                    prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
@@
                                                    iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13, 
-                                                   file = "ho_rt_shifted_log_ttc_slope_priors")
-
-print(summary(mod_ho_rt_bayesian_shifted_lognormal_ttc_slope), digits = 5)
-describe_posterior(mod_ho_rt_bayesian_shifted_lognormal_ttc_slope)
-
+                                                   file = here::here("takeover_performance_cogload_time_budget/Models/handson_rt_shifted_lognormal_maximal"))
+
+# posterior predictive checks
+pp_check(handson_rt_shifted_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
+pp_check(handson_rt_shifted_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
+
+# posterior predictive checks
+pp_check(handson_rt_shifted_lognormal_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100) 
+pp_check(handson_rt_shifted_lognormal_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
+
+```
+
+# Hands-on steering time: model predictions
+
+```{r}
+print(summary(handson_rt_shifted_lognormal_maximal), digits = 5)
+describe_posterior(handson_rt_shifted_lognormal_maximal)
+
+#### Global mean effect of TTC #### # setting re_formula = NA tells the function to not use any random effects - here we plot the n-back specific distributions 
+predicted_ho_rt_ttc <- handson_rt_shifted_lognormal_maximal %>% 
+  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
+                                    n_back = FALSE),
+              re_formula = NA)
+
+predicted_ho_rt_ttc %>% mean_hdi()
+
+# and now we plot the distribution of the difference between n_back and no n-back 
+ho_rt_MER_TTC <- handson_rt_shifted_lognormal_maximal %>% 
+  emmeans(~ ttc_criticality_factor,
+          at = list(n_back = FALSE),
+          epred = TRUE, re_formula = NA) %>% 
+  contrast(method = "revpairwise") %>% 
+  gather_emmeans_draws()
+
+ho_rt_MER_TTC %>% mean_hdi()
+```
+
+# Hands-on steering time - visualising posterior draws and means
+
+```{r}
 #### predicted posterior means and distribution ####
 predicted_draws = empty_grid %>%
-  add_predicted_draws(mod_ho_rt_bayesian_shifted_lognormal_ttc_slope)
+  add_predicted_draws(handson_rt_shifted_lognormal_maximal)
 
 expected_values = empty_grid %>%
-  add_epred_draws(mod_ho_rt_bayesian_shifted_lognormal_ttc_slope)
+  add_epred_draws(handson_rt_shifted_lognormal_maximal)
 
@@
   ggtitle("A") +
-  #xlim(.5, 3.5) +
+  xlim(.5, 3.5) +
   xlab(expression(RT[HO]~ "(s)")) +
   ylab(" ") +
-  scale_x_continuous(limits = c(0, 3.5), breaks = seq(0, 3, .5), labels = label_number(accuracy = .5)) +
+  #scale_x_continuous(limits = c(0, 3.5), breaks = seq(0, 3, .5), labels = label_number(accuracy = .5)) +
   facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
@@
 
-#### Global mean effect of TTC ####
-
-# setting re_formula = NA tells the function to not use any random effects - here we plot the n-back specific distributions 
-grand_mean_n_back_dist_hort <- mod_ho_rt_bayesian_shifted_lognormal_ttc_slope %>% 
-  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
-                                    n_back = FALSE),
-              re_formula = NA)
-
-grand_mean_n_back_dist_hort %>% mean_hdi()
-
-global_mean_ttc_ho_rt <- ggplot(grand_mean_n_back_dist_hort, aes(x = .epred, y = " ", fill = ttc_criticality_factor)) +
+# predicted hands-on time 
+predicted_ho_rt_ttc_plot <- ggplot(predicted_ho_rt_ttc, aes(x = .epred, y = " ", fill = ttc_criticality_factor)) +
   stat_halfeye(alpha = .5) +
   ylab(NULL) +
-  xlab(expression("Predicted mean"~ RT[HO]~ "(s)")) +
+  xlab(expression("Predicted" ~ mu ~ "of" ~ RT[HO]~ "(s)")) +
   ggtitle("B") +
@@
 
-# and now we plot the distribution of the difference between n_back and no n-back 
-grand_mean_n_back_mer_hort <- mod_ho_rt_bayesian_shifted_lognormal_ttc_slope %>% 
-  emmeans(~ ttc_criticality_factor,
-          at = list(n_back = FALSE),
-          epred = TRUE, re_formula = NA) %>% 
-  contrast(method = "revpairwise") %>% 
-  gather_emmeans_draws()
-
-grand_mean_n_back_mer_hort %>% mean_hdi()
-
 # MER of TTC on hands on RT
-MER_ttc_ho_rt <- ggplot(grand_mean_n_back_mer_hort, aes(x = .value, y = " ")) +
+ho_rt_MER_TTC_plot <- ggplot(ho_rt_MER_TTC, aes(x = .value, y = " ")) +
   stat_halfeye() +
@@
 
-fig2 <- posterior_ho_rt / (global_mean_ttc_ho_rt | MER_ttc_ho_rt)
+fig5 <- posterior_ho_rt / (predicted_ho_rt_ttc_plot | ho_rt_MER_TTC_plot)
 
 # plot saving
-ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript_plots/fig2.tiff"), plot = fig2, width = 16, height = 11, units = 'cm', dpi = 300, type = 'cairo')
-```
-
-# Difference between hands on time and braking reaction time
-
-```{r}
-response.vehicle.eye.removed <- response.vehicle.eye %>%
-  dplyr::ungroup() %>%
-  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0) %>%
-  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x), ppid = as.factor(ppid))
-
-effects_existing_groups_braking_rt <- mod_braking_rt_bayesian_shifted_lognormal_ttc_slope %>%
-  emmeans(~ ttc_criticality_factor + ppid,
-          at = list(n_back = FALSE,
-                    ppid = levels(as.factor(response.vehicle.eye.removed$ppid))),
-          epred = TRUE, re_formula = NULL) %>% 
-  contrast(method = "revpairwise", by = "ppid") %>% 
-  gather_emmeans_draws() %>%
-  mean_hdi()
-
-braking_rt_mer_drivers <- effects_existing_groups_braking_rt %>%
-  ggplot() +
-  geom_point(mapping = aes(x = .value, y = ppid)) +
-  geom_errorbarh(mapping = aes(x = .value, y = ppid, xmin = .lower, xmax = .upper), height = .5) +
-  geom_vline(mapping = aes(xintercept = 0), linetype = "dashed", col = "red") + 
-  xlim(-1, 3) +
-  ggtitle("A") +
-  ylab("Drivers") +
-  xlab(expression(italic(BRT[MER])~ "of TTC (s) for each driver")) +
-  theme_bw() +
-  theme(legend.position = c(.9, .7), axis.title.x = element_text(size = 12), axis.text.x = element_text(size = 12), axis.title.y = element_text(size = 12), axis.text.y = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10)) +
-  expand_limits(y = c(-5, 20))
-
-effects_existing_groups_ho_rt <- mod_ho_rt_bayesian_shifted_lognormal_ttc_slope %>%
-  emmeans(~ ttc_criticality_factor + ppid,
-          at = list(n_back = FALSE,
-                    ppid = levels(as.factor(response.vehicle.eye.removed$ppid))),
-          epred = TRUE, re_formula = NULL) %>% 
-  contrast(method = "revpairwise", by = "ppid") %>% 
-  gather_emmeans_draws() %>%
-  mean_hdi()
-
-ho_rt_mer_drivers <- effects_existing_groups_ho_rt %>%
-  ggplot() +
-  geom_point(mapping = aes(x = .value, y = ppid)) +
-  geom_errorbarh(mapping = aes(x = .value, y = ppid, xmin = .lower, xmax = .upper), height = .5) +
-  geom_vline(mapping = aes(xintercept = 0), linetype = "dashed", col = "red") +
-  xlim(-1, 3) +
-  ggtitle("B") +
-  xlab(expression(italic(HORT[MER])~ "of TTC (s) for each driver")) +
-  ylab("Drivers") +
-  theme_bw() +
-  theme(legend.position = c(.9, .7), axis.title.x = element_text(size = 12), axis.text.x = element_text(size = 12), axis.title.y = element_text(size = 12), axis.text.y = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10)) +
-  expand_limits(y = c(-5, 20))
-
-fig3 <- braking_rt_mer_drivers / ho_rt_mer_drivers
-
-# plot saving
-ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript_plots/fig3.tiff"), plot = fig3, width = 17, height = 15, units = 'cm', dpi = 300, type = 'cairo')
-```
-
-## Modelling - SD of SWA
-
-```{r}
-
-# load model
-mod_sd_steer_bayesian_lognormal_priors <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/sd_steer_lognormal_priors.rds"))
-
-# sd of steering variance with regularising priors
-mod_sd_steer_bayesian_lognormal_priors <- brm(data = response.vehicle.eye %>%
-                                         dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>% 
-                                         dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>% 
-                                         dplyr::mutate(ppid = as.factor(ppid)),
-                                       family = lognormal(),
-                                       sd_steer ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor| ppid),
-                                       prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
-                                                 prior(student_t(3, 0, 2.5), class = "b")),
-                                       iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
-                                       file = "sd_steer_lognormal_priors")
-
-print(summary(mod_sd_steer_bayesian_lognormal_priors), digits = 5)
-describe_posterior(mod_sd_steer_bayesian_lognormal_priors, centrality = "mean")
-
-# posterior predictive checks
-pp_check(mod_sd_steer_bayesian_lognormal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
-
-# sd of steering variance with flat priors?
-mod_sd_steer_bayesian_lognormal_flat_priors <- brm(data = response.vehicle.eye %>%
-                                                     dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>% 
-                                                     dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
-                                                     dplyr::mutate(ppid = as.factor(ppid)),
-                                                   family = lognormal(), 
-                                                   sd_steer ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor| ppid),
-                                                   iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
-                                                   file = "sd_steer_lognormal")
-
-# logit model with weakly informative priors
-prior(student_t(3, 0, 2.5)) %>% 
-  parse_dist() %>% 
-  ggplot(aes(xdist = .dist_obj, y = prior)) + 
-  stat_halfeye(.width = c(.5, .99)) +
-  scale_y_discrete(NULL, breaks = NULL, expand = expansion(add = 0.1)) +
-  scale_x_continuous(expression(italic(p)(beta[1]))) +
-  theme_bw() +xlim(-20, 20)
-
-prior(cauchy(0, 2.5)) %>% 
-  parse_dist() %>% 
-  ggplot(aes(xdist = .dist_obj, y = prior)) + 
-  stat_halfeye(.width = c(.5, .99)) +
-  scale_y_discrete(NULL, breaks = NULL, expand = expansion(add = 0.1)) +
-  scale_x_continuous(expression(italic(p)(beta[1]))) +
-  theme_bw() +
-  xlim(-20, 20)
-
-print(summary(mod_sd_steer_bayesian_lognormal_flat_priors), digits = 5)
-describe_posterior(mod_sd_steer_bayesian_lognormal_flat_priors)
-
-### effect of TTC s###
-grand_mean_ttc_sd_steer <- mod_sd_steer_bayesian_lognormal_priors %>% 
-  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
-                                    n_back = FALSE),
-              re_formula = NA)
-
-grand_mean_ttc_sd_steer %>% mean_hdi()
-
-# and now we plot the distribution of the difference between n_back and no n-back 
-grand_mean_ttc_ame_sd_steer <- mod_sd_steer_bayesian_lognormal_priors %>% 
-  emmeans(~ ttc_criticality_factor,
-          at = list(n_back = FALSE),
-          epred = TRUE, re_formula = NA) %>% 
-  contrast(method = "revpairwise") %>% 
-  gather_emmeans_draws()
-
-grand_mean_ttc_ame_sd_steer %>% mean_hdi()
-
-#### effect of n-back ###
-grand_mean_n_back_sd_steer <- mod_sd_steer_bayesian_lognormal_priors %>% 
-  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3)),
-                                    n_back = c(FALSE, TRUE)),
-              re_formula = NA)
-
-grand_mean_n_back_sd_steer %>% mean_hdi()
-
-grand_mean_n_back_ame_sd_steer <- mod_sd_steer_bayesian_lognormal_priors %>% 
-  emmeans(~ n_back,
-          at = list(ttc_criticality_factor = as.factor(3)),
-          epred = TRUE, re_formula = NA) %>% 
-  contrast(method = "revpairwise") %>% 
-  gather_emmeans_draws()
-
-grand_mean_n_back_ame_sd_steer %>% mean_hdi()
-
-```
-
-## Modelling - longituindal accelerations
+ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig5.tiff"), plot = fig5, width = 16, height = 11, units = 'cm', dpi = 300, type = 'cairo')
+```
+
+## Modelling - mean decelerations
 
@@
   geom_histogram() +
-  facet_grid(n_back ~ ttc_criticality_factor)
+  facet_grid(~ttc_criticality_factor)
 
@@
 
-# model of maximum longitudinal jerk with regularising priors. Random effects structure is maximal
+# modelling average deceleration with regularising priors. Random effects structure is maximal. Distribution family is skew-normal. 
 mean_decel_skewnormal_reg_priors_maximal <- brm(data = response.vehicle.eye %>%
@@
                                            file = here::here("takeover_performance_cogload_time_budget/Models/mean_decel_skewnormal_reg_priors_maximal"))
+
 # summarising model parameters 
@@
 
-pp_check(mean_decel_skewnormal_reg_priors_maximal, type = "hist", group = "ttc_criticality_factor")
-
-# model of maximum longitudinal jerk with regularising priors. Random effects structure is maximal
-skew_skew_mix = mixture(family = skew_normal(), family = skew_normal(), order = 'mu')
-
-max_long_jerk_skewnormal_mix_reg_priors_maximal <- brm(data = response.vehicle.eye %>%
+d <- pp_check(mean_decel_skewnormal_reg_priors_maximal, type = "hist", group = "ttc_criticality_factor")
+
+ggplot(d[["data"]], mapping = aes(value)) +
+  geom_histogram(aes(fill = as.factor(is_y))) +
+  facet_wrap(~ rep_id)
+
+# modelling average deceleration with regularising priors. Random effects structure is maximal. Distribution family is Gaussian.
+mean_decel_gaussian_reg_priors_maximal <- brm(data = response.vehicle.eye %>%
                                              dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
@@
                                              dplyr::mutate(ppid = as.factor(ppid)),
-                                           family = skew_skew_mix,
-                                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept", dpar = "mu1"),
-                                                prior(student_t(3, 0, 2.5), class = "Intercept", dpar = "mu2"),
-                                                prior(student_t(3, 0, 2.5), class = "b", dpar = "mu1"),
-                                                prior(student_t(3, 0, 2.5), class = "b", dpar = "mu2")),
-                                           max_long_jerk ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor | ppid),
+                                           family = gaussian(),
+                                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
+                                                     prior(student_t(3, 0, 2.5), class = "b")),
+                                           bf(mean_decel ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor | ppid)),
                                            control = list(adapt_delta = 0.99999999999),
                                            iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
-                                           file = here::here("takeover_performance_cogload_time_budget/Models/max_long_jerk_skewnormal_mix_reg_priors_maximal"))
+                                           file = here::here("takeover_performance_cogload_time_budget/Models/mean_decel_gaussian_reg_priors_maximal"))
 # summarising model parameters 
-print(summary(max_long_jerk_skewnormal_mix_reg_priors_maximal), digits = 5)
-describe_posterior(max_long_jerk_skewnormal_reg_priors_maximal, centrality = "mean")
-
-pp_check(max_long_jerk_skewnormal_reg_priors_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-pp_check(max_long_jerk_skewnormal_reg_priors_maximal, type = "stat_grouped", stat = "mean", group = "n_back.x")
-
-pp_check(max_long_jerk_skewnormal_reg_priors_maximal, type = "hist", stat = "mean", group = "n_back.x")
-
-pp_check(max_long_jerk_skewnormal_mix_reg_priors_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
-pp_check(max_long_jerk_skewnormal_mix_reg_priors_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
-
-grand_mean_n_back_dist <- max_long_jerk_skewnormal_reg_priors_maximal %>% 
-  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
-                                    n_back = c(TRUE, FALSE)),
-              re_formula = NA)
-
-grand_mean_n_back_dist %>% mean_hdi()
-
-max_long_skewnormal_hella_weak_priors <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/max_long_skewnormal_hella_weak.rds"))
-
-# model of maximum longitudinal acceleration with hella weak priors. To check if the model is blowing up cause if lack of priors constraining parameter values
-max_long_skewnormal_hella_weak_priors <- brm(data = response.vehicle.eye %>%
-                                               dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
-                                               dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
-                                               dplyr::mutate(ppid = as.factor(ppid)),
-                                      family = skew_normal(),
-                                      prior = c(prior(normal(0, 100), class = "Intercept"),
-                                                prior(normal(0, 100), class = "b")),
-                                      max_long ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor | ppid),
-                                      control = list(adapt_delta = 0.99999999999),
-                                      iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
-                                      file = "max_long_skewnormal_hella_weak")
-
-grand_mean_n_back_dist <- max_long_skewnormal_hella_weak_priors %>% 
-  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
-                                    n_back = c(TRUE, FALSE)),
-              re_formula = NA)
-
-grand_mean_n_back_dist %>% mean_hdi()
-
-print(summary(max_long_skewnormal_hella_weak_priors), digits = 5)
-describe_posterior(max_long_skewnormal_hella_weak_priors, centrality = "mean")
-
-pp_check(max_long_skewnormal_hella_weak_priors, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
-
-pp_check(max_long_skewnormal_hella_weak_priors, type = "stat_grouped", stat = "mean", group = "n_back")
-pp_check(max_long_skewnormal_hella_weak_priors, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-
-pp_check(max_long_skewnormal_hella_weak_priors, type = "stat_2d", stat = c("max", "min"))
-
-max_long_skewnormal_kinda_weak_priors <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/max_long_skewnormal_kinda_weak.rds"))
-
-# model of maximum longitudinal acceleration with kinda weak priors. Do parameter values still make sense ruling out really extreme values. 
-max_long_skewnormal_kinda_weak_priors <- brm(data = response.vehicle.eye %>%
-                                               dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
-                                               dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
-                                               dplyr::mutate(ppid = as.factor(ppid)),
-                                      family = skew_normal(),
-                                      prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
-                                                prior(student_t(3, 0, 2.5), class = "b")),
-                                      max_long ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor | ppid),
-                                      control = list(adapt_delta = 0.99999999999),
-                                      iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
-                                      file = "max_long_skewnormal_kinda_weak")
-
-print(summary(max_long_skewnormal_kinda_weak_priors), digits = 5)
-describe_posterior(max_long_skewnormal_kinda_weak_priors, centrality = "mean")
-
-pp_check(max_long_skewnormal_kinda_weak_priors, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
-pp_check(max_long_skewnormal_kinda_weak_priors, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
-
-pp_check(max_long_skewnormal_kinda_weak_priors, type = "stat_grouped", stat = "mean", group = "n_back")
-pp_check(max_long_skewnormal_kinda_weak_priors, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-
-pp_check(max_long_skewnormal_specific_priors, type = "stat_2d", stat = c("max", "min"))
-
-grand_mean_n_back_dist <- max_long_skewnormal_kinda_weak_priors %>% 
-  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
-                                    n_back = c(TRUE, FALSE)),
-              re_formula = NA)
-
-grand_mean_n_back_dist %>% mean_hdi()
-
-# model of maximum longitudinal acceleration with kinda weak priors. Including an interaction in the random effects
-max_long_skewnormal_kinda_weak_priors_maximal <- brm(data = response.vehicle.eye %>%
-                                               dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
-                                               dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
-                                               dplyr::mutate(ppid = as.factor(ppid)),
-                                      family = skew_normal(),
-                                      prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
-                                                prior(student_t(3, 0, 2.5), class = "b")),
-                                      max_long ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor | ppid),
-                                      control = list(adapt_delta = 0.99999999999),
-                                      iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
-                                      file = "max_long_skewnormal_kinda_weak_maximal")
-
-print(summary(max_long_skewnormal_kinda_weak_priors_maximal), digits = 5)
-describe_posterior(max_long_skewnormal_kinda_weak_priors_maximal, centrality = "mean")
-
-pp_check(max_long_skewnormal_kinda_weak_priors_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
-
-ggplot() +
-  geom_vline(response.vehicle.eye %>%
-               dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
-               dplyr::group_by(n_back) %>%
-               dplyr::summarise(m = mean(max_long)), mapping = aes(xintercept = m)) +
-  geom_histogram(pp_n_back_data$data %>%
-                   dplyr::mutate(n_back = group), mapping = aes(x = value)) +
-  facet_wrap(~ n_back)
-
-pp_check(max_long_skewnormal_kinda_weak_priors_maximal, type = "stat_grouped", stat = "median", group = "ttc_criticality_factor")
-
-pp_check(max_long_skewnormal_kinda_weak_priors_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
-pp_check(max_long_skewnormal_kinda_weak_priors_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
-
-grand_mean_n_back_dist <- max_long_skewnormal_kinda_weak_priors_maximal %>% 
-  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
-                                    n_back = c(TRUE, FALSE)),
-              re_formula = NA)
-
-grand_mean_n_back_dist %>% mean_hdi()
-
-max_long_laplace_kinda_weak_priors_maximal <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/max_long_asym_laplace_kinda_weak_maximal.rds"))
-
-# model of maximum longitudinal acceleration with kinda weak priors. Including an interaction in the random effects
-max_long_laplace_kinda_weak_priors_maximal <- brm(data = response.vehicle.eye %>%
-                                               dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
-                                               dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
-                                               dplyr::mutate(ppid = as.factor(ppid)),
-                                      family = asym_laplace(),
-                                      prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
-                                                prior(student_t(3, 0, 2.5), class = "b")),
-                                      max_long ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor | ppid),
-                                      control = list(adapt_delta = 0.99999999999),
-                                      iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
-                                      file = "max_long_asym_laplace_kinda_weak_maximal")
-
-print(summary(max_long_laplace_kinda_weak_priors_maximal), digits = 5)
-describe_posterior(max_long_laplace_kinda_weak_priors_maximal, centrality = "mean")
-
-grand_mean_n_back_dist <- max_long_laplace_kinda_weak_priors_maximal %>% 
-  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
-                                    n_back = c(TRUE, FALSE)),
-              re_formula = NA)
-
-grand_mean_n_back_dist %>% mean_hdi()
-
-pp_check(max_long_laplace_kinda_weak_priors_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
-pp_check(max_long_laplace_kinda_weak_priors_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
-
-pp_check(max_long_laplace_kinda_weak_priors_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-pp_check(max_long_laplace_kinda_weak_priors_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
-
-# model of maximum longitudinal acceleration with kinda weak priors.
-Including an interaction in the random effects - seems like a more specific prior helps the model fit.
-Work out what the parameters are for laplace and work out if we can get more specific?
-Also toy around with removing interaction random effect?
-max_long_laplace_specific_priors <- brm(data = response.vehicle.eye %>%
-                                               dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
-                                               dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
-                                               dplyr::mutate(ppid = as.factor(ppid)),
-                                      family = asym_laplace(),
-                                      prior = c(prior(normal(9, .5), class = "Intercept"),
-                                                prior(normal(.5, .1), class = "b", coef = "ttc_criticality_factor5"),
-                                                prior(student_t(3, 0, 2.5), class = "b", coef = "n_backTRUE"),
-                                                prior(student_t(3, 0, 2.5), class = "b", coef = "n_backTRUE:ttc_criticality_factor5")),
-                                      max_long ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor | ppid),
-                                      control = list(adapt_delta = 0.99999999999),
-                                      iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
-                                      file = "max_long_laplace_specific_priors")
-
-grand_mean_n_back_dist <- max_long_laplace_specific_priors %>% 
-  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
-                                    n_back = c(TRUE, FALSE)),
-              re_formula = NA)
-
-grand_mean_n_back_dist %>% mean_hdi()
-
-print(summary(max_long_laplace_specific_priors), digits = 5)
-describe_posterior(max_long_laplace_specific_priors, centrality = "mean")
-
-pp_check(max_long_laplace_specific_priors, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-pp_check(max_long_laplace_specific_priors, type = "stat_grouped", stat = "mean", group = "n_back")
-
-pp_check(max_long_laplace_specific_priors, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
-pp_check(max_long_laplace_specific_priors, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
-
-# model of maximum longitudinal acceleration with kinda weak priors. Including an interaction in the random effects
-max_long_laplace_kinda_weak_priors <- brm(data = response.vehicle.eye %>%
-                                               dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
-                                               dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
-                                               dplyr::mutate(ppid = as.factor(ppid)),
-                                      family = asym_laplace(),
-                                      prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
-                                                prior(student_t(3, 0, 2.5), class = "b")),
-                                      max_long ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor | ppid),
-                                      control = list(adapt_delta = 0.99999999999),
-                                      iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
-                                      file = "max_long_asym_laplace_kinda_weak")
-
-print(summary(max_long_laplace_specific_priors), digits = 5)
-describe_posterior(max_long_laplace_specific_priors, centrality = "mean")
-
-pp_check(max_long_laplace_kinda_weak_priors, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-pp_check(max_long_laplace_kinda_weak_priors, type = "stat_grouped", stat = "mean", group = "n_back")
-
-pp_check(max_long_laplace_kinda_weak_priors, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
-pp_check(max_long_laplace_kinda_weak_priors, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
-
-# prior for beta_0 i.e., when ttc = 3, and N-back = FALSE. max decelerations typically do not exceed 11 m/s^2 so the prior distribution for TTC = 3 should reflect this. 
-prior(normal(9, .5)) %>% 
-  parse_dist() %>% 
-  ggplot(aes(xdist = .dist_obj, y = prior)) + 
-  stat_halfeye(.width = c(.5, .99)) +
-  scale_y_discrete(NULL, breaks = NULL, expand = expansion(add = 0.1)) +
-  scale_x_continuous(expression(italic(p)(beta[1]))) +
-  theme_bw()
-
-# model of maximum longitudinal acceleration with kinda weak priors. Including an interaction in the random effects
-max_long_laplace_specific_priors <- brm(data = response.vehicle.eye %>%
-                                               dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
-                                               dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
-                                               dplyr::mutate(ppid = as.factor(ppid)),
-                                      family = asym_laplace(),
-                                      prior = c(prior(normal(0, 50), class = "Intercept"),
-                                                prior(normal(0, 50), class = "b")),
-                                      max_long ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor | ppid),
-                                      control = list(adapt_delta = 0.99999999999),
-                                      iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
-                                      file = "max_long_laplace_hella_weak_normal_0_50")
-
-print(summary(max_long_laplace_specific_priors), digits = 5)
-describe_posterior(max_long_laplace_normal_0_5, centrality = "mean")
-
-pp_check(max_long_laplace_hella_weak_normal_0_50, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-pp_check(max_long_laplace_hella_weak_normal_0_50, type = "stat_grouped", stat = "mean", group = "n_back")
-
-pp_check(max_long_laplace_hella_weak_normal_0_50, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
-pp_check(max_long_laplace_hella_weak_normal_0_50, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
-
-grand_mean_n_back_dist <- max_long_laplace_hella_weak %>% 
-  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
-                                    n_back = c(TRUE, FALSE)),
-              re_formula = NA)
-
-grand_mean_n_back_dist %>% mean_hdi()
-
-max_long_laplace_hella_weak <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/max_long_laplace_hella_weak.rds"))
-
-max_long_laplace_normal_0_5 <- brm(data = response.vehicle.eye %>%
-                                               dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
-                                               dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
-                                               dplyr::mutate(ppid = as.factor(ppid)),
-                                      family = asym_laplace(),
-                                      prior = c(prior(normal(0, 5), class = "Intercept"),
-                                                prior(normal(0, 5), class = "b")),
-                                      max_long ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor | ppid),
-                                      control = list(adapt_delta = 0.99999999999),
-                                      iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
-                                      file = "max_long_laplace_normal_0_5")
-
-print(summary(max_long_laplace_normal_0_5), digits = 5)
-describe_posterior(max_long_laplace_normal_0_5, centrality = "mean")
-
-pp_check(max_long_laplace_hella_weak, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-pp_check(max_long_laplace_hella_weak, type = "stat_grouped", stat = "mean", group = "n_back")
-
-pp_check(max_long_laplace_hella_weak, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
-pp_check(max_long_laplace_hella_weak, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
-
-grand_mean_n_back_dist <- max_long_laplace_hella_weak %>% 
-  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
-                                    n_back = c(TRUE, FALSE)),
-              re_formula = NA)
-
-grand_mean_n_back_dist %>% mean_hdi()
-
-# model of maximum longitudinal acceleration with kinda weak priors. Including an interaction in the random effects
-
-max_long_mixture_6  <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/max_long_jerk_skewnormal_reg_priors_maximal.rds"))
-
-skew_skew_mix = mixture(family = skew_normal(), family = skew_normal(), order = 'mu')
-
-max_long_mixture_6 <- brm(data = response.vehicle.eye %>%
-                                dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
-                                dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
-                                dplyr::mutate(ppid = as.factor(ppid)),
-                              family = skew_skew_mix,
-                                      prior = c(prior(student_t(3, 0, 2.5), class = "Intercept", dpar = "mu1"),
-                                                prior(student_t(3, 0, 2.5), class = "Intercept", dpar = "mu2"),
-                                                prior(student_t(3, 0, 2.5), class = "b", dpar = "mu1"),
-                                                prior(student_t(3, 0, 2.5), class = "b", dpar = "mu2")),
-                                      bf(max_long ~ n_back * ttc_criticality_factor + (1 | ppid),
-                                         theta1 ~ ttc_criticality_factor),
-                                      control = list(adapt_delta = 0.99999999999),
-                                      iter = 6000, warmup = 3000, chains = 4, cores = 4, seed = 13,
-                                      file = "max_long_mixture_6")
-
-print(summary(max_long_mixture_6), digits = 5)
-describe_posterior(max_long_mixture_6, centrality = "mean")
-
-pp_check(max_long_mixture_6, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-pp_check(max_long_mixture_6, type = "stat_grouped", stat = "mean", group = "n_back.x")
-
-pp_check(max_long_mixture_6, type = "dens_overlay_grouped", group = "n_back.x", ndraws = 100)
-pp_check(max_long_mixture_6, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
-
-grand_mean_n_back_dist <- max_long_mixture_6 %>% 
-  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
-                                    n_back.x = c(TRUE, FALSE)),
-              re_formula = NA)
-
-grand_mean_n_back_dist %>% mean_hdi()
-
-# model of maximum longitudinal acceleration with hella weak priors. To check if the model is blowing up cause if lack of priors constraining parameter values
-max_long_jerk_laplace_reg_priors_maximal <- brm(data = response.vehicle.eye %>%
-                                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
-                                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
-                                             dplyr::mutate(ppid = as.factor(ppid)),
-                                           family = asym_laplace(),
-                                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
-                                                     prior(student_t(3, 0, 2.5), class = "b")),
-                                           max_long_jerk ~ n_back.x * ttc_criticality_factor + (n_back.x * ttc_criticality_factor | ppid),
-                                           control = list(adapt_delta = 0.99999999999),
-                                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
-                                           file = "max_long_jerk_laplace_reg_priors_maximal")
-
-print(summary(max_long_jerk_laplace_reg_priors_maximal), digits = 5)
-describe_posterior(max_long_jerk_laplace_reg_priors_maximal, centrality = "mean")
-
-pp_check(max_long_jerk_laplace_reg_priors_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-pp_check(max_long_jerk_laplace_reg_priors_maximal, type = "stat_grouped", stat = "mean", group = "n_back.x")
-
-pp_check(max_long_jerk_laplace_reg_priors_maximal, type = "dens_overlay_grouped", group = "n_back.x", ndraws = 100)
-pp_check(max_long_jerk_laplace_reg_priors_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
-
-# setting re_formula = NA tells the function to not use any random effects - here we plot the n-back specific distributions 
-grand_mean_n_back_dist <- max_long_jerk_skewnormal_reg_priors %>% 
-  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
-                                    n_back.x = FALSE),
-              re_formula = NA)
-
-grand_mean_n_back_dist %>% mean_hdi()
-
-d <- max_long_mixture_6$data
-
-ggplot(d, mapping = aes(max_long_jerk)) +
-  geom_histogram() +
-  facet_grid(n_back.x ~ ttc_criticality_factor)
-```
-
-## Modelling - lateral accelerations
-
-```{r}
-ggplot(response.vehicle.eye %>%
-         dplyr::filter(rt.outlier == FALSE, ho.rt != 0, collision == 0), mapping = aes(x = max_lat)) +
-  geom_histogram(aes(fill = as.factor(n_back)), alpha = 0.5, bins = 50, col = "black") +
-  facet_grid(n_back ~ttc_criticality.x)
-
+print(summary(mean_decel_gaussian_reg_priors_maximal), digits = 5)
+describe_posterior(mean_decel_gaussian_reg_priors_maximal, centrality = "mean")
+
+pp_check(mean_decel_gaussian_reg_priors_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
+pp_check(mean_decel_gaussian_reg_priors_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
+
+pp_check(mean_decel_gaussian_reg_priors_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
+pp_check(mean_decel_gaussian_reg_priors_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
+
+pp_check(mean_decel_skewnormal_reg_priors_maximal, type = "hist", group = "ttc_criticality_factor")
+```
+
+## Modelling - mean lateral accelerations
+
+```{r}
 ggplot(response.vehicle.eye %>%
@@
   geom_histogram(aes(fill = as.factor(n_back)), alpha = 0.5, bins = 50, col = "black") +
-  facet_grid(n_back ~ttc_criticality.x)
+  facet_grid(n_back ~ ttc_criticality.x)
 
 # load model
-mod_max_lat_bayesian_lognormal <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/max_lat_lognormal_priors.rds"))
+mean_lat_acc_lognormal_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/mean_lat_acc_lognormal_maximal.rds"))
 
 # model of maximum longitudinal acceleration with priors
-mod_max_lat_bayesian_lognormal <- brm(data = response.vehicle.eye %>%
+mean_lat_acc_lognormal_maximal <- brm(data = response.vehicle.eye %>%
                                         dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
@@
                                                 prior(student_t(3, 0, 2.5), class = "b")),
-                                       max_lat ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor | ppid),
+                                       bf(mean_lat_acc ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor | ppid)),
                                       control = list(adapt_delta = 0.99999999999),
                                       iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
-                                      file = "max_lat_lognormal_priors")
-
-print(summary(mod_max_lat_bayesian_lognormal), digits = 5)
-describe_posterior(mod_max_lat_bayesian_lognormal, centrality = "mean")
+                                      file = here::here("takeover_performance_cogload_time_budget/Models/mean_lat_acc_lognormal_maximal"))
+
+pp_check(mean_lat_acc_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
+pp_check(mean_lat_acc_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
+
+pp_check(mean_lat_acc_lognormal_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
+pp_check(mean_lat_acc_lognormal_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
+
+print(summary(mean_lat_acc_lognormal_maximal), digits = 5)
+describe_posterior(mean_lat_acc_lognormal_maximal, centrality = "mean")
 
@@
 
-# load model
-mod_sdlp_bayesian_lognormal_priors <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/sdlp_lognormal_priors.rds"))
+sdlp_lognormal_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/sdlp_lognormal_maximal.rds"))
 
 # initial model of SDLP
-mod_sdlp_bayesian_lognormal_priors <- brm(data = response.vehicle.eye %>%
+sdlp_lognormal_maximal <- brm(data = response.vehicle.eye %>%
                                 dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
@@
                                         prior(student_t(3, 0, 2.5), class = "b")),
-                                   sdlp ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor| ppid),
+                              bf(sdlp ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor| ppid)),
                                    control = list(adapt_delta = 0.95),
                                    iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13, 
-                                   file = "sdlp_lognormal_priors")
-
-print(summary(mod_sdlp_bayesian_lognormal_priors), digits = 5)
-describe_posterior(mod_sdlp_bayesian_lognormal_priors, centrality = "mean")
-
-pp_check(mod_sdlp_bayesian_lognormal_priors, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100) 
-pp_check(mod_sdlp_bayesian_lognormal_priors, type = "stat_grouped", stat = "mean", group = c("ttc_criticality_factor"))
+                                   file = here::here("takeover_performance_cogload_time_budget/Models/sdlp_lognormal_maximal"))
+
+print(summary(sdlp_lognormal_maximal), digits = 5)
+describe_posterior(sdlp_lognormal_maximal, centrality = "mean")
+
+pp_check(sdlp_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
+pp_check(sdlp_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
+
+pp_check(sdlp_lognormal_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
+pp_check(sdlp_lognormal_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
+
+pp_check(sdlp_lognormal_maximal, type = "hist", group = "ttc_criticality_factor")
+
+# initial model of SDLP
+sdlp_skew_normal_maximal <- brm(data = response.vehicle.eye %>%
+                                  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
+                                  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
+                                  dplyr::mutate(ppid = as.factor(ppid)),
+                              family = skew_normal(),
+                              prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
+                                        prior(student_t(3, 0, 2.5), class = "b")),
+                              bf(sdlp ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor| ppid)),
+                                   control = list(adapt_delta = 0.95),
+                                   iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13, 
+                                   file = here::here("takeover_performance_cogload_time_budget/Models/sdlp_skew_normal_maximal"))
+
+print(summary(sdlp_skew_normal_maximal), digits = 5)
+describe_posterior(sdlp_skew_normal_maximal, centrality = "mean")
+
+pp_check(sdlp_skew_normal_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
+pp_check(sdlp_skew_normal_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
+
+pp_check(sdlp_skew_normal_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
+pp_check(sdlp_skew_normal_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
 
@@
 ```{r}
-# load model
-mod_sd_yaw_gaussian <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/sd_yaw_gaussian_priors.rds"))
+# SDLP - distributions
+ggplot(response.vehicle.eye %>%
+                dplyr::filter(rt.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15), mapping = aes(x = sd_yaw_manual)) +
+  geom_histogram(alpha = 0.5, bins = 50, col = "black") + 
+  xlab("SD yaw") +
+  facet_wrap(n_back ~ ttc_criticality.x)
+
+sd_yaw_manual_gaussian_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_manual_gaussian_maximal.rds"))
 
 # initial model of sd_yaw
-mod_sd_yaw_gaussian <- brm(data = response.vehicle.eye %>%
+sd_yaw_manual_gaussian_maximal <- brm(data = response.vehicle.eye %>%
                              dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
@@
                            family = gaussian(),
-                           sd_yaw ~ n_back * ttc_criticality_factor + (n_back + ttc_criticality_factor| ppid),
+                           bf(sd_yaw_manual ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor| ppid)),
                            prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
@@
                            iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13, 
-                                                   file = "sd_yaw_gaussian_priors")
+                           control = list(adapt_delta = 0.95),
+                           file = here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_manual_gaussian_maximal"))
+
 # posterior predictive checks
-pp_check(mod_sd_yaw_gaussian, type = "dens_overlay_grouped", group = "n_back", ndraws = 100) +
-  ggtitle("gaussian")
-
-print(summary(mod_sd_yaw_gaussian), digits = 5)
-describe_posterior(mod_sd_yaw_gaussian)
+pp_check(sd_yaw_manual_gaussian_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
+pp_check(sd_yaw_manual_gaussian_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
+
+pp_check(sd_yaw_manual_gaussian_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
+pp_check(sd_yaw_manual_gaussian_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
+
+print(summary(sd_yaw_manual_gaussian_maximal), digits = 5)
+describe_posterior(sd_yaw_manual_gaussian_maximal)
 ```
@@
 ```{r}
-# load model
-mod_sd_yaw_automation_gaussian <- readRDS(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/sd_yaw_automation_gaussian_priors.rds"))
+# SDLP - distributions
+ggplot(response.vehicle.eye %>%
+                dplyr::filter(rt.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15), mapping = aes(x = sd_yaw_automation)) +
+  geom_histogram(alpha = 0.5, bins = 50, col = "black") + 
+  xlab("SD yaw") +
+  facet_wrap(~n_back)
+
+sd_yaw_automation_gaussian_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_automation_gaussian_maximal.rds"))
 
 # initial model of sd_yaw
-mod_sd_yaw_automation_gaussian <- brm(data = response.vehicle.eye %>%
-                             dplyr::filter(rt.outlier == FALSE, 
-                                           ho.outlier == FALSE, 
-                                           ho.rt != 0, collision == 0, 
-                                           ho.rt > .15) %>%
+sd_yaw_automation_gaussian_maximal <- brm(data = response.vehicle.eye %>%
+                                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
                              dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
@@
                            iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13, 
-                                                   file = "sd_yaw_automation_gaussian_priors")
+                                                   file = here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_automation_gaussian_maximal"))
+
 # model summmary
-print(summary(mod_sd_yaw_automation_gaussian), digits = 5)
-describe_posterior(mod_sd_yaw_automation_gaussian)
+print(summary(sd_yaw_automation_gaussian_maximal), digits = 5)
+describe_posterior(sd_yaw_automation_gaussian_maximal)
 
 # posterior predictive checks
-pp_check(mod_sd_yaw_automation_gaussian, type = "dens_overlay_grouped", group = "n_back", ndraws = 100) 
-pp_check(mod_sd_yaw_automation_gaussian, type = "stat_grouped", stat = "mean", group = c("n_back"))
+pp_check(sd_yaw_automation_gaussian_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
+pp_check(sd_yaw_automation_gaussian_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
 

### 2024-08-15 manuscript_and_modelling_plots_takeovers.Rmd
figs 6 and 7 and associated code

@@
 
-## Modelling - mean decelerations
+## Mean decelerations - model fitting
 
@@
                                            file = here::here("takeover_performance_cogload_time_budget/Models/mean_decel_skewnormal_reg_priors_maximal"))
-
-# summarising model parameters 
-print(summary(mean_decel_skewnormal_reg_priors_maximal), digits = 5)
-describe_posterior(mean_decel_skewnormal_reg_priors_maximal , centrality = "mean")
 
@@
 
+# Mean decelerations: model predictions
+
+```{r}
+# summarising model parameters 
+print(summary(mean_decel_skewnormal_reg_priors_maximal), digits = 5)
+describe_posterior(mean_decel_skewnormal_reg_priors_maximal , centrality = "mean")
+
+#### Global mean effect of TTC #### # setting re_formula = NA tells the function to not use any random effects - here we plot the n-back specific distributions 
+predicted_mean_decel_ttc <- mean_decel_skewnormal_reg_priors_maximal %>% 
+  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
+                                    n_back = FALSE),
+              re_formula = NA)
+
+predicted_mean_decel_ttc %>% mean_hdi()
+
+# effect of TTC when N-back is not TRUE
+mean_decel_MER_TTC <- mean_decel_skewnormal_reg_priors_maximal %>% 
+  emmeans(~ ttc_criticality_factor,
+          at = list(n_back = FALSE),
+          epred = TRUE, re_formula = NA) %>% 
+  contrast(method = "revpairwise") %>% 
+  gather_emmeans_draws()
+
+mean_decel_MER_TTC %>% mean_hdi()
+```
+
+## Mean decelerations: visualising posterior draws and means
+
+```{r}
+#### predicted posterior means and distribution ####
+predicted_draws = empty_grid %>%
+  add_predicted_draws(mean_decel_skewnormal_reg_priors_maximal)
+
+expected_values = empty_grid %>%
+  add_epred_draws(mean_decel_skewnormal_reg_priors_maximal)
+
+# labels
+ttc_labs <- c("TTC = 3 s", "TTC = 5 s")
+names(ttc_labs) <- c(as.factor(3), as.factor(5))
+
+posterior_mean_decel <- response.vehicle.eye %>%
+  dplyr::ungroup() %>%
+  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
+  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
+  ggplot(aes(x = mean_decel, y = n_back)) +
+  stat_pointinterval(aes(x = .epred), data = expected_values, .width = c(.50, .95), position = position_nudge(y = -0.35)) +
+  stat_interval(aes(x = .prediction), data = predicted_draws, .width = c(.50, .80, .95, .99)) +
+  geom_jitter(data = response.vehicle.eye %>%
+  dplyr::ungroup() %>%
+  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
+  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)), size = 2, height = .05, alpha = .3) +
+  #geom_point(conditional_df_fitted[[3]], mapping = aes(x = estimate__, y = n_back), col = "white") +
+  scale_y_discrete(labels = c('No N-B','N-B'), guide = guide_axis(angle = 90)) +
+  scale_color_brewer("Posterior predictive interval") +
+  ggtitle("A") +
+  xlim(-7, 0) +
+  xlab(expression(M[D] ~"("~m/s^2~")")) +
+  ylab(" ") +
+  #scale_x_continuous(limits = c(0, 3.5), breaks = seq(0, 3, .5), labels = label_number(accuracy = .5)) +
+  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
+  theme_bw() +
+  theme(legend.position = "bottom", legend.direction = "horizontal", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 8, face = "bold"), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+# predicted mean decelerations
+predicted_mean_decel_ttc_plot <- ggplot(predicted_mean_decel_ttc, aes(x = .epred, y = " ", fill = ttc_criticality_factor)) +
+  stat_halfeye(alpha = .5) +
+  ylab(NULL) +
+  xlab(expression("Predicted" ~ mu ~ "of" ~ M[D] ~ "("~m/s^2~")")) +
+  ggtitle("B") +
+  scale_fill_discrete(name = "TTC", labels = c("3 s", "5 s")) +
+  xlim(-4, -.5) +
+  theme_bw() +
+  theme(legend.position = c(.88, .57), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+# MER of TTC on mean deceleration
+mean_decel_MER_TTC_plot <- ggplot(mean_decel_MER_TTC, aes(x = .value, y = " ")) +
+  stat_halfeye() +
+  ylab(NULL) +
+  xlab(expression(MER[M[D]]~ "("~m/s^2~")" ~ "of TTC")) +
+  ggtitle("C") +
+  scale_fill_discrete(name = "TTC", labels = c("3 s", "5 s")) +
+  theme_bw() +
+  theme(legend.position = c(.93, .62), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+fig6 <- posterior_mean_decel / (predicted_mean_decel_ttc_plot | mean_decel_MER_TTC_plot)
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig6.tiff"), plot = fig6, width = 16, height = 11, units = 'cm', dpi = 300, type = 'cairo')
+```
+
 ## Modelling - mean lateral accelerations
@@
 pp_check(mean_lat_acc_lognormal_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
-
+```
+
+## Mean lateral accelerations: model predictions
+
+```{r}
 print(summary(mean_lat_acc_lognormal_maximal), digits = 5)
@@
 
-# effect of event critcality
-grand_mean_ttc_ame_max_la <- mod_max_lat_bayesian_lognormal %>% 
-  emmeans(~ ttc_criticality_factor,
-          at = list(n_back = FALSE),
-          epred = TRUE, re_formula = NA) %>% 
-  contrast(method = "revpairwise") %>% 
-  gather_emmeans_draws()
-
-grand_mean_ttc_ame_max_la %>% mean_hdi()
-
-# effect of n-back
-grand_mean_ttc_ame_max_la <- mod_max_lat_bayesian_lognormal %>% 
-  emmeans(~ n_back,
-          at = list(ttc_criticality_factor = as.factor(5)),
-          epred = TRUE, re_formula = NA) %>% 
-  contrast(method = "revpairwise") %>% 
-  gather_emmeans_draws()
-
-grand_mean_ttc_ame_max_la %>% mean_hdi()
+# predicted lateral accelerations across all conditions
+predicted_lat_acc_ttc <- mean_lat_acc_lognormal_maximal %>% 
+  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
+                                    n_back = c(FALSE, TRUE)),
+              re_formula = NA)
+
+predicted_lat_acc_ttc %>% mean_hdi()
+```
+
+## Mean lateral accelerations  - visualising posterior draws and means
+
+```{r}
+avg_lat_acc <- fread(file = here::here("takeover_performance_cogload_time_budget/Data/avg_lat_acc.csv"))
 
@@
 predicted_draws = empty_grid %>%
-  add_predicted_draws(mod_max_lat_bayesian_lognormal)
+  add_predicted_draws(mean_lat_acc_lognormal_maximal)
 
 expected_values = empty_grid %>%
-  add_epred_draws(mod_max_lat_bayesian_lognormal)
-
-posterior_max_lat <- response.vehicle.eye %>%
+  add_epred_draws(mean_lat_acc_lognormal_maximal)
+
+posterior_mean_lat_acc <- response.vehicle.eye %>%
   dplyr::ungroup() %>%
@@
   dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
-  ggplot(aes(x = max_lat, y = n_back)) +
+  ggplot(aes(x = mean_lat_acc, y = n_back)) +
   stat_pointinterval(aes(x = .epred), data = expected_values, .width = c(.50, .95), position = position_nudge(y = -0.35)) +
@@
   scale_color_brewer("Posterior predictive interval") +
-  xlim(0, 10) +
-  xlab(expression(MAX[LA] ~"("~m/s^2~")")) +
+  xlim(0, 1.25) +
+  xlab(expression(M[LA] ~"("~m/s^2~")")) +
   ylab(" ") +
@@
 
-avg_lat_acc <- ggplot(critical.manual %>%
-         dplyr::arrange(trialid, timestamp_common_manual) %>%
-         dplyr::group_by(n_back, ttc_criticality, timestamp_common_manual) %>%
-         dplyr::summarise(lat_acc = mean(latacc)) %>%
-         dplyr::ungroup(), mapping = aes(x = timestamp_common_manual, y = lat_acc, col = as.factor(ttc_criticality))) +
+avg_lat_acc_plot <- ggplot(avg_lat_acc, mapping = aes(x = timestamp_common_manual, y = lat_acc, col = as.factor(n_back))) +
   geom_path() +
@@
   xlab("Time (s)") +
-  scale_color_discrete(name = "TTC", labels = c("3 s", "5 s")) +
-  facet_wrap(~ n_back, labeller = labeller(n_back = l.labs)) +
-  theme_bw() +
-  theme(legend.position = c(.35, .21), legend.direction = "horizontal", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
-
-fig6 <- posterior_max_lat / avg_lat_acc
+  facet_wrap(~ ttc_criticality) +
+  scale_color_manual(name = " ", labels = c("No N-back", "N-back"), values = viridis(3)[1:2]) +
+  facet_wrap(~ ttc_criticality, labeller = labeller(ttc_criticality = ttc_labs)) +
+  theme_bw() +
+  theme(legend.position = c(.703, .21), legend.direction = "horizontal", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+fig7 <- posterior_mean_lat_acc / avg_lat_acc_plot
 
 # plot saving
-ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript_plots/fig6.tiff"), plot = fig6, width = 16, height = 11, units = 'cm', dpi = 300, type = 'cairo')
-
-# predicted means for max lat
-grand_mean_n_back_dist <- mod_max_lat_bayesian_lognormal %>% 
-  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
-                                    n_back = FALSE),
-              re_formula = NA)
-
-grand_mean_n_back_dist %>% mean_hdi()
+ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig7.tiff"), plot = fig7, width = 16, height = 11, units = 'cm', dpi = 300, type = 'cairo')
 ```

### 2024-08-16 manuscript_and_modelling_plots_takeovers.Rmd
main analysis script and supplemental material

@@
 
-## Packages
-
-Here we load the packages that will be used for this analysis
+# Packages
+
+Loading packages that will be used for this analysis
 
@@
 
-## Load vehicle data
+# Load vehicle data
 
@@
 
-## Loading participant information
+# Load participant information
 
@@
 
-# Number of participants
+# Participants demographics
 
@@
   dplyr::summarise(avg = mean(age), min_age = min(age), max_age = max(age), mean_milage = mean(Approximate.Annual.Mileage..Miles.), min_mileage = min(Approximate.Annual.Mileage..Miles.), max_mileage = max(Approximate.Annual.Mileage..Miles.), mean_license = mean(No..of.years.holding.a.full.UK.driving.license), min_license = min(No..of.years.holding.a.full.UK.driving.license), max_license = max(No..of.years.holding.a.full.UK.driving.license), N = n()) %>%
+  View()
+
+response.vehicle.eye %>%
+  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
+  dplyr::group_by(ppid) %>%
+  dplyr::slice(1) %>%
+  dplyr::group_by(Gender) %>%
+  dplyr::summarise(n = n()) %>%
   View()
@@
 
-Calculating predicted braking RT implied by the model parameters, and the average effect of time budget on braking RT
-
-```{r}
-# average effect of TTC on braking RT 
+Calculating predicted braking RT implied by the model parameters, and the average effect of time budget on braking RT.
+
+The tutorial I use to help calculate these model predictions: https://www.andrewheiss.com/blog/2021/11/10/ame-bayes-re-guide/#different-kinds-of-average-predictions-with-multilevel-models
+
+```{r}
+# calculating the marginal effect of TTC on braking RT 
 braking_rt_MER_TTC <- braking_rt_shifted_lognormal_maximal %>% 
@@
 In the chunk below, I plot the posterior expected values alongside the distributions, over the raw data.
-The function *data_grid()* produces an empty dataframe from which to generate predictions from bthe model (https://mjskay.github.io/tidybayes/articles/tidy-brms.html)
+The function *data_grid()* produces an empty dataframe from which to generate predictions from the model (https://mjskay.github.io/tidybayes/articles/tidy-brms.html)
 
@@
 predicted_lat_acc_ttc %>% mean_hdi()
+
+# marginal effect of TTC when N-back is FALSE
+lat_acc_MER_TTC_noNback <- mean_lat_acc_lognormal_maximal %>% 
+  emmeans(~ ttc_criticality_factor,
+          at = list(n_back = FALSE),
+          epred = TRUE, re_formula = NA) %>% 
+  contrast(method = "revpairwise") %>% 
+  gather_emmeans_draws()
+
+# marginal effect of TTC when N-back is TRUE
+lat_acc_MER_TTC_Nback <- mean_lat_acc_lognormal_maximal %>% 
+  emmeans(~ ttc_criticality_factor,
+          at = list(n_back = TRUE),
+          epred = TRUE, re_formula = NA) %>% 
+  contrast(method = "revpairwise") %>% 
+  gather_emmeans_draws()
 ```
@@
 
+# labels - n-back
+l.labs <- c("No N-back", "N-back")
+names(l.labs) <- c("FALSE", "TRUE")
+
+# predicted mean lateral accelerations
+predicted_lat_acc_ttc_plot <- ggplot(predicted_lat_acc_ttc, aes(x = .epred, y = " ", fill = ttc_criticality_factor)) +
+  stat_halfeye(alpha = .5) +
+  ylab(NULL) +
+  xlab(expression("Predicted" ~ mu ~ "of" ~ M[LA] ~ "("~m/s^2~")")) +
+  ggtitle("B") +
+  scale_fill_discrete(name = "TTC", labels = c("3 s", "5 s")) +
+  xlim(.1, .4) +
+  facet_wrap(~ n_back, labeller = labeller(n_back = l.labs)) +
+  theme_bw() +
+  theme(legend.position = c(.945, .58), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+# average lateral accelerations over time
 avg_lat_acc_plot <- ggplot(avg_lat_acc, mapping = aes(x = timestamp_common_manual, y = lat_acc, col = as.factor(n_back))) +
   geom_path() +
-  ggtitle("B") +
+  ggtitle("C") +
   ylab(expression("LA ("~m/s^2~")")) +
@@
 
-fig7 <- posterior_mean_lat_acc / avg_lat_acc_plot
+fig7 <- posterior_mean_lat_acc / predicted_lat_acc_ttc_plot
 
 # plot saving
-ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig7.tiff"), plot = fig7, width = 16, height = 11, units = 'cm', dpi = 300, type = 'cairo')
-```
-
-## SDLP
+ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig7.tiff"), plot = fig7, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+```
+
+# SDLP: model fitting
 
@@
 
+pp_check(sdlp_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
+pp_check(sdlp_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
+
+pp_check(sdlp_lognormal_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
+pp_check(sdlp_lognormal_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
+
+pp_check(sdlp_lognormal_maximal, type = "hist", group = "ttc_criticality_factor")
+```
+
+# SDLP: model predictions
+
+```{r}
 print(summary(sdlp_lognormal_maximal), digits = 5)
@@
 
-pp_check(sdlp_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-pp_check(sdlp_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
-
-pp_check(sdlp_lognormal_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
-pp_check(sdlp_lognormal_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
-
-pp_check(sdlp_lognormal_maximal, type = "hist", group = "ttc_criticality_factor")
-
-# initial model of SDLP
-sdlp_skew_normal_maximal <- brm(data = response.vehicle.eye %>%
-                                  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
-                                  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
-                                  dplyr::mutate(ppid = as.factor(ppid)),
-                              family = skew_normal(),
-                              prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
-                                        prior(student_t(3, 0, 2.5), class = "b")),
-                              bf(sdlp ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor| ppid)),
-                                   control = list(adapt_delta = 0.95),
-                                   iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13, 
-                                   file = here::here("takeover_performance_cogload_time_budget/Models/sdlp_skew_normal_maximal"))
-
-print(summary(sdlp_skew_normal_maximal), digits = 5)
-describe_posterior(sdlp_skew_normal_maximal, centrality = "mean")
-
-pp_check(sdlp_skew_normal_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-pp_check(sdlp_skew_normal_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
-
-pp_check(sdlp_skew_normal_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
-pp_check(sdlp_skew_normal_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
-
 #### predicted posterior means and distribution ####
 predicted_draws = empty_grid %>%
-  add_predicted_draws(mod_sdlp_bayesian_lognormal_priors)
+  add_predicted_draws(sdlp_lognormal_maximal)
 
 expected_values = empty_grid %>%
-  add_epred_draws(mod_sdlp_bayesian_lognormal_priors)
-
+  add_epred_draws(sdlp_lognormal_maximal)
+
+#### Global mean effect of TTC #### # setting re_formula = NA tells the function to not use any random effects - here we plot the n-back specific distributions 
+predicted_SDLP_ttc <- sdlp_lognormal_maximal %>% 
+  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
+                                    n_back = FALSE),
+              re_formula = NA)
+
+predicted_SDLP_ttc  %>% mean_hdi()
+
+# effect of TTC on SDLP when N-back is not TRUE
+SDLP_MER_TTC <- sdlp_lognormal_maximal%>% 
+  emmeans(~ ttc_criticality_factor,
+          at = list(n_back = FALSE),
+          epred = TRUE, re_formula = NA) %>% 
+  contrast(method = "revpairwise") %>% 
+  gather_emmeans_draws()
+
+SDLP_MER_TTC %>% mean_hdi()
+```
+
+# SDLP: visualising posterior draws and means
+
+```{r}
 # labels
@@
 
-# predicted global mean RTs implied by the model
-
-# setting re_formula = NA tells the function to not use any random effects - here we plot the n-back specific distributions 
-grand_mean_n_back_dist <- mod_sdlp_bayesian_lognormal_priors %>% 
-  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
-                                    n_back = FALSE),
-              re_formula = NA)
-
-grand_mean_n_back_dist %>% mean_hdi()
-
-global_mean_ttc_SDLP <- ggplot(grand_mean_n_back_dist ,aes(x = .epred, y = " ", fill = ttc_criticality_factor)) +
+# predicted means of SDLP
+predicted_SDLP_ttc_plot <- ggplot(predicted_SDLP_ttc, aes(x = .epred, y = " ", fill = ttc_criticality_factor)) +
   stat_halfeye(alpha = .5) +
   ylab(NULL) +
-  xlab(expression("Predicted mean"~ SD[LP]~ "(m)")) +
+  xlab(expression("Predicted" ~ mu ~ "of" ~ SD[LP]~ "(m)")) +
   ggtitle("B") +
@@
 
-# and now we plot the distribution of the difference between n_back and no n-back 
-grand_mean_n_back_mer <- mod_sdlp_bayesian_lognormal_priors %>% 
-  emmeans(~ ttc_criticality_factor,
-          at = list(n_back = FALSE),
-          epred = TRUE, re_formula = NA) %>% 
-  contrast(method = "revpairwise") %>% 
-  gather_emmeans_draws()
-
-grand_mean_n_back_mer %>% mean_hdi()
-
-grand_mean_n_back_mer <- mod_sdlp_bayesian_lognormal_priors %>% 
-  emmeans(~ n_back,
-          at = list(ttc_criticality_factor = as.factor(5)),
-          epred = TRUE, re_formula = NA) %>% 
-  contrast(method = "revpairwise") %>% 
-  gather_emmeans_draws()
-
-grand_mean_n_back_mer %>% mean_hdi()
-
-# Average marginal effect (AME) of TTC on braking RT
-MER_ttc_SDLP <- ggplot(grand_mean_n_back_mer, aes(x = .value, y = " ")) +
+# Average marginal effect of TTC on SDLP
+SDLP_MER_TTC_plot <- ggplot(SDLP_MER_TTC, aes(x = .value, y = " ")) +
   stat_halfeye() +
@@
 
-fig7 <- posterior_sdlp / (global_mean_ttc_SDLP | MER_ttc_SDLP)
+fig8 <- posterior_sdlp / (predicted_SDLP_ttc_plot | SDLP_MER_TTC_plot)
 
 # plot saving
-ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript_plots/fig7.tiff"), plot = fig7, width = 16, height = 11, units = 'cm', dpi = 300, type = 'cairo')
-```
-
-## Loading model for SD of horizontal gaze during manual driving
-
-```{r}
-# SDLP - distributions
-ggplot(response.vehicle.eye %>%
-                dplyr::filter(rt.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15), mapping = aes(x = sd_yaw_manual)) +
-  geom_histogram(alpha = 0.5, bins = 50, col = "black") + 
-  xlab("SD yaw") +
-  facet_wrap(n_back ~ ttc_criticality.x)
-
-sd_yaw_manual_gaussian_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_manual_gaussian_maximal.rds"))
-
-# initial model of sd_yaw
-sd_yaw_manual_gaussian_maximal <- brm(data = response.vehicle.eye %>%
-                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
-                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
-                             dplyr::mutate(ppid = as.factor(ppid)),
-                           family = gaussian(),
-                           bf(sd_yaw_manual ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor| ppid)),
-                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
-                                     prior(student_t(3, 0, 2.5), class = "b")),
-                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13, 
-                           control = list(adapt_delta = 0.95),
-                           file = here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_manual_gaussian_maximal"))
-
-# posterior predictive checks
-pp_check(sd_yaw_manual_gaussian_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-pp_check(sd_yaw_manual_gaussian_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
-
-pp_check(sd_yaw_manual_gaussian_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
-pp_check(sd_yaw_manual_gaussian_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
-
-print(summary(sd_yaw_manual_gaussian_maximal), digits = 5)
-describe_posterior(sd_yaw_manual_gaussian_maximal)
-```
-
-## Modelling SD yaw during automation
+ggsave(here::here("takeover_performance_cogload_time_budget/Figures/fig8.tiff"), plot = fig8, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+```
+
+# SD of horitzonal gaze during automation: model fitting
 
@@
 
-# model summmary
-print(summary(sd_yaw_automation_gaussian_maximal), digits = 5)
-describe_posterior(sd_yaw_automation_gaussian_maximal)
-
 # posterior predictive checks
@@
 pp_check(sd_yaw_automation_gaussian_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
+```
+
+# SD of horitzonal gaze during automation: model predictions
+
+```{r}
+# model summmary
+print(summary(sd_yaw_automation_gaussian_maximal), digits = 5)
+describe_posterior(sd_yaw_automation_gaussian_maximal, centrality = "mean")
 
 # average predicted SD of yaw during automation with and without n-back
-sd_yaw_automation_n_back_dist <- mod_sd_yaw_automation_gaussian %>% 
+predicted_sd_yaw_automation_nback <- sd_yaw_automation_gaussian_maximal %>% 
   epred_draws(newdata = expand_grid(n_back = c(TRUE, FALSE)),
@@
 
-sd_yaw_automation_n_back_dist %>% mean_hdi()
-
-# average effect
-sd_yaw_automation_n_back_mer <- mod_sd_yaw_automation_gaussian %>% 
+predicted_sd_yaw_automation_nback %>% mean_hdi()
+
+# average marginal effect of n-back
+sd_yaw_automation_MER_nback <- sd_yaw_automation_gaussian_maximal %>% 
   emmeans(~ n_back,
@@
 
-sd_yaw_automation_n_back_mer %>% mean_hdi()
-
-# 
-prior(student_t(3, -2, 2.5)) %>% 
-  parse_dist() %>% 
-  ggplot(aes(xdist = .dist_obj, y = prior)) + 
-  stat_halfeye(.width = c(.5, .99)) +
-  scale_y_discrete(NULL, breaks = NULL, expand = expansion(add = 0.1)) +
-  scale_x_continuous(expression(italic(p)(beta[1]))) +
-  theme_bw()
-
-```
-
-## Plotting SD of horizontal/vertical gaze data
+sd_yaw_automation_MER_nback  %>% mean_hdi()
+```
+
+# SD of horitzonal gaze during automation: dispersion plots
 
@@
 
-n_back_automation_disp <- n_back_FALSE_automation + n_back_TRUE_automation + plot_layout(axes = "collect")
+fig9 <- n_back_FALSE_automation + n_back_TRUE_automation + plot_layout(axes = "collect")
 
 # plot saving
-ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript_plots/n_back_automation_disp.tiff"), plot = n_back_automation_disp, width = 16, height = 8, units = 'cm', dpi = 300, type = 'cairo')
-
+ggsave(here::here("takeover_performance_cogload_time_budget/Figures/fig9.tiff"), plot = fig9, width = 16, height = 8, units = 'cm', dpi = 300, type = 'cairo')
+```
+
+## SD of horizontal gaze during manual driving: model fitting
+
+```{r}
+# distributions
+ggplot(response.vehicle.eye %>%
+                dplyr::filter(rt.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15), mapping = aes(x = sd_yaw_manual)) +
+  geom_histogram(alpha = 0.5, bins = 50, col = "black") + 
+  xlab("SD yaw") +
+  facet_wrap(n_back ~ ttc_criticality.x)
+
+sd_yaw_manual_gaussian_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_manual_gaussian_maximal.rds"))
+
+# initial model of sd_yaw
+sd_yaw_manual_gaussian_maximal <- brm(data = response.vehicle.eye %>%
+                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
+                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
+                             dplyr::mutate(ppid = as.factor(ppid)),
+                           family = gaussian(),
+                           bf(sd_yaw_manual ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor| ppid)),
+                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
+                                     prior(student_t(3, 0, 2.5), class = "b")),
+                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13, 
+                           control = list(adapt_delta = 0.95),
+                           file = here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_manual_gaussian_maximal"))
+
+# posterior predictive checks
+pp_check(sd_yaw_manual_gaussian_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
+pp_check(sd_yaw_manual_gaussian_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
+
+pp_check(sd_yaw_manual_gaussian_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
+pp_check(sd_yaw_manual_gaussian_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
+```
+
+## SD of horizontal gaze during manual driving: model predictions
+
+```{r}
+print(summary(sd_yaw_manual_gaussian_maximal), digits = 5)
+describe_posterior(sd_yaw_manual_gaussian_maximal, centrality = "mean")
+
+#### predicted posterior means and distribution ####
+predicted_draws = empty_grid %>%
+  add_predicted_draws(sd_yaw_manual_gaussian_maximal)
+
+expected_values = empty_grid %>%
+  add_epred_draws(sd_yaw_manual_gaussian_maximal)
+
+# predicted mean SD yaw  implied by the model as a function of TTC # setting re_formula = NA tells the function to not use any random effects - here we plot the n-back specific distributions 
+predicted_sd_yaw_manual_ttc <- sd_yaw_manual_gaussian_maximal %>% 
+  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
+                                    n_back = FALSE),
+              re_formula = NA)
+
+predicted_sd_yaw_manual_ttc %>% mean_hdi()
+
+# margainal effect of TTC for SD of yaw
+sd_yaw_manual_MER_TTC <- sd_yaw_manual_gaussian_maximal %>% 
+  emmeans(~ ttc_criticality_factor,
+          at = list(n_back = FALSE),
+          epred = TRUE, re_formula = NA) %>% 
+  contrast(method = "revpairwise") %>% 
+  gather_emmeans_draws()
+
+sd_yaw_manual_MER_TTC %>% mean_hdi()
+
+## predicted means for the effect of n-back on SD yaw
+predicted_sd_yaw_manual_nback <- sd_yaw_manual_gaussian_maximal %>% 
+  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3)),
+                                    n_back = c(FALSE, TRUE)),
+              re_formula = NA)
+
+predicted_sd_yaw_manual_nback  %>% mean_hdi()
+
+# marginal effect of N-back of SD of yaw during manual driving
+sd_yaw_manual_MER_nback <- sd_yaw_manual_gaussian_maximal %>% 
+  emmeans(~ n_back,
+          at = list(ttc_criticality_factor = as.factor(3)),
+          epred = TRUE, re_formula = NA) %>% 
+  contrast(method = "revpairwise") %>% 
+  gather_emmeans_draws()
+
+sd_yaw_manual_MER_nback %>% mean_hdi()
+```
+
+## SD of horizontal gaze during manual driving: visualising posteriors and means
+
+```{r}
+# posterior distribution
+posterior_sdyaw <- response.vehicle.eye %>%
+  dplyr::ungroup() %>%
+  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
+  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
+  ggplot(aes(x = sd_yaw_manual, y = n_back)) +
+  stat_pointinterval(aes(x = .epred), data = expected_values, .width = c(.50, .95), position = position_nudge(y = -0.35)) +
+  stat_interval(aes(x = .prediction), data = predicted_draws, .width = c(.50, .80, .95, .99)) +
+  geom_jitter(data = response.vehicle.eye %>%
+  dplyr::ungroup() %>%
+  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
+  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)), size = 2, height = .05, alpha = .3) +
+  #geom_point(conditional_df_fitted[[3]], mapping = aes(x = estimate__, y = n_back), col = "white") +
+  scale_y_discrete(labels = c('No N-B','N-B'), guide = guide_axis(angle = 90)) +
+  scale_color_brewer("Posterior predictive interval") +
+  ggtitle("A") +
+  #xlim(.5, 3.5) +
+  xlab(expression(SD[YAW]~ "(°)")) +
+  ylab(" ") +
+  #xlim(0, 2) +
+  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
+  theme_bw() +
+  theme(legend.position = "bottom", legend.direction = "horizontal", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 8, face = "bold"), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+# predicted means
+predicted_sd_yaw_manual_ttc_plot <- ggplot(predicted_sd_yaw_manual_ttc, aes(x = .epred, y = " ", fill = ttc_criticality_factor)) +
+  stat_halfeye(alpha = .5) +
+  ylab(NULL) +
+  xlab(expression("Predicted" ~ mu ~ "of" ~ SD[YAW]~ "(°)")) +
+  ggtitle("B") +
+  scale_fill_discrete(name = "TTC", labels = c("3 s", "5 s")) +
+  xlim(8, 14) +
+  theme_bw() +
+  theme(legend.position = c(.88, .6), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+# Average marginal effect for SD of yaw
+sd_yaw_manual_MER_TTC_plot <- ggplot(sd_yaw_manual_MER_TTC, aes(x = .value, y = " ")) +
+  stat_halfeye() +
+  ylab(NULL) +
+  xlab(expression(MER[SD[YAW]]~ "(°)")) +
+  ggtitle("C") +
+  scale_fill_discrete(name = "TTC", labels = c("3 s", "5 s")) +
+  theme_bw() +
+  theme(legend.position = c(.9, .7), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+fig10 <- posterior_sdyaw / (predicted_sd_yaw_manual_ttc_plot | sd_yaw_manual_MER_TTC_plot)
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Figures/fig10.tiff"), plot = fig10, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+```
+
+# SD of horitzonal gaze during manual: dispersion plots
+
+```{r}
 # gaze concentration during manual driving
-
 n_back_ttc_manual_disp_ttc5 <- ggplot(dat.eye.manual %>%
@@
 
-n_back_ttc_manual_disp <- n_back_ttc_manual_disp_ttc3 / n_back_ttc_manual_disp_ttc5 + plot_layout(axes = "collect")
+fig11 <- n_back_ttc_manual_disp_ttc3 / n_back_ttc_manual_disp_ttc5 + plot_layout(axes = "collect")
 
 # plot saving
-ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript_plots/n_back_ttc_manual_disp.tiff"), plot = n_back_ttc_manual_disp, width = 16, height = 16, units = 'cm', dpi = 300, type = 'cairo')
-
-#### predicted posterior means and distribution ####
-predicted_draws = empty_grid %>%
-  add_predicted_draws(mod_sd_yaw_gaussian)
-
-expected_values = empty_grid %>%
-  add_epred_draws(mod_sd_yaw_gaussian)
-
-posterior_sdyaw <- response.vehicle.eye %>%
-  dplyr::ungroup() %>%
-  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
-  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
-  ggplot(aes(x = sd_yaw, y = n_back)) +
-  stat_pointinterval(aes(x = .epred), data = expected_values, .width = c(.50, .95), position = position_nudge(y = -0.35)) +
-  stat_interval(aes(x = .prediction), data = predicted_draws, .width = c(.50, .80, .95, .99)) +
-  geom_jitter(data = response.vehicle.eye %>%
-  dplyr::ungroup() %>%
-  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
-  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)), size = 2, height = .05, alpha = .3) +
-  #geom_point(conditional_df_fitted[[3]], mapping = aes(x = estimate__, y = n_back), col = "white") +
-  scale_y_discrete(labels = c('No N-B','N-B'), guide = guide_axis(angle = 90)) +
-  scale_color_brewer("Posterior predictive interval") +
-  ggtitle("A") +
-  #xlim(.5, 3.5) +
-  xlab(expression(SD[YAW]~ "(°)")) +
-  ylab(" ") +
-  #xlim(0, 2) +
-  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
-  theme_bw() +
-  theme(legend.position = "bottom", legend.direction = "horizontal", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 8, face = "bold"), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
-
-# predicted global mean RTs implied by the model
-
-# setting re_formula = NA tells the function to not use any random effects - here we plot the n-back specific distributions 
-grand_mean_ttc_dist <- mod_sd_yaw_gaussian %>% 
-  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
-                                    n_back = FALSE),
-              re_formula = NA)
-
-grand_mean_ttc_dist %>% mean_hdi()
-
-global_mean_ttc_sdyaw <- ggplot(grand_mean_ttc_dist ,aes(x = .epred, y = " ", fill = ttc_criticality_factor)) +
-  stat_halfeye(alpha = .5) +
-  ylab(NULL) +
-  xlab(expression("Predicted mean"~ SD[YAW]~ "(°)")) +
-  ggtitle("B") +
-  scale_fill_discrete(name = "TTC", labels = c("3 s", "5 s")) +
-  xlim(8, 14) +
-  theme_bw() +
-  theme(legend.position = c(.88, .6), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
-
-# and now we plot the distribution of the difference between n_back and no n-back 
-grand_mean_ttc_mer <- mod_sd_yaw_gaussian %>% 
-  emmeans(~ ttc_criticality_factor,
-          at = list(n_back = FALSE),
-          epred = TRUE, re_formula = NA) %>% 
-  contrast(method = "revpairwise") %>% 
-  gather_emmeans_draws()
-
-grand_mean_ttc_mer %>% mean_hdi()
-
-# Average marginal effect (AME) of TTC on braking RT
-MER_ttc_sdyaw <- ggplot(grand_mean_ttc_mer, aes(x = .value, y = " ")) +
-  stat_halfeye() +
-  ylab(NULL) +
-  xlab(expression(MER[SD[YAW]]~ "(°)")) +
-  ggtitle("C") +
-  scale_fill_discrete(name = "TTC", labels = c("3 s", "5 s")) +
-  theme_bw() +
-  theme(legend.position = c(.9, .7), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
-
-fig8 <- posterior_sdyaw / (global_mean_ttc_sdyaw  | MER_ttc_sdyaw)
-
-# plot saving
-ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript_plots/fig8.tiff"), plot = fig8, width = 16, height = 11, units = 'cm', dpi = 300, type = 'cairo')
-
-## effect of n-back on SD yaw
-grand_mean_n_back_dist <- mod_sd_yaw_gaussian %>% 
-  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3)),
-                                    n_back = c(FALSE, TRUE)),
-              re_formula = NA)
-
-grand_mean_n_back_dist %>% mean_hdi()
-
-grand_mean_n_back_mer <- mod_sd_yaw_gaussian %>% 
-  emmeans(~ n_back,
-          at = list(ttc_criticality_factor = as.factor(3)),
-          epred = TRUE, re_formula = NA) %>% 
-  contrast(method = "revpairwise") %>% 
-  gather_emmeans_draws()
-
-grand_mean_n_back_mer  %>% mean_hdi()
-```
-
-## Individual variation of SD of yaw
-
-## TO DO
-
-- MAKE TITLES ON GZE SUBPLOTS A NORMAL SIZE
-- PUT ARROWS ON STRIP PLOT
-- CLEAN UP CODE SCRIPT FOR PUBLICATION
+ggsave(here::here("takeover_performance_cogload_time_budget/Figures/fig11.tiff"), plot = fig11, width = 16, height = 16, units = 'cm', dpi = 300, type = 'cairo')
+```
+
+# SD of horitzonal gaze during manual: individual dispersion plots
 
@@
 # relative size of  heterogenity effect for 2-back on mu
-summary(mod_sd_yaw_gaussian)[["random"]][["ppid"]][2,1] / summary(mod_sd_yaw_gaussian)[["fixed"]][2,1]
+summary(sd_yaw_manual_gaussian_maximal)[["random"]][["ppid"]][2,1] / summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1]
 
@@
 # individual effects for SD of yaw during manual driving
-ppid.effects <- as.data.frame(ranef(mod_sd_yaw_gaussian)) %>%
+ppid.effects <- as.data.frame(ranef(sd_yaw_manual_gaussian_maximal)) %>%
   dplyr::select(ppid.Estimate.n_backTRUE) %>%
-  dplyr::mutate(ranef = ppid.Estimate.n_backTRUE + summary(mod_sd_yaw_gaussian)[["fixed"]][2,1]) %>%
+  dplyr::mutate(ranef = ppid.Estimate.n_backTRUE + summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1]) %>%
   tibble::rownames_to_column("ppid")
@@
 # CI interval for average effect
-bayes.credible.intervals <- as.data.frame(summary(mod_sd_yaw_gaussian)[["fixed"]][3:4])
+bayes.credible.intervals <- as.data.frame(summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][3:4])
 
 # select random effects parameter 
-ran.effects <- summary(mod_sd_yaw_gaussian)[["random"]][["ppid"]][2,1]
+ran.effects <- summary(sd_yaw_manual_gaussian_maximal)[["random"]][["ppid"]][2,1]
 
@@
   geom_hline(aes(yintercept = bayes.credible.intervals$`u-95% CI`[2], linetype="95% CI"), size = 1.5,  color = viridis(5)[3]) +
-  geom_hline(aes(yintercept = summary(mod_sd_yaw_gaussian)[["fixed"]][2,1], linetype = "beta_1"), size = 1.5, color = "black") +
-  geom_hline(aes(yintercept = summary(mod_sd_yaw_gaussian)[["fixed"]][2,1] + 1.96 * ran.effects, linetype = "95% HI"), size = 1.5, color = viridis(5)[2]) +
-  geom_hline(aes(yintercept = summary(mod_sd_yaw_gaussian)[["fixed"]][2,1] - 1.96 * ran.effects, linetype = "95% HI"), size = 1.5, color = viridis(5)[2]) +
+  geom_hline(aes(yintercept = summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1], linetype = "beta_1"), size = 1.5, color = "black") +
+  geom_hline(aes(yintercept = summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1] + 1.96 * ran.effects, linetype = "95% HI"), size = 1.5, color = viridis(5)[2]) +
+  geom_hline(aes(yintercept = summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1] - 1.96 * ran.effects, linetype = "95% HI"), size = 1.5, color = viridis(5)[2]) +
   scale_linetype_manual(name = " ", values = c(2, 1, 1), labels = c(expression(CI[95]), expression(HI[95]), expression(beta[N])), guide = guide_legend(override.aes = list(color = c(viridis(5)[3], viridis(5)[2], "black")))) +
@@
 # heterogenity intervals for the effect of N-back on SD of yaw during manual driving
-summary(mod_sd_yaw_gaussian)[["fixed"]][2,1] + 1.96 * ran.effects
-summary(mod_sd_yaw_gaussian)[["fixed"]][2,1] - 1.96 * ran.effects
+summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1] + 1.96 * ran.effects
+summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1] - 1.96 * ran.effects
 
@@
   ggtitle(label = "B",
-          subtitle = "Participant 3," ~ beta[N[14]] ~ "= -.065") +
+          subtitle = "Participant 3," ~ beta[N[3]] ~ "= -.065") +
   xlab("Yaw (°)") +
@@
 
-fig99 <- strip_plot / (p_3 | p_14) / (p_7 | p_13)
-
-ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript_plots/fig99.tiff"), plot = fig99, width = 16, height = 18, units = 'cm', dpi = 300, type = 'cairo')
-```
+fig12 <- strip_plot / (p_3 | p_14) / (p_7 | p_13)
+
+ggsave(here::here("takeover_performance_cogload_time_budget/Figures/fig12.tiff"), plot = fig12, width = 16, height = 18, units = 'cm', dpi = 300, type = 'cairo')
+```

### 2024-08-16 supplemental_material.Rmd
main analysis script and supplemental material

---
title: "Supplemental material"
author: "Courtney Goodridge"
date: "16/08/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Supplemental material

This analysis script contains analysis and plotting for the supplemental material associated with the following manuscript:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2024-08-16 manuscript_and_modelling_plots_takeovers.Rmd
new fig 4

@@
 # expected values and model predicted means
-
 posterior_braking_rt <- response.vehicle.eye %>%
@@
 # plot saving
-ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig4.tiff"), plot = fig4, width = 16, height = 11, units = 'cm', dpi = 300, type = 'cairo')
+ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig4.tiff"), plot = fig4, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
 ```

### 2024-08-28 manuscript_and_modelling_plots_takeovers.Rmd
resizing figures for manuscript

@@
 # plot saving
-ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig5.tiff"), plot = fig5, width = 16, height = 11, units = 'cm', dpi = 300, type = 'cairo')
+ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig5.tiff"), plot = fig5, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
 ```
@@
 # plot saving
-ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig6.tiff"), plot = fig6, width = 16, height = 11, units = 'cm', dpi = 300, type = 'cairo')
+ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig6.tiff"), plot = fig6, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
 ```

### 2024-08-29 supplemental_material.Rmd
suuplemental matieral figures

@@
 
-```{r cars}
-summary(cars)
+## Packages
+
+```{r}
+if(!require(here)) install.packages("here")
+library(here)
+
+if(!require(ggplot2)) install.packages("ggplot2")
+library(ggplot2)
+
+if(!require(dplyr)) install.packages("dplyr")
+library(dplyr)
+
+if(!require(tidyr)) install.packages("tidyr")
+library(tidyr)
+
+if(!require(viridis)) install.packages("viridis")
+library(viridis)
+
+if(!require(gridExtra)) install.packages("gridExtra")
+library(gridExtra)
+
+if(!require(readr)) install.packages("readr")
+library(readr)
+
+if(!require(plyr)) install.packages("plyr")
+library(plyr)
+
+if(!require(stringr)) install.packages("stringr")
+library(stringr)
+
+if(!require(readxl)) install.packages("readxl")
+library(readxl)
+
+if(!require(data.table)) install.packages("data.table")
+library(data.table)
+
+if(!require(xfun)) install.packages("xfun")
+library(xfun)
+
+if(!require(cowplot)) install.packages("cowplot")
+library(cowplot)
+
+if(!require(gganimate)) install.packages("gganimate")
+library(gganimate)
+
+if(!require(ggExtra)) install.packages("ggExtra")
+library(ggExtra)
+
+if(!require(plotly)) install.packages("plotly")
+library(plotly)
+
+if(!require(brms)) install.packages("brms")
+library(brms)
+
+if(!require(bayestestR)) install.packages("bayestestR")
+library(bayestestR)
+
+if(!require(emmeans)) install.packages("emmeans")
+library(emmeans)
+
+if(!require(ROSE)) install.packages("ROSE")
+library(ROSE)
+
+if(!require(Rmisc)) install.packages("Rmisc")
+library(Rmisc)
+
+if(!require(metafolio)) install.packages("metafolio")
+library(metafolio)
+
+if(!require(tibble)) install.packages("tibble")
+library(tibble)
+
+if(!require(modelr)) install.packages("modelr")
+library(modelr)
+
+if(!require(tidybayes)) install.packages("tidybayes")
+library(tidybayes)
+
+if(!require(mgcv)) install.packages("mgcv")
+library(mgcv)
+
+if(!require(ciTools)) install.packages("ciTools")
+library(ciTools)
+
+if(!require(gratia)) install.packages("gratia")
+library(gratia)
+
+if(!require(scales)) install.packages("scales")
+library(scales)
+
+if(!require(patchwork)) install.packages("patchwork")
+library(patchwork)
+
+if(!require(ggforce)) install.packages("ggforce")
+library(ggforce)
 ```
 
-## Including Plots
+# Load vehicle data
 
-You can also embed plots, for example:
+This provides timing responses to takeovers and collision data. We also remove participants that were removed in the gaze entropy analysis.
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+```{r}
+# response data frame for vehicle and eye data per trial
+response.vehicle.eye <- fread(file = here::here("takeover_performance_cogload_time_budget/Data/takeover.responses.critical.lat.long.csv"))
+
+# removing participants from vehicle and gaze data
+response.vehicle.eye <- response.vehicle.eye %>%
+  dplyr::filter(ppid != 34, ppid != 39, ppid != 47) %>%
+  tidyr::drop_na()
+
+# make collision data 1s and 0s
+response.vehicle.eye <- response.vehicle.eye %>%
+  dplyr::mutate(collision = case_when(collision == TRUE ~ 1,
+                                      collision == FALSE ~ 0))
+
+# computing outliers for braking reaction time
+response.vehicle.eye <-  response.vehicle.eye %>%
+  #dplyr::filter(collision == 0) %>%
+  tidyr::drop_na() %>%
+  dplyr::group_by(n_back, ttc_criticality.x) %>%
+  dplyr::mutate(mean.rt = mean(rt), sd.rt = sd(rt)) %>%
+  dplyr::mutate(sd.rt.4 =  sd.rt * 4) %>%
+  dplyr::mutate(mean_4_sd = mean.rt + sd.rt.4) %>%
+  dplyr::mutate(rt.outlier = rt > mean_4_sd)
+
+# calculating outliers for hands on reaction time
+response.vehicle.eye <-  response.vehicle.eye %>%
+  #dplyr::filter(collision == 0) %>%
+  tidyr::drop_na() %>%
+  dplyr::group_by(n_back, ttc_criticality.x) %>%
+  dplyr::mutate(mean.ho = mean(ho.rt), sd.ho = sd(ho.rt)) %>%
+  dplyr::mutate(sd.ho.4 =  sd.ho * 4) %>%
+  dplyr::mutate(mean_4_sd = mean.ho + sd.ho.4) %>%
+  dplyr::mutate(ho.outlier = ho.rt > mean_4_sd)
+
+# removing outliers
+response.vehicle.eye <- response.vehicle.eye %>%
+  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
+  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x))
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+## Braking reaction time
+
+```{r}
+# loading model
+braking_rt_shifted_lognormal_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/braking_rt_shifted_lognormal_maximal.rds"))
+
+# posterior predictive checks
+brt_stat_grouped_ttc <- pp_check(braking_rt_shifted_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
+brt_stat_grouped_nback <- pp_check(braking_rt_shifted_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
+
+# predicted global mean RTs implied by the model # setting re_formula = NA tells the function to not use any random effects - here we plot the TTC specific distributions 
+predicted_braking_rt_ttc <- braking_rt_shifted_lognormal_maximal %>% 
+  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
+                                    n_back = FALSE),
+              re_formula = NA)
+
+predicted_braking_rt_ttc %>% mean_hdi()
+
+ttc_labs <- c("TTC = 3 s", "TTC = 5 s")
+names(ttc_labs) <- c(as.factor(3), as.factor(5))
+
+### STAT GROUPED PLOTS FOR MEAN BRT
+
+# mean BRT for critcality
+sm_fig_1_1 <- ggplot(brt_stat_grouped_ttc[["data"]] %>%
+         dplyr::mutate(ttc_criticality_factor = as.factor(group)), mapping = aes(value)) +
+  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
+  geom_vline(response.vehicle.eye %>% 
+               dplyr::group_by(ttc_criticality_factor) %>%
+               dplyr::summarise(mean_brt = mean(rt)), mapping = aes(xintercept = mean_brt, fill = "T(y)"), col = "darkblue", size = 2) +
+  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
+  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
+  scale_x_continuous(limits = c(1.0, 1.5), breaks = seq(1.0, 1.4, .1), labels = label_number(accuracy = 0.1)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("A") +
+  ylab(" ") +
+  xlab(expression(RT[B]~ "(s)")) +
+  theme_bw() +
+  theme(legend.position = c(.593, .65), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+n_back_labs <- c("No N-back", "N-back")
+names(n_back_labs) <- c(FALSE, TRUE)
+
+# mean BRT for N-back
+sm_fig_1_2 <- ggplot(brt_stat_grouped_nback[["data"]] %>%
+         dplyr::mutate(n_back = as.factor(group)), mapping = aes(value)) +
+  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
+  geom_vline(response.vehicle.eye %>% 
+               dplyr::group_by(n_back) %>%
+               dplyr::summarise(mean_brt = mean(rt)), mapping = aes(xintercept = mean_brt, fill = "T(y)"), col = "darkblue", size = 2) +
+  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
+  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
+  scale_x_continuous(limits = c(1.0, 1.5), breaks = seq(1.0, 1.4, .1), labels = label_number(accuracy = 0.1)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("B") +
+  ylab(" ") +
+  xlab(expression(RT[B]~ "(s)")) +
+  theme_bw() +
+  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+sm_fig1 <- sm_fig_1_1 / sm_fig_1_2
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig1.tiff"), plot = sm_fig1, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+
+### DENSITY POSTERIOR PLOTS
+
+pp_check(braking_rt_shifted_lognormal_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100) 
+pp_check(braking_rt_shifted_lognormal_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
+
+yrep_brt <- response.vehicle.eye %>% 
+  select(rt, n_back, ttc_criticality_factor, ppid) %>% 
+  add_predicted_draws(braking_rt_shifted_lognormal_maximal, ndraws = 100)
+
+sm_fig2_1 <- ggplot() + 
+  geom_density(yrep_brt, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
+  geom_density(response.vehicle.eye, mapping = aes(rt, col = "y"), size = 1) +
+  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
+  xlim(0, 5) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("A") +
+  ylab(" ") +
+  xlab(expression(RT[B]~ "(s)")) +
+  theme_bw() +
+  theme(legend.position = c(.94, .69), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+sm_fig2_2 <- ggplot() + 
+  geom_density(yrep_brt, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
+  geom_density(response.vehicle.eye, mapping = aes(rt, col = "y"), size = 1) +
+  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
+  xlim(0, 5) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("B") +
+  ylab(" ") +
+  xlab(expression(RT[B]~ "(s)")) +
+  theme_bw() +
+  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+sm_fig2 <- sm_fig2_1 / sm_fig2_2
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig2.tiff"), plot = sm_fig2, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+
+### SIMULATED NEW PARTICIPANTS
+
+# - change NA to observed data - then use legend to identify y versus y_rep
+brt_hist <- pp_check(braking_rt_shifted_lognormal_maximal, type = "hist", ndraws = 11)
+
+ggplot(brt_hist[["data"]], mapping = aes(value)) +
+  geom_histogram() +
+  facet_wrap(~ rep_id)
+```

### 2024-08-30 manuscript_and_modelling_plots_takeovers.Rmd
new code for plotting and model fitting with truncation

@@
 
-pp_check(mean_decel_skewnormal_reg_priors_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-pp_check(mean_decel_skewnormal_reg_priors_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
-
-pp_check(mean_decel_skewnormal_reg_priors_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
-pp_check(mean_decel_skewnormal_reg_priors_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
-
-d <- pp_check(mean_decel_skewnormal_reg_priors_maximal, type = "hist", group = "ttc_criticality_factor")
-
-ggplot(d[["data"]], mapping = aes(value)) +
-  geom_histogram(aes(fill = as.factor(is_y))) +
-  facet_wrap(~ rep_id)
+mean_decel_trunc_gaussian_reg_priors_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/mean_decel_trunc_skewnormal_reg_priors_maximal.rds"))
+
+# modelling average deceleration with regularising priors. Random effects structure is maximal. Distribution family is skew-normal. 
+mean_decel_trunc_gaussian_reg_priors_maximal <- brm(data = response.vehicle.eye %>%
+                                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
+                                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
+                                             dplyr::mutate(ppid = as.factor(ppid)),
+                                           family = gaussian(),
+                                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
+                                                     prior(student_t(3, 0, 2.5), class = "b")),
+                                           bf(mean_decel | trunc(ub = 0) ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor | ppid)),
+                                           control = list(adapt_delta = 0.99999999999),
+                                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
+                                           file = here::here("takeover_performance_cogload_time_budget/Models/mean_decel_trunc_gaussian_reg_priors_maximal"))
+
+mean_decel_gaussian_reg_priors_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/mean_decel_gaussian_reg_priors_maximal.rds"))
 
@@
                                            file = here::here("takeover_performance_cogload_time_budget/Models/mean_decel_gaussian_reg_priors_maximal"))
-# summarising model parameters 
-print(summary(mean_decel_gaussian_reg_priors_maximal), digits = 5)
-describe_posterior(mean_decel_gaussian_reg_priors_maximal, centrality = "mean")
-
-pp_check(mean_decel_gaussian_reg_priors_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-pp_check(mean_decel_gaussian_reg_priors_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
-
-pp_check(mean_decel_gaussian_reg_priors_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
-pp_check(mean_decel_gaussian_reg_priors_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
-
-pp_check(mean_decel_skewnormal_reg_priors_maximal, type = "hist", group = "ttc_criticality_factor")
 ```
@@
 print(summary(mean_decel_skewnormal_reg_priors_maximal), digits = 5)
-describe_posterior(mean_decel_skewnormal_reg_priors_maximal , centrality = "mean")
+describe_posterior(mean_decel_skewnormal_reg_priors_maximal, centrality = "mean")
 
@@
 
-# posterior predictive checks
-pp_check(sd_yaw_automation_gaussian_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
-pp_check(sd_yaw_automation_gaussian_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
+sd_yaw_automation_lognormal_maximal <- brm(data = response.vehicle.eye %>%
+                                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
+                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
+                             dplyr::mutate(ppid = as.factor(ppid)),
+                           family = lognormal(),
+                           sd_yaw_automation ~ n_back + (n_back | ppid),
+                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
+                                     prior(student_t(3, 0, 2.5), class = "b")),
+                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13, 
+                                                   file = here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_automation_lognormal_maximal"))
+
 ```
@@
 sd_yaw_automation_MER_nback <- sd_yaw_automation_gaussian_maximal %>% 
+  emmeans(~ n_back,
+          epred = TRUE, re_formula = NA) %>% 
+  contrast(method = "revpairwise") %>% 
+  gather_emmeans_draws()
+
+sd_yaw_automation_MER_nback  %>% mean_hdi()
+
+## Log normal model summary
+
+# model summary
+print(summary(sd_yaw_automation_lognormal_maximal), digits = 5)
+describe_posterior(sd_yaw_automation_lognormal_maximal, centrality = "mean")
+
+# average predicted SD of yaw during automation with and without n-back
+predicted_sd_yaw_automation_nback <- sd_yaw_automation_lognormal_maximal %>% 
+  epred_draws(newdata = expand_grid(n_back = c(TRUE, FALSE)),
+              re_formula = NA)
+
+predicted_sd_yaw_automation_nback %>% mean_hdi()
+
+# average marginal effect of n-back
+sd_yaw_automation_MER_nback <- sd_yaw_automation_lognormal_maximal %>% 
   emmeans(~ n_back,
@@
 
+sd_yaw_manual_trunc_gaussian_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_manual_trunc_gaussian_maximal.rds"))
+
+# initial model of sd_yaw
+sd_yaw_manual_trunc_gaussian_maximal <- brm(data = response.vehicle.eye %>%
+                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
+                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
+                             dplyr::mutate(ppid = as.factor(ppid)),
+                           family = gaussian(),
+                           bf(sd_yaw_manual | trunc(lb = 0) ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor| ppid)),
+                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
+                                     prior(student_t(3, 0, 2.5), class = "b")),
+                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13, 
+                           control = list(adapt_delta = 0.95),
+                           file = here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_manual_trunc_gaussian_maximal"))
+
 # posterior predictive checks
@@
 pp_check(sd_yaw_manual_gaussian_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
+
+# posterior predictive checks
+pp_check(sd_yaw_manual_gaussian_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
+pp_check(sd_yaw_manual_gaussian_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
+
+pp_check(sd_yaw_manual_trunc_gaussian_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
+pp_check(sd_yaw_manual_trunc_gaussian_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
 ```
@@
 ```{r}
-print(summary(sd_yaw_manual_gaussian_maximal), digits = 5)
-describe_posterior(sd_yaw_manual_gaussian_maximal, centrality = "mean")
+print(summary(sd_yaw_manual_trunc_gaussian_maximal), digits = 5)
+describe_posterior(sd_yaw_manual_trunc_gaussian_maximal, centrality = "mean")
 
@@
 # predicted mean SD yaw  implied by the model as a function of TTC # setting re_formula = NA tells the function to not use any random effects - here we plot the n-back specific distributions 
-predicted_sd_yaw_manual_ttc <- sd_yaw_manual_gaussian_maximal %>% 
+predicted_sd_yaw_manual_ttc <- sd_yaw_manual_trunc_gaussian_maximal %>% 
   epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
@@
 # margainal effect of TTC for SD of yaw
-sd_yaw_manual_MER_TTC <- sd_yaw_manual_gaussian_maximal %>% 
+sd_yaw_manual_MER_TTC <- sd_yaw_manual_trunc_gaussian_maximal %>% 
   emmeans(~ ttc_criticality_factor,
@@
 ## predicted means for the effect of n-back on SD yaw
-predicted_sd_yaw_manual_nback <- sd_yaw_manual_gaussian_maximal %>% 
+predicted_sd_yaw_manual_nback <- sd_yaw_manual_trunc_gaussian_maximal %>% 
   epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3)),
@@
 # marginal effect of N-back of SD of yaw during manual driving
-sd_yaw_manual_MER_nback <- sd_yaw_manual_gaussian_maximal %>% 
+sd_yaw_manual_MER_nback <- sd_yaw_manual_trunc_gaussian_maximal %>% 
   emmeans(~ n_back,

### 2024-08-30 supplemental_material.Rmd
new code for plotting and model fitting with truncation

@@
   theme_bw() +
-  theme(legend.position = c(.593, .65), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+  theme(legend.position = c(.585, .70), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
 
@@
 
-sm_fig1 <- sm_fig_1_1 / sm_fig_1_2
+sm_fig1 <- sm_fig_1_1 / sm_fig_1_2 + plot_layout(axes = "collect")
 
@@
   theme_bw() +
-  theme(legend.position = c(.94, .69), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+  theme(legend.position = c(.94, .71), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
 
@@
 
-sm_fig2 <- sm_fig2_1 / sm_fig2_2
+sm_fig2 <- sm_fig2_1 / sm_fig2_2 + plot_layout(axes = "collect")
 
@@
 
-ggplot(brt_hist[["data"]], mapping = aes(value)) +
-  geom_histogram() +
-  facet_wrap(~ rep_id)
+brt_hist_df <- brt_hist[["data"]] %>%
+  mutate(across(everything(), ~ replace_na(., 12)))
+
+sim_labs <- c(seq(1, 11, 1), "Observed data")
+names(sim_labs) <- c(seq(1, 11, 1), 12)
+
+sm_fig3 <- ggplot(brt_hist_df, mapping = aes(value, fill = is_y_label)) +
+  geom_histogram(col = "black") +
+  scale_fill_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ rep_id, labeller = labeller(rep_id = sim_labs)) +
+  xlim(0, 5) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ylab(" ") +
+  xlab(expression(RT[B]~ "(s)")) +
+  theme_bw() +
+  theme(legend.position = c(.945, .905), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig3.tiff"), plot = sm_fig3, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
 ```
+
+## Hands on reatcion time
+
+```{r}
+# loading model
+hands_on_rt_model <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/handson_rt_shifted_lognormal_maximal.rds"))
+
+# posterior predictive checks
+hort_stat_grouped_ttc <- pp_check(hands_on_rt_model, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
+hort_stat_grouped_nback <- pp_check(hands_on_rt_model, type = "stat_grouped", stat = "mean", group = "n_back")
+
+ttc_labs <- c("TTC = 3 s", "TTC = 5 s")
+names(ttc_labs) <- c(as.factor(3), as.factor(5))
+
+### STAT GROUPED PLOTS FOR MEAN BRT
+
+# mean HORT for critcality
+sm_fig_4_1 <- ggplot(hort_stat_grouped_ttc[["data"]] %>%
+         dplyr::mutate(ttc_criticality_factor = as.factor(group)), mapping = aes(value)) +
+  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
+  geom_vline(response.vehicle.eye %>% 
+               dplyr::group_by(ttc_criticality_factor) %>%
+               dplyr::summarise(mean_hort = mean(ho.rt)), mapping = aes(xintercept = mean_hort, fill = "T(y)"), col = "darkblue", size = 2) +
+  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
+  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
+  scale_x_continuous(limits = c(1.1, 1.8), breaks = seq(1.1, 1.8, .2), labels = label_number(accuracy = 0.1)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("A") +
+  ylab(" ") +
+  xlab(expression(RT[HO]~ "(s)")) +
+  theme_bw() +
+  theme(legend.position = c(.593, .65), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+n_back_labs <- c("No N-back", "N-back")
+names(n_back_labs) <- c(FALSE, TRUE)
+
+# mean BRT for N-back
+sm_fig_4_2 <- ggplot(hort_stat_grouped_nback[["data"]] %>%
+         dplyr::mutate(n_back = as.factor(group)), mapping = aes(value)) +
+  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
+  geom_vline(response.vehicle.eye %>% 
+               dplyr::group_by(n_back) %>%
+               dplyr::summarise(mean_hort = mean(ho.rt)), mapping = aes(xintercept = mean_hort, fill = "T(y)"), col = "darkblue", size = 2) +
+  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
+  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
+  scale_x_continuous(limits = c(1.1, 1.8), breaks = seq(1.1, 1.8, .2), labels = label_number(accuracy = 0.1)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("B") +
+  ylab(" ") +
+  xlab(expression(RT[HO]~ "(s)")) +
+  theme_bw() +
+  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+sm_fig4 <- sm_fig_4_1 / sm_fig_4_2 + plot_layout(axes = "collect")
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig4.tiff"), plot = sm_fig4, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+
+### DENSITY POSTERIOR PLOTS
+
+pp_check(hands_on_rt_model, type = "dens_overlay_grouped", group = "n_back", ndraws = 100) 
+pp_check(hands_on_rt_model, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
+
+yrep_hort <- response.vehicle.eye %>% 
+  select(ho.rt, n_back, ttc_criticality_factor, ppid) %>% 
+  add_predicted_draws(hands_on_rt_model, ndraws = 100)
+
+sm_fig5_1 <- ggplot() + 
+  geom_density(yrep_hort, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
+  geom_density(response.vehicle.eye, mapping = aes(rt, col = "y"), size = 1) +
+  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
+  xlim(0, 8) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("A") +
+  ylab(" ") +
+  xlab(expression(RT[HO]~ "(s)")) +
+  theme_bw() +
+  theme(legend.position = c(.94, .69), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+sm_fig5_2 <- ggplot() + 
+  geom_density(yrep_hort, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
+  geom_density(response.vehicle.eye, mapping = aes(rt, col = "y"), size = 1) +
+  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
+  xlim(0, 8) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("B") +
+  ylab(" ") +
+  xlab(expression(RT[HO]~ "(s)")) +
+  theme_bw() +
+  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+sm_fig5 <- sm_fig5_1 / sm_fig5_2 + plot_layout(axes = "collect")
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig5.tiff"), plot = sm_fig5, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+
+### SIMULATED NEW PARTICIPANTS
+
+# - change NA to observed data - then use legend to identify y versus y_rep
+hort_hist <- pp_check(hands_on_rt_model, type = "hist", ndraws = 11)
+
+hort_hist_df <- hort_hist[["data"]] %>%
+  mutate(across(everything(), ~ replace_na(., 12)))
+
+sim_labs <- c(seq(1, 11, 1), "Observed data")
+names(sim_labs) <- c(seq(1, 11, 1), 12)
+
+sm_fig6 <- ggplot(hort_hist_df, mapping = aes(value, fill = is_y_label)) +
+  geom_histogram(col = "black") +
+  scale_fill_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ rep_id, labeller = labeller(rep_id = sim_labs)) +
+  xlim(0, 8) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ylab(" ") +
+  xlab(expression(RT[HO]~ "(s)")) +
+  theme_bw() +
+  theme(legend.position = c(.945, .905), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig6.tiff"), plot = sm_fig6, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+```
+
+## Mean deceleration
+
+```{r}
+# loading model
+mean_decel_model <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/mean_decel_skewnormal_reg_priors_maximal.rds"))
+
+# posterior predictive checks
+decel_stat_grouped_ttc <- pp_check(mean_decel_model, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
+decel_stat_grouped_nback <- pp_check(mean_decel_model, type = "stat_grouped", stat = "mean", group = "n_back")
+
+ttc_labs <- c("TTC = 3 s", "TTC = 5 s")
+names(ttc_labs) <- c(as.factor(3), as.factor(5))
+
+### STAT GROUPED PLOTS FOR MEAN BRT
+
+# mean decel for critcality
+sm_fig_7_1 <- ggplot(decel_stat_grouped_ttc[["data"]] %>%
+         dplyr::mutate(ttc_criticality_factor = as.factor(group)), mapping = aes(value)) +
+  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
+  geom_vline(response.vehicle.eye %>% 
+               dplyr::group_by(ttc_criticality_factor) %>%
+               dplyr::summarise(mean_decel = mean(mean_decel)), mapping = aes(xintercept = mean_decel, fill = "T(y)"), col = "darkblue", size = 2) +
+  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
+  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
+  scale_x_continuous(limits = c(-4, -1), breaks = seq(-1, -4, -1), labels = label_number(accuracy = 0.1)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("A") +
+  ylab(" ") +
+  xlab(expression(M[D] ~"("~m/s^2~")")) +
+  theme_bw() +
+  theme(legend.position = c(.593, .65), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+n_back_labs <- c("No N-back", "N-back")
+names(n_back_labs) <- c(FALSE, TRUE)
+
+# mean BRT for N-back
+sm_fig_7_2 <- ggplot(decel_stat_grouped_nback[["data"]] %>%
+         dplyr::mutate(n_back = as.factor(group)), mapping = aes(value)) +
+  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
+  geom_vline(response.vehicle.eye %>% 
+               dplyr::group_by(n_back) %>%
+               dplyr::summarise(mean_decel = mean(mean_decel)), mapping = aes(xintercept = mean_decel, fill = "T(y)"), col = "darkblue", size = 2) +
+  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
+  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
+  scale_x_continuous(limits = c(-3, -1.75), breaks = seq(-3, -2, .25), labels = label_number(accuracy = 0.1)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("B") +
+  ylab(" ") +
+  xlab(expression(M[D] ~"("~m/s^2~")")) +
+  theme_bw() +
+  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+sm_fig7 <- sm_fig_7_1 / sm_fig_7_2 + plot_layout(axes = "collect")
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig7.tiff"), plot = sm_fig7, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+
+### DENSITY POSTERIOR PLOTS
+
+pp_check(mean_decel_model, type = "dens_overlay_grouped", group = "n_back", ndraws = 100) 
+pp_check(mean_decel_model, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
+
+yrep_decel <- response.vehicle.eye %>% 
+  select(mean_decel, n_back, ttc_criticality_factor, ppid) %>% 
+  add_predicted_draws(mean_decel_model, ndraws = 100)
+
+sm_fig8_1 <- ggplot() + 
+  geom_density(yrep_decel, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
+  geom_density(response.vehicle.eye, mapping = aes(mean_decel, col = "y"), size = 1) +
+  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
+  #xlim(-9, 2) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("A") +
+  ylab(" ") +
+  xlab(expression(M[D] ~"("~m/s^2~")")) +
+  theme_bw() +
+  theme(legend.position = c(.94, .69), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+sm_fig8_2 <- ggplot() + 
+  geom_density(yrep_decel, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
+  geom_density(response.vehicle.eye, mapping = aes(mean_decel, col = "y"), size = 1) +
+  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
+  #xlim(-9, 2) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("B") +
+  ylab(" ") +
+  xlab(expression(M[D] ~"("~m/s^2~")")) +
+  theme_bw() +
+  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+sm_fig8 <- sm_fig8_1 / sm_fig8_2 + plot_layout(axes = "collect")
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig8.tiff"), plot = sm_fig8, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+
+### SIMULATED NEW PARTICIPANTS
+
+# - change NA to observed data - then use legend to identify y versus y_rep
+decel_hist <- pp_check(mean_decel_model, type = "hist", ndraws = 11)
+
+decel_hist_df <- decel_hist[["data"]] %>%
+  mutate(across(everything(), ~ replace_na(., 12)))
+
+sim_labs <- c(seq(1, 11, 1), "Observed data")
+names(sim_labs) <- c(seq(1, 11, 1), 12)
+
+sm_fig9 <- ggplot(decel_hist_df, mapping = aes(value, fill = is_y_label)) +
+  geom_histogram(col = "black") +
+  scale_fill_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ rep_id, labeller = labeller(rep_id = sim_labs)) +
+  #xlim(-8.5, 1) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ylab(" ") +
+  xlab(expression(M[D] ~"("~m/s^2~")")) +
+  theme_bw() +
+  theme(legend.position = c(.815, .905), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig9.tiff"), plot = sm_fig9, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+```
+
+## Mean lateral accelerations
+
+```{r}
+# loading model
+lat_model <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/mean_lat_acc_lognormal_maximal.rds"))
+
+# posterior predictive checks
+lat_stat_grouped_ttc <- pp_check(lat_model, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
+lat_stat_grouped_nback <- pp_check(lat_model, type = "stat_grouped", stat = "mean", group = "n_back")
+
+ttc_labs <- c("TTC = 3 s", "TTC = 5 s")
+names(ttc_labs) <- c(as.factor(3), as.factor(5))
+
+### STAT GROUPED PLOTS FOR MEAN lat
+
+# mean lateral for criticality
+sm_fig_10_1 <- ggplot(lat_stat_grouped_ttc[["data"]] %>%
+         dplyr::mutate(ttc_criticality_factor = as.factor(group)), mapping = aes(value)) +
+  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
+  geom_vline(response.vehicle.eye %>% 
+               dplyr::group_by(ttc_criticality_factor) %>%
+               dplyr::summarise(lat = mean(mean_lat_acc)), mapping = aes(xintercept = lat, fill = "T(y)"), col = "darkblue", size = 2) +
+  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
+  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
+  scale_x_continuous(limits = c(.1, .4), breaks = seq(.1, .4, .1), labels = label_number(accuracy = 0.1)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("A") +
+  ylab(" ") +
+  xlab(expression(M[LA] ~"("~m/s^2~")")) +
+  theme_bw() +
+  theme(legend.position = c(.593, .65), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+n_back_labs <- c("No N-back", "N-back")
+names(n_back_labs) <- c(FALSE, TRUE)
+
+# mean lateral for N-back
+sm_fig_10_2 <- ggplot(lat_stat_grouped_nback[["data"]] %>%
+         dplyr::mutate(n_back = as.factor(group)), mapping = aes(value)) +
+  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
+  geom_vline(response.vehicle.eye %>% 
+               dplyr::group_by(n_back) %>%
+               dplyr::summarise(lat = mean(mean_lat_acc)), mapping = aes(xintercept = lat, fill = "T(y)"), col = "darkblue", size = 2) +
+  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
+  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
+  scale_x_continuous(limits = c(.1, .4), breaks = seq(.1, .4, .1), labels = label_number(accuracy = 0.1)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("B") +
+  ylab(" ") +
+  xlab(expression(M[LA] ~"("~m/s^2~")")) +
+  theme_bw() +
+  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+sm_fig10 <- sm_fig_10_1 / sm_fig_10_2 + plot_layout(axes = "collect")
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig10.tiff"), plot = sm_fig10, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+
+### DENSITY POSTERIOR PLOTS
+
+pp_check(lat_model, type = "dens_overlay_grouped", group = "n_back", ndraws = 100) 
+pp_check(lat_model, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
+
+yrep_lat <- response.vehicle.eye %>% 
+  select(mean_lat_acc, n_back, ttc_criticality_factor, ppid) %>% 
+  add_predicted_draws(lat_model, ndraws = 100)
+
+sm_fig11_1 <- ggplot() + 
+  geom_density(yrep_lat, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
+  geom_density(response.vehicle.eye, mapping = aes(mean_lat_acc, col = "y"), size = 1) +
+  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
+  xlim(0, 3) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("A") +
+  ylab(" ") +
+  xlab(expression(M[LA] ~"("~m/s^2~")")) +
+  theme_bw() +
+  theme(legend.position = c(.94, .69), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+sm_fig11_2 <- ggplot() + 
+  geom_density(yrep_lat, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
+  geom_density(response.vehicle.eye, mapping = aes(mean_lat_acc, col = "y"), size = 1) +
+  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
+  xlim(0, 3) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("B") +
+  ylab(" ") +
+  xlab(expression(M[LA] ~"("~m/s^2~")")) +
+  theme_bw() +
+  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+sm_fig11 <- sm_fig11_1 / sm_fig11_2 + plot_layout(axes = "collect")
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig11.tiff"), plot = sm_fig11, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+
+### SIMULATED NEW PARTICIPANTS
+
+# - change NA to observed data - then use legend to identify y versus y_rep
+lat_hist <- pp_check(lat_model, type = "hist", ndraws = 11)
+
+lat_hist_df <- lat_hist[["data"]] %>%
+  mutate(across(everything(), ~ replace_na(., 12)))
+
+sim_labs <- c(seq(1, 11, 1), "Observed data")
+names(sim_labs) <- c(seq(1, 11, 1), 12)
+
+sm_fig12 <- ggplot(lat_hist_df, mapping = aes(value, fill = is_y_label)) +
+  geom_histogram(col = "black") +
+  scale_fill_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ rep_id, labeller = labeller(rep_id = sim_labs)) +
+  scale_x_continuous(limits = c(0, 2), breaks = seq(0, 1.5, .5), labels = label_number(accuracy = 0.1)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ylab(" ") +
+  xlab(expression(M[LA] ~"("~m/s^2~")")) +
+  theme_bw() +
+  theme(legend.position = c(.945, .905), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+  # plot saving
+  ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig12.tiff"), plot = sm_fig12, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+```
+
+## SDLP
+
+```{r}
+# loading model
+sdlp_model <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/sdlp_lognormal_maximal.rds"))
+
+# posterior predictive checks
+sdlp_stat_grouped_ttc <- pp_check(sdlp_model, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
+sdlp_stat_grouped_nback <- pp_check(sdlp_model, type = "stat_grouped", stat = "mean", group = "n_back")
+
+ttc_labs <- c("TTC = 3 s", "TTC = 5 s")
+names(ttc_labs) <- c(as.factor(3), as.factor(5))
+
+### STAT GROUPED PLOTS FOR MEAN SDLP
+
+# mean SDLP for criticality
+sm_fig_13_1 <- ggplot(sdlp_stat_grouped_ttc[["data"]] %>%
+         dplyr::mutate(ttc_criticality_factor = as.factor(group)), mapping = aes(value)) +
+  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
+  geom_vline(response.vehicle.eye %>% 
+               dplyr::group_by(ttc_criticality_factor) %>%
+               dplyr::summarise(sdlp = mean(sdlp)), mapping = aes(xintercept = sdlp, fill = "T(y)"), col = "darkblue", size = 2) +
+  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
+  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
+  scale_x_continuous(limits = c(.2, .6), breaks = seq(.2, .6, .1), labels = label_number(accuracy = 0.1)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("A") +
+  ylab(" ") +
+  xlab(expression(SD[LP]~ "(m)")) +
+  theme_bw() +
+  theme(legend.position = c(.92, .70), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+n_back_labs <- c("No N-back", "N-back")
+names(n_back_labs) <- c(FALSE, TRUE)
+
+# mean SDLP for N-back
+sm_fig_13_2 <- ggplot(sdlp_stat_grouped_nback[["data"]] %>%
+         dplyr::mutate(n_back = as.factor(group)), mapping = aes(value)) +
+  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
+  geom_vline(response.vehicle.eye %>% 
+               dplyr::group_by(n_back) %>%
+               dplyr::summarise(sdlp = mean(sdlp)), mapping = aes(xintercept = sdlp, fill = "T(y)"), col = "darkblue", size = 2) +
+  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
+  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
+  scale_x_continuous(limits = c(.2, .6), breaks = seq(.2, .6, .1), labels = label_number(accuracy = 0.1)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("B") +
+  ylab(" ") +
+  xlab(expression(SD[LP]~ "(m)")) +
+  theme_bw() +
+  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+sm_fig13 <- sm_fig_13_1 / sm_fig_13_2 + plot_layout(axes = "collect")
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig13.tiff"), plot = sm_fig13, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+
+### DENSITY POSTERIOR PLOTS
+
+pp_check(sdlp_model, type = "dens_overlay_grouped", group = "n_back", ndraws = 100) 
+pp_check(sdlp_model, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
+
+yrep_sdlp <- response.vehicle.eye %>% 
+  select(sdlp, n_back, ttc_criticality_factor, ppid) %>% 
+  add_predicted_draws(sdlp_model, ndraws = 100)
+
+sm_fig14_1 <- ggplot() + 
+  geom_density(yrep_sdlp, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
+  geom_density(response.vehicle.eye, mapping = aes(sdlp, col = "y"), size = 1) +
+  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
+  xlim(0, 5) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("A") +
+  ylab(" ") +
+  xlab(expression(SD[LP]~ "(m)")) +
+  theme_bw() +
+  theme(legend.position = c(.94, .72), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+sm_fig14_2 <- ggplot() + 
+  geom_density(yrep_sdlp, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
+  geom_density(response.vehicle.eye, mapping = aes(sdlp, col = "y"), size = 1) +
+  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
+  xlim(0, 5) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("B") +
+  ylab(" ") +
+  xlab(expression(SD[LP]~ "(m)")) +
+  theme_bw() +
+  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+sm_fig14 <- sm_fig14_1 / sm_fig14_2 + plot_layout(axes = "collect")
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig14.tiff"), plot = sm_fig14, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+
+### SIMULATED NEW PARTICIPANTS
+
+sdlp_hist <- pp_check(sdlp_model, type = "hist", ndraws = 11)
+
+sdlp_hist_df <- sdlp_hist[["data"]] %>%
+  mutate(across(everything(), ~ replace_na(., 12)))
+
+sim_labs <- c(seq(1, 11, 1), "Observed data")
+names(sim_labs) <- c(seq(1, 11, 1), 12)
+
+sm_fig15 <- ggplot(sdlp_hist_df, mapping = aes(value, fill = is_y_label)) +
+  geom_histogram(col = "black") +
+  scale_fill_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ rep_id, labeller = labeller(rep_id = sim_labs)) +
+  xlim(0, 5) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ylab(" ") +
+  xlab(expression(SD[LP]~ "(m)")) +
+  theme_bw() +
+  theme(legend.position = c(.945, .905), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig15.tiff"), plot = sm_fig15, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+```
+
+## SD of horizontal gaze - pre-takeover
+
+```{r}
+sd_yaw_automation_lognormal_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_automation_lognormal_maximal.rds"))
+
+# posterior predictive checks
+yaw_pre_stat_grouped_nback <- pp_check(sd_yaw_automation_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
+
+n_back_labs <- c("No N-back", "N-back")
+names(n_back_labs) <- c(FALSE, TRUE)
+
+# mean SSD of yaw for N-back
+sm_fig16 <- ggplot(yaw_pre_stat_grouped_nback[["data"]] %>%
+         dplyr::mutate(n_back = as.factor(group)), mapping = aes(value)) +
+  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
+  geom_vline(response.vehicle.eye %>% 
+               dplyr::group_by(n_back) %>%
+               dplyr::summarise(sd_yaw_automation = mean(sd_yaw_automation)), mapping = aes(xintercept = sd_yaw_automation, fill = "T(y)"), col = "darkblue", size = 2) +
+  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
+  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
+  scale_x_continuous(limits = c(3, 12), breaks = seq(4, 12, 2), labels = label_number(accuracy = 0.1)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ylab(" ") +
+  xlab(expression(SD[YAW]~ "(°)")) +
+  theme_bw() +
+  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig16.tiff"), plot = sm_fig16, width = 16, height = 6, units = 'cm', dpi = 300, type = 'cairo')
+
+### DENSITY POSTERIOR PLOTS 
+pp_check(sd_yaw_automation_lognormal_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
+
+yrep_yaw_pre <- response.vehicle.eye %>% 
+  select(sd_yaw_automation, n_back, ttc_criticality_factor, ppid) %>% 
+  add_predicted_draws(sd_yaw_automation_lognormal_maximal, ndraws = 100)
+
+sm_fig17 <- ggplot() + 
+  geom_density(yrep_yaw_pre, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
+  geom_density(response.vehicle.eye, mapping = aes(sd_yaw_automation, col = "y"), size = 1) +
+  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ylab(" ") +
+  xlab(expression(SD[YAW]~ "(°)")) +
+  theme_bw() +
+  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig17.tiff"), plot = sm_fig17, width = 16, height = 6, units = 'cm', dpi = 300, type = 'cairo')
+
+### SIMULATED NEW PARTICIPANTS
+yaw_pre_hist <- pp_check(sd_yaw_automation_lognormal_maximal, type = "hist", ndraws = 11)
+
+yaw_pre_hist_df <- yaw_pre_hist[["data"]] %>%
+  mutate(across(everything(), ~ replace_na(., 12)))
+
+sim_labs <- c(seq(1, 11, 1), "Observed data")
+names(sim_labs) <- c(seq(1, 11, 1), 12)
+
+sm_fig18 <- ggplot(yaw_pre_hist_df, mapping = aes(value, fill = is_y_label)) +
+  geom_histogram(col = "black") +
+  scale_fill_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ rep_id, labeller = labeller(rep_id = sim_labs)) +
+  xlim(-5, 40) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ylab(" ") +
+  xlab(expression(SD[YAW]~ "(°)")) +
+  theme_bw() +
+  theme(legend.position = c(.945, .905), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig18.tiff"), plot = sm_fig18, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+```
+
+## SD of horizontal gaze - post-takeover (Gaussian)
+
+```{r}
+# loading model
+yaw_post_model <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_manual_gaussian_maximal.rds"))
+
+# posterior predictive checks
+yaw_post_grouped_ttc <- pp_check(yaw_post_model, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
+yaw_post_grouped_nback <- pp_check(yaw_post_model, type = "stat_grouped", stat = "mean", group = "n_back")
+
+ttc_labs <- c("TTC = 3 s", "TTC = 5 s")
+names(ttc_labs) <- c(as.factor(3), as.factor(5))
+
+### STAT GROUPED PLOTS FOR sd of yaw
+sm_fig_19_1 <- ggplot(yaw_post_grouped_ttc[["data"]] %>%
+         dplyr::mutate(ttc_criticality_factor = as.factor(group)), mapping = aes(value)) +
+  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
+  geom_vline(response.vehicle.eye %>% 
+               dplyr::group_by(ttc_criticality_factor) %>%
+               dplyr::summarise(sd_yaw = mean(sd_yaw_manual)), mapping = aes(xintercept = sd_yaw, fill = "T(y)"), col = "darkblue", size = 2) +
+  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
+  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
+  scale_x_continuous(limits = c(8, 12), breaks = seq(8, 12, 1), labels = label_number(accuracy = 0.1)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("A") +
+  ylab(" ") +
+  xlab(expression(SD[YAW]~ "(°)")) +
+  theme_bw() +
+  theme(legend.position = c(.92, .70), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+n_back_labs <- c("No N-back", "N-back")
+names(n_back_labs) <- c(FALSE, TRUE)
+
+# mean lateral for N-back
+sm_fig_19_2 <- ggplot(yaw_post_grouped_nback[["data"]] %>%
+         dplyr::mutate(n_back = as.factor(group)), mapping = aes(value)) +
+  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
+  geom_vline(response.vehicle.eye %>% 
+               dplyr::group_by(n_back) %>%
+               dplyr::summarise(sd_yaw = mean(sd_yaw_manual)), mapping = aes(xintercept = sd_yaw, fill = "T(y)"), col = "darkblue", size = 2) +
+  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
+  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
+  scale_x_continuous(limits = c(8, 12), breaks = seq(8, 12, 1), labels = label_number(accuracy = 0.1)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("B") +
+  ylab(" ") +
+  xlab(expression(SD[YAW]~ "(°)")) +
+  theme_bw() +
+  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+sm_fig19 <- sm_fig_19_1 / sm_fig_19_2 + plot_layout(axes = "collect")
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig19.tiff"), plot = sm_fig19, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+
+### DENSITY POSTERIOR PLOTS 
+pp_check(yaw_post_model, type = "dens_overlay_grouped", group = "n_back", ndraws = 100) 
+pp_check(yaw_post_model, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
+
+yrep_yaw_post <- response.vehicle.eye %>% 
+  select(sd_yaw_manual, n_back, ttc_criticality_factor, ppid) %>% 
+  add_predicted_draws(yaw_post_model, ndraws = 100)
+
+sm_fig20_1 <- ggplot() + 
+  geom_density(yrep_yaw_post, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
+  geom_density(response.vehicle.eye, mapping = aes(sd_yaw_manual, col = "y"), size = 1) +
+  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
+  #xlim(-5, 25) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("A") +
+  ylab(" ") +
+  xlab(expression(SD[YAW]~ "(°)")) +
+  theme_bw() +
+  theme(legend.position = c(.94, .69), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+sm_fig20_2 <- ggplot() + 
+  geom_density(yrep_yaw_post, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
+  geom_density(response.vehicle.eye, mapping = aes(sd_yaw_manual, col = "y"), size = 1) +
+  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
+  #xlim(-5, 25) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("B") +
+  ylab(" ") +
+  xlab(expression(SD[YAW]~ "(°)")) +
+  theme_bw() +
+  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+sm_fig20 <- sm_fig20_1 / sm_fig20_2 + plot_layout(axes = "collect")
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig20.tiff"), plot = sm_fig20, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+
+### SIMULATED NEW PARTICIPANTS
+lat_hist <- pp_check(yaw_post_model, type = "hist", ndraws = 11)
+
+lat_hist_df <- lat_hist[["data"]] %>%
+  mutate(across(everything(), ~ replace_na(., 12)))
+
+sim_labs <- c(seq(1, 11, 1), "Observed data")
+names(sim_labs) <- c(seq(1, 11, 1), 12)
+
+sm_fig21 <- ggplot(lat_hist_df, mapping = aes(value, fill = is_y_label)) +
+  geom_histogram(col = "black") +
+  scale_fill_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ rep_id, labeller = labeller(rep_id = sim_labs)) +
+  #xlim(-5, 30) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ylab(" ") +
+  xlab(expression(SD[YAW]~ "(°)")) +
+  theme_bw() +
+  theme(legend.position = c(.611, .955), legend.direction = "horizontal", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig21.tiff"), plot = sm_fig21, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+```
+
+## SD of horizontal gaze - post-takeover (Truncated Gaussian)
+
+```{r}
+# loading model
+yaw_post_model_trunc <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_manual_trunc_gaussian_maximal.rds"))
+
+ttc_labs <- c("TTC = 3 s", "TTC = 5 s")
+names(ttc_labs) <- c(as.factor(3), as.factor(5))
+
+n_back_labs <- c("No N-back", "N-back")
+names(n_back_labs) <- c(FALSE, TRUE)
+
+### DENSITY POSTERIOR PLOTS 
+pp_check(yaw_post_model_trunc, type = "dens_overlay_grouped", group = "n_back", ndraws = 100) 
+pp_check(yaw_post_model_trunc, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
+
+yrep_yaw_post <- response.vehicle.eye %>% 
+  select(sd_yaw_manual, n_back, ttc_criticality_factor, ppid) %>% 
+  add_predicted_draws(yaw_post_model_trunc, ndraws = 100)
+
+sm_fig22_1 <- ggplot() + 
+  geom_density(yrep_yaw_post, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
+  geom_density(response.vehicle.eye, mapping = aes(sd_yaw_manual, col = "y"), size = 1) +
+  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
+  #xlim(-5, 25) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("A") +
+  ylab(" ") +
+  xlab(expression(SD[YAW]~ "(°)")) +
+  theme_bw() +
+  theme(legend.position = c(.94, .69), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+sm_fig22_2 <- ggplot() + 
+  geom_density(yrep_yaw_post, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
+  geom_density(response.vehicle.eye, mapping = aes(sd_yaw_manual, col = "y"), size = 1) +
+  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
+  #xlim(-5, 25) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ggtitle("B") +
+  ylab(" ") +
+  xlab(expression(SD[YAW]~ "(°)")) +
+  theme_bw() +
+  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+sm_fig22 <- sm_fig22_1 / sm_fig22_2 + plot_layout(axes = "collect")
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig22.tiff"), plot = sm_fig22, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+
+### SIMULATED NEW PARTICIPANTS
+lat_hist <- pp_check(yaw_post_model_trunc, type = "hist", ndraws = 11)
+
+lat_hist_df <- lat_hist[["data"]] %>%
+  mutate(across(everything(), ~ replace_na(., 12)))
+
+sim_labs <- c(seq(1, 11, 1), "Observed data")
+names(sim_labs) <- c(seq(1, 11, 1), 12)
+
+sm_fig23 <- ggplot(lat_hist_df, mapping = aes(value, fill = is_y_label)) +
+  geom_histogram(col = "black") +
+  scale_fill_manual(name = NULL, values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
+  facet_wrap(~ rep_id, labeller = labeller(rep_id = sim_labs)) +
+  #xlim(-5, 30) +
+  scale_y_continuous(expand = c(0, 0)) +
+  ylab(" ") +
+  xlab(expression(SD[YAW]~ "(°)")) +
+  theme_bw() +
+  theme(legend.position = c(.945, .565), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig23.tiff"), plot = sm_fig23, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+```

### 2024-09-03 manuscript_and_modelling_plots_takeovers.Rmd
edited figs and associated code

@@
 # regularising priors for parameter values
-prior(student_t(5, 9, 2.5)) %>% 
+prior(normal(0, 5)) %>% 
   parse_dist() %>% 
@@
                                            file = here::here("takeover_performance_cogload_time_budget/Models/mean_decel_gaussian_reg_priors_maximal"))
+
+print(summary(mean_decel_skewnormal_reg_priors_maximal), digits = 5)
+describe_posterior(mean_decel_skewnormal_reg_priors_maximal, centrality = "mean")
 ```
@@
                                       file = here::here("takeover_performance_cogload_time_budget/Models/mean_lat_acc_lognormal_maximal"))
-
-pp_check(mean_lat_acc_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-pp_check(mean_lat_acc_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
-
-pp_check(mean_lat_acc_lognormal_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
-pp_check(mean_lat_acc_lognormal_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
 ```
@@
                                    file = here::here("takeover_performance_cogload_time_budget/Models/sdlp_lognormal_maximal"))
-
-pp_check(sdlp_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-pp_check(sdlp_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
-
-pp_check(sdlp_lognormal_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
-pp_check(sdlp_lognormal_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
-
-pp_check(sdlp_lognormal_maximal, type = "hist", group = "ttc_criticality_factor")
 ```
@@
 
+sd_yaw_automation_lognormal_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_automation_lognormal_maximal.rds"))
+
 sd_yaw_automation_lognormal_maximal <- brm(data = response.vehicle.eye %>%
@@
                                                    file = here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_automation_lognormal_maximal"))
-
 ```
@@
 ```{r}
-# model summmary
-print(summary(sd_yaw_automation_gaussian_maximal), digits = 5)
-describe_posterior(sd_yaw_automation_gaussian_maximal, centrality = "mean")
-
-# average predicted SD of yaw during automation with and without n-back
-predicted_sd_yaw_automation_nback <- sd_yaw_automation_gaussian_maximal %>% 
-  epred_draws(newdata = expand_grid(n_back = c(TRUE, FALSE)),
-              re_formula = NA)
-
-predicted_sd_yaw_automation_nback %>% mean_hdi()
-
-# average marginal effect of n-back
-sd_yaw_automation_MER_nback <- sd_yaw_automation_gaussian_maximal %>% 
-  emmeans(~ n_back,
-          epred = TRUE, re_formula = NA) %>% 
-  contrast(method = "revpairwise") %>% 
-  gather_emmeans_draws()
-
-sd_yaw_automation_MER_nback  %>% mean_hdi()
-
 ## Log normal model summary
@@
 
+# truncated Gaussian model
 sd_yaw_manual_trunc_gaussian_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_manual_trunc_gaussian_maximal.rds"))
 
-# initial model of sd_yaw
 sd_yaw_manual_trunc_gaussian_maximal <- brm(data = response.vehicle.eye %>%
@@
                            file = here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_manual_trunc_gaussian_maximal"))
-
-# posterior predictive checks
-pp_check(sd_yaw_manual_gaussian_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-pp_check(sd_yaw_manual_gaussian_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
-
-pp_check(sd_yaw_manual_gaussian_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
-pp_check(sd_yaw_manual_gaussian_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
-
-# posterior predictive checks
-pp_check(sd_yaw_manual_gaussian_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
-pp_check(sd_yaw_manual_gaussian_maximal, type = "stat_grouped", stat = "mean", group = "n_back")
-
-pp_check(sd_yaw_manual_trunc_gaussian_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
-pp_check(sd_yaw_manual_trunc_gaussian_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
 ```
@@
 predicted_draws = empty_grid %>%
-  add_predicted_draws(sd_yaw_manual_gaussian_maximal)
+  add_predicted_draws(sd_yaw_manual_trunc_gaussian_maximal)
 
 expected_values = empty_grid %>%
-  add_epred_draws(sd_yaw_manual_gaussian_maximal)
+  add_epred_draws(sd_yaw_manual_trunc_gaussian_maximal)
 
@@
 # relative size of  heterogenity effect for 2-back on mu
-summary(sd_yaw_manual_gaussian_maximal)[["random"]][["ppid"]][2,1] / summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1]
+summary(sd_yaw_manual_trunc_gaussian_maximal)[["random"]][["ppid"]][2,1] / summary(sd_yaw_manual_trunc_gaussian_maximal)[["fixed"]][2,1]
 
@@
 # individual effects for SD of yaw during manual driving
-ppid.effects <- as.data.frame(ranef(sd_yaw_manual_gaussian_maximal)) %>%
+ppid.effects <- as.data.frame(ranef(sd_yaw_manual_trunc_gaussian_maximal)) %>%
   dplyr::select(ppid.Estimate.n_backTRUE) %>%
-  dplyr::mutate(ranef = ppid.Estimate.n_backTRUE + summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1]) %>%
+  dplyr::mutate(ranef = ppid.Estimate.n_backTRUE + summary(sd_yaw_manual_trunc_gaussian_maximal)[["fixed"]][2,1]) %>%
   tibble::rownames_to_column("ppid")
@@
 # CI interval for average effect
-bayes.credible.intervals <- as.data.frame(summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][3:4])
+bayes.credible.intervals <- as.data.frame(summary(sd_yaw_manual_trunc_gaussian_maximal)[["fixed"]][3:4])
 
 # select random effects parameter 
-ran.effects <- summary(sd_yaw_manual_gaussian_maximal)[["random"]][["ppid"]][2,1]
+ran.effects <- summary(sd_yaw_manual_trunc_gaussian_maximal)[["random"]][["ppid"]][2,1]
 
@@
   geom_hline(aes(yintercept = bayes.credible.intervals$`u-95% CI`[2], linetype="95% CI"), size = 1.5,  color = viridis(5)[3]) +
-  geom_hline(aes(yintercept = summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1], linetype = "beta_1"), size = 1.5, color = "black") +
-  geom_hline(aes(yintercept = summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1] + 1.96 * ran.effects, linetype = "95% HI"), size = 1.5, color = viridis(5)[2]) +
-  geom_hline(aes(yintercept = summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1] - 1.96 * ran.effects, linetype = "95% HI"), size = 1.5, color = viridis(5)[2]) +
+  geom_hline(aes(yintercept = summary(sd_yaw_manual_trunc_gaussian_maximal)[["fixed"]][2,1], linetype = "beta_1"), size = 1.5, color = "black") +
+  geom_hline(aes(yintercept = summary(sd_yaw_manual_trunc_gaussian_maximal)[["fixed"]][2,1] + 1.96 * ran.effects, linetype = "95% HI"), size = 1.5, color = viridis(5)[2]) +
+  geom_hline(aes(yintercept = summary(sd_yaw_manual_trunc_gaussian_maximal)[["fixed"]][2,1] - 1.96 * ran.effects, linetype = "95% HI"), size = 1.5, color = viridis(5)[2]) +
   scale_linetype_manual(name = " ", values = c(2, 1, 1), labels = c(expression(CI[95]), expression(HI[95]), expression(beta[N])), guide = guide_legend(override.aes = list(color = c(viridis(5)[3], viridis(5)[2], "black")))) +
@@
 # heterogenity intervals for the effect of N-back on SD of yaw during manual driving
-summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1] + 1.96 * ran.effects
-summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1] - 1.96 * ran.effects
-
-# participant 3, beta_n = -0.065
+summary(sd_yaw_manual_trunc_gaussian_maximal)[["fixed"]][2,1] + 1.96 * ran.effects
+summary(sd_yaw_manual_trunc_gaussian_maximal)[["fixed"]][2,1] - 1.96 * ran.effects
+
+# participant 3, beta_n = -0.022
 p_3 <- ggplot(dat.eye.manual %>%
@@
   ggtitle(label = "B",
-          subtitle = "Participant 3," ~ beta[N[3]] ~ "= -.065") +
+          subtitle = "Participant 3," ~ beta[N[3]] ~ "= -.022") +
   xlab("Yaw (°)") +
@@
 
-# participant 14, beta_n = .036
+# participant 14, beta_n = 0.052
 p_14 <- ggplot(dat.eye.manual %>%
@@
   ggtitle(label = " ",
-          subtitle = "Participant 14," ~ beta[N[14]] ~ "= .036") +
+          subtitle = "Participant 14," ~ beta[N[14]] ~ "= .052") +
   xlab("Yaw (°)") +
@@
 
-# participant 7, beta_n = -2.128
+# participant 7, beta_n = -2.424
 p_7 <- ggplot(dat.eye.manual %>%
@@
   ggtitle(label = "C",
-          subtitle = "Participant 7," ~ beta[N[7]] ~ "= -2.128") +
+          subtitle = "Participant 7," ~ beta[N[7]] ~ "= -2.424") +
   xlab("Yaw (°)") +
@@
 
-# participant 13, beta_n = -2.391
+# participant 13, beta_n = -2.317
 p_13 <- ggplot(dat.eye.manual %>%
@@
   ggtitle(label = " ",
-          subtitle = "Participant 13," ~ beta[N[13]] ~ "= -2.391") +
+          subtitle = "Participant 13," ~ beta[N[13]] ~ "= -2.317") +
   xlab("Yaw (°)") +

### 2024-09-03 supplemental_material.Rmd
edited figs and associated code

@@
 library(ggforce)
+
+if(!require(afex)) install.packages("afex")
+library(afex)
+
+if(!require(BayesFactor)) install.packages("BayesFactor")
+library(BayesFactor)
 ```
@@
 
+## Identifying order effects
+
+```{r}
+# braking reaction time
+rt_order <- anovaBF(rt ~ event.order.factor, data = response.vehicle.eye %>% 
+                      dplyr::mutate(event.order.factor = as.factor(event.order)) %>%
+                      dplyr::group_by(ppid, event.order.factor) %>%
+                      dplyr::summarise(rt = mean(rt)))
+
+rt_order
+
+# hands on time
+hort_order <- anovaBF(ho.rt ~ event.order.factor, data = response.vehicle.eye %>%
+                        dplyr::mutate(event.order.factor = as.factor(event.order)) %>%
+                        dplyr::group_by(ppid, event.order.factor) %>%
+                        dplyr::summarise(ho.rt = mean(ho.rt)))
+
+hort_order
+
+# mean decel
+decel_order <- anovaBF(mean_decel ~ event.order.factor, data = response.vehicle.eye %>%
+                         dplyr::mutate(event.order.factor = as.factor(event.order)) %>%
+                         dplyr::group_by(ppid, event.order.factor) %>%
+                          dplyr::summarise(mean_decel = mean(mean_decel)))
+
+decel_order
+
+# mean lateral accelerations
+lat_order <- anovaBF(mean_lat_acc ~ event.order.factor, data = response.vehicle.eye %>%
+                       dplyr::mutate(event.order.factor = as.factor(event.order)) %>%
+                       dplyr::group_by(ppid, event.order.factor) %>%
+                        dplyr::summarise(mean_lat_acc = mean(mean_lat_acc)))
+
+lat_order
+
+# sdlp
+sdlp_order <- anovaBF(sdlp ~ event.order.factor, data = response.vehicle.eye %>%
+                        dplyr::mutate(event.order.factor = as.factor(event.order)) %>%
+                        dplyr::group_by(ppid, event.order.factor) %>%
+                        dplyr::summarise(sdlp = mean(sdlp))
+                        )
+
+sdlp_order
+
+# SD of yaw - automation
+yaw_automation <- anovaBF(sd_yaw_automation ~ event.order.factor, data = response.vehicle.eye %>%
+                        dplyr::mutate(event.order.factor = as.factor(event.order)) %>%
+                        dplyr::group_by(ppid, event.order.factor) %>%
+                        dplyr::summarise(sd_yaw_automation = mean(sd_yaw_automation))
+                        )
+
+yaw_automation
+
+# SD of yaw - manual
+yaw_manual <- anovaBF(sd_yaw_manual ~ event.order.factor, data = response.vehicle.eye %>%
+                        dplyr::mutate(event.order.factor = as.factor(event.order)) %>%
+                        dplyr::group_by(ppid, event.order.factor) %>%
+                        dplyr::summarise(sd_yaw_manual = mean(sd_yaw_manual))
+                        )
+
+yaw_manual
+```
+
 ## Braking reaction time

### 2024-11-22 manuscript_and_modelling_plots_takeovers.Rmd
analysis code and extra plots

@@
 ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig4.tiff"), plot = fig4, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig4.png"), plot = fig4, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
 ```
@@
 ggsave(here::here("takeover_performance_cogload_time_budget/Figures/fig8.tiff"), plot = fig8, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Figures/fig8.png"), plot = fig8, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
 ```
@@
 ggsave(here::here("takeover_performance_cogload_time_budget/Figures/fig12.tiff"), plot = fig12, width = 16, height = 18, units = 'cm', dpi = 300, type = 'cairo')
-```
+
+ggsave(here::here("takeover_performance_cogload_time_budget/Figures/fig12.png"), plot = fig12, width = 16, height = 18, units = 'cm', dpi = 300, type = 'cairo')
+```

### 2025-02-11 manuscript_and_modelling_plots_takeovers.Rmd
some new figures

@@
 ggsave(here::here("takeover_performance_cogload_time_budget/Figures/fig10.tiff"), plot = fig10, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
+```
+
+# SD of horizontal gaze during maual driving - effect of N-back
+
+```{r}
+# predicted means
+predicted_sd_yaw_manual_nback_plot <- ggplot(predicted_sd_yaw_manual_nback, aes(x = .epred, y = " ", fill = n_back)) +
+  stat_halfeye(alpha = .5) +
+  ylab(NULL) +
+  xlab(expression("Predicted" ~ mu ~ "of" ~ SD[YAW]~ "(°)")) +
+  scale_fill_discrete(name = "Task", labels = c("Monitoring", "N-back + monitoring")) +
+  ggtitle(expression(SD[YAW]~": post-transition manual drive")) +
+  xlim(8, 17) +
+  theme_bw() +
+  theme(legend.position = c(.70, .70), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 10), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 10, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+# Average marginal effect for SD of yaw
+sd_yaw_manual_MER_nback_plot <- ggplot(sd_yaw_manual_MER_nback, aes(x = .value, y = " ")) +
+  stat_halfeye() +
+  ylab(NULL) +
+  xlab(expression(MER[SD[YAW]]~ "(°)")) +
+  #scale_fill_discrete(name = "TTC", labels = c("3 s", "5 s")) +
+  theme_bw() +
+  theme(legend.position = c(.9, .7), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+
+fig99 <- (predicted_sd_yaw_manual_nback_plot | sd_yaw_manual_MER_nback_plot)
+
+# plot saving
+ggsave(here::here("takeover_performance_cogload_time_budget/Figures/fig99.tiff"), plot = fig99, width = 18, height = 6, units = 'cm', dpi = 300, type = 'cairo')
+
 ```

### 2025-03-07 manuscript_and_modelling_plots_takeovers.Rmd
updated figures for manuscript

@@
 
-predicted_braking_rt_ttc_plot <- ggplot(predicted_braking_rt_ttc, aes(x = .epred, y = " ", fill = ttc_criticality_factor)) +
+predicted_braking_rt_ttc_plot <- ggplot(predicted_braking_rt_ttc, aes(x = .epred, fill = ttc_criticality_factor)) +
   stat_halfeye(alpha = .5) +
-  ylab(NULL) +
+  ylim(-.1, 1) +
+  ylab("Density") +
   xlab(expression("Predicted" ~ mu ~ "of" ~ RT[B]~ "(s)")) +
@@
 # Marginal Effects at Representative values (MER) of TTC on braking RT
-braking_rt_MER_TTC_plot <- ggplot(braking_rt_MER_TTC, aes(x = .value, y = " ")) +
+braking_rt_MER_TTC_plot <- ggplot(braking_rt_MER_TTC, aes(x = .value)) +
   stat_halfeye() +
-  ylab(NULL) +
+  ylim(-.1, 1) +
+  ylab("Density") +
   xlab(expression(MER[RT[B]]~ "(s) for TTC")) +
@@
 
-fig4 <- posterior_braking_rt / (predicted_braking_rt_ttc_plot | braking_rt_MER_TTC_plot)
+fig4 <- posterior_braking_rt / (predicted_braking_rt_ttc_plot | braking_rt_MER_TTC_plot) + plot_layout(axes = "collect")
 
@@
 # predicted hands-on time 
-predicted_ho_rt_ttc_plot <- ggplot(predicted_ho_rt_ttc, aes(x = .epred, y = " ", fill = ttc_criticality_factor)) +
+predicted_ho_rt_ttc_plot <- ggplot(predicted_ho_rt_ttc, aes(x = .epred, fill = ttc_criticality_factor)) +
   stat_halfeye(alpha = .5) +
-  ylab(NULL) +
+  ylim(-.1, 1) +
+  ylab("Density") +
   xlab(expression("Predicted" ~ mu ~ "of" ~ RT[HO]~ "(s)")) +
@@
   theme_bw() +
-  theme(legend.position = c(.88, .60), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+  theme(legend.position = c(.85, .65), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
 
 # MER of TTC on hands on RT
-ho_rt_MER_TTC_plot <- ggplot(ho_rt_MER_TTC, aes(x = .value, y = " ")) +
+ho_rt_MER_TTC_plot <- ggplot(ho_rt_MER_TTC, aes(x = .value)) +
   stat_halfeye() +
-  ylab(NULL) +
+  ylim(-.1, 1) +
+  ylab("Density") +
   xlab(expression(MER[RT[HO]]~ "(s) of TTC")) +
@@
   theme_bw() +
-  theme(legend.position = c(.93, .62), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+  theme(legend.position = c(.90, .65), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
 
@@
                                            file = here::here("takeover_performance_cogload_time_budget/Models/mean_decel_skewnormal_reg_priors_maximal"))
-
-mean_decel_trunc_gaussian_reg_priors_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/mean_decel_trunc_skewnormal_reg_priors_maximal.rds"))
-
-# modelling average deceleration with regularising priors. Random effects structure is maximal. Distribution family is skew-normal. 
-mean_decel_trunc_gaussian_reg_priors_maximal <- brm(data = response.vehicle.eye %>%
-                                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
-                                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
-                                             dplyr::mutate(ppid = as.factor(ppid)),
-                                           family = gaussian(),
-                                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
-                                                     prior(student_t(3, 0, 2.5), class = "b")),
-                                           bf(mean_decel | trunc(ub = 0) ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor | ppid)),
-                                           control = list(adapt_delta = 0.99999999999),
-                                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
-                                           file = here::here("takeover_performance_cogload_time_budget/Models/mean_decel_trunc_gaussian_reg_priors_maximal"))
-
-mean_decel_gaussian_reg_priors_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/mean_decel_gaussian_reg_priors_maximal.rds"))
-
-# modelling average deceleration with regularising priors. Random effects structure is maximal. Distribution family is Gaussian.
-mean_decel_gaussian_reg_priors_maximal <- brm(data = response.vehicle.eye %>%
-                                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
-                                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
-                                             dplyr::mutate(ppid = as.factor(ppid)),
-                                           family = gaussian(),
-                                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
-                                                     prior(student_t(3, 0, 2.5), class = "b")),
-                                           bf(mean_decel ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor | ppid)),
-                                           control = list(adapt_delta = 0.99999999999),
-                                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
-                                           file = here::here("takeover_performance_cogload_time_budget/Models/mean_decel_gaussian_reg_priors_maximal"))
 
@@
 # predicted mean decelerations
-predicted_mean_decel_ttc_plot <- ggplot(predicted_mean_decel_ttc, aes(x = .epred, y = " ", fill = ttc_criticality_factor)) +
+predicted_mean_decel_ttc_plot <- ggplot(predicted_mean_decel_ttc, aes(x = .epred, fill = ttc_criticality_factor)) +
   stat_halfeye(alpha = .5) +
-  ylab(NULL) +
+  ylim(-.1, 1) +
+  ylab("Density") +
   xlab(expression("Predicted" ~ mu ~ "of" ~ M[D] ~ "("~m/s^2~")")) +
@@
   theme_bw() +
-  theme(legend.position = c(.88, .57), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+  theme(legend.position = c(.85, .60), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
 
 # MER of TTC on mean deceleration
-mean_decel_MER_TTC_plot <- ggplot(mean_decel_MER_TTC, aes(x = .value, y = " ")) +
+mean_decel_MER_TTC_plot <- ggplot(mean_decel_MER_TTC, aes(x = .value)) +
   stat_halfeye() +
-  ylab(NULL) +
+    ylim(-.1, 1) +
+  ylab("Density") +
   xlab(expression(MER[M[D]]~ "("~m/s^2~")" ~ "of TTC")) +
@@
 # predicted mean lateral accelerations
-predicted_lat_acc_ttc_plot <- ggplot(predicted_lat_acc_ttc, aes(x = .epred, y = " ", fill = ttc_criticality_factor)) +
+predicted_lat_acc_ttc_plot <- ggplot(predicted_lat_acc_ttc, aes(x = .epred, fill = ttc_criticality_factor)) +
   stat_halfeye(alpha = .5) +
-  ylab(NULL) +
+  ylim(-.1, 1) +
+  ylab("Density") +
   xlab(expression("Predicted" ~ mu ~ "of" ~ M[LA] ~ "("~m/s^2~")")) +
@@
 # predicted means of SDLP
-predicted_SDLP_ttc_plot <- ggplot(predicted_SDLP_ttc, aes(x = .epred, y = " ", fill = ttc_criticality_factor)) +
+predicted_SDLP_ttc_plot <- ggplot(predicted_SDLP_ttc, aes(x = .epred, fill = ttc_criticality_factor)) +
   stat_halfeye(alpha = .5) +
-  ylab(NULL) +
+  ylim(-.1, 1) +
+  ylab("Density") +
   xlab(expression("Predicted" ~ mu ~ "of" ~ SD[LP]~ "(m)")) +
@@
   theme_bw() +
-  theme(legend.position = c(.88, .6), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+  theme(legend.position = c(.85, .65), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
 
 # Average marginal effect of TTC on SDLP
-SDLP_MER_TTC_plot <- ggplot(SDLP_MER_TTC, aes(x = .value, y = " ")) +
+SDLP_MER_TTC_plot <- ggplot(SDLP_MER_TTC, aes(x = .value)) +
   stat_halfeye() +
-  ylab(NULL) +
+  ylim(-.1, 1) +
+  ylab("Density") +
   xlab(expression(MER[SD[LP]]~ "(m) of TTC")) +
@@
 # predicted means
-predicted_sd_yaw_manual_ttc_plot <- ggplot(predicted_sd_yaw_manual_ttc, aes(x = .epred, y = " ", fill = ttc_criticality_factor)) +
+predicted_sd_yaw_manual_ttc_plot <- ggplot(predicted_sd_yaw_manual_ttc, aes(x = .epred, fill = ttc_criticality_factor)) +
   stat_halfeye(alpha = .5) +
-  ylab(NULL) +
+  ylim(-.1, 1) +
+  ylab("Density") +
   xlab(expression("Predicted" ~ mu ~ "of" ~ SD[YAW]~ "(°)")) +
@@
   theme_bw() +
-  theme(legend.position = c(.88, .6), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
+  theme(legend.position = c(.85, .65), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 11), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))
 
 # Average marginal effect for SD of yaw
-sd_yaw_manual_MER_TTC_plot <- ggplot(sd_yaw_manual_MER_TTC, aes(x = .value, y = " ")) +
+sd_yaw_manual_MER_TTC_plot <- ggplot(sd_yaw_manual_MER_TTC, aes(x = .value)) +
   stat_halfeye() +
-  ylab(NULL) +
+  ylim(-.1, 1) +
+  ylab("Density") +
   xlab(expression(MER[SD[YAW]]~ "(°)")) +
